---
title: "family_selection_long"
author: "Eren Kafadar"
date: "2025-02-27"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
diagnostics = FALSE
generate = FALSE
save_fits = FALSE
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library(dplyr)
library(magrittr)
library(readr)
library(stringr)
library(ggplot2)
library(gamlss) #to fit model
require(gamlss.ggplots)
library(tidyr)
library(gamlssTools) #Margaret's package
library(gridExtra)

source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/inspect_model_fits.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/gamlss_functions_EK.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/data_functions.R")

source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/pred_og_centile_EK.R")

phenotypes <- readRDS("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/phenotype_set.rds")

#df to map variable names onto names displayed on figures
name_mapping <- data.frame(
  abbreviation = c(
     "smri_vol_cdk_totallh", "smri_vol_cdk_totalrh", "smri_vol_cdk_total",   
     "totalWM_cb", "totalWM_crb", "totalGM_crb",
     
    "smri_vol_scs_cbwmatterlh", "smri_vol_scs_ltventriclelh", "smri_vol_scs_inflatventlh",
    "smri_vol_scs_crbwmatterlh", "smri_vol_scs_crbcortexlh", "smri_vol_scs_tplh",
    "smri_vol_scs_caudatelh", "smri_vol_scs_putamenlh", "smri_vol_scs_pallidumlh",
    "smri_vol_scs_3rdventricle", "smri_vol_scs_4thventricle", "smri_vol_scs_bstem",
    "smri_vol_scs_hpuslh", "smri_vol_scs_amygdalalh", "smri_vol_scs_csf",
    "smri_vol_scs_lesionlh", "smri_vol_scs_aal", "smri_vol_scs_vedclh",
    
    "smri_vol_scs_cbwmatterrh", "smri_vol_scs_ltventriclerh", "smri_vol_scs_inflatventrh",
    "smri_vol_scs_crbwmatterrh", "smri_vol_scs_crbcortexrh", "smri_vol_scs_tprh",
    "smri_vol_scs_caudaterh", "smri_vol_scs_putamenrh", "smri_vol_scs_pallidumrh",
    "smri_vol_scs_hpusrh", "smri_vol_scs_amygdalarh", "smri_vol_scs_lesionrh",
    "smri_vol_scs_aar", "smri_vol_scs_vedcrh", 
    
    "smri_vol_scs_wmhint",
    "smri_vol_scs_wmhintlh", "smri_vol_scs_wmhintrh", 
    
    "smri_vol_scs_ccps",
    "smri_vol_scs_ccmidps", "smri_vol_scs_ccct", "smri_vol_scs_ccmidat",
    "smri_vol_scs_ccat", 
    
    "smri_vol_scs_wholeb", "smri_vol_scs_latventricles",
    "smri_vol_scs_allventricles", "smri_vol_scs_intracranialv", "smri_vol_scs_suprateialv",
    "smri_vol_scs_subcorticalgv",
    
    "smri_vol_cdk_banksstslh", "smri_vol_cdk_cdacatelh", "smri_vol_cdk_cdmdfrlh",
    "smri_vol_cdk_cuneuslh", "smri_vol_cdk_ehinallh", "smri_vol_cdk_fusiformlh",
    "smri_vol_cdk_ifpllh", "smri_vol_cdk_iftmlh", "smri_vol_cdk_ihcatelh",
    "smri_vol_cdk_locclh", "smri_vol_cdk_lobfrlh", "smri_vol_cdk_linguallh",
    "smri_vol_cdk_mobfrlh", "smri_vol_cdk_mdtmlh", "smri_vol_cdk_parahpallh",
    "smri_vol_cdk_paracnlh", "smri_vol_cdk_parsopclh", "smri_vol_cdk_parsobislh",
    "smri_vol_cdk_parstgrislh", "smri_vol_cdk_pericclh", "smri_vol_cdk_postcnlh",
    "smri_vol_cdk_ptcatelh", "smri_vol_cdk_precnlh", "smri_vol_cdk_pclh",
    "smri_vol_cdk_rracatelh", "smri_vol_cdk_rrmdfrlh", "smri_vol_cdk_sufrlh",
    "smri_vol_cdk_supllh", "smri_vol_cdk_sutmlh", "smri_vol_cdk_smlh",
    "smri_vol_cdk_frpolelh", "smri_vol_cdk_tmpolelh", "smri_vol_cdk_trvtmlh",
    "smri_vol_cdk_insulalh",
    
     "smri_vol_cdk_banksstsrh", "smri_vol_cdk_cdacaterh", "smri_vol_cdk_cdmdfrrh",
    "smri_vol_cdk_cuneusrh", "smri_vol_cdk_ehinalrh", "smri_vol_cdk_fusiformrh",
    "smri_vol_cdk_ifplrh", "smri_vol_cdk_iftmrh", "smri_vol_cdk_ihcaterh",
    "smri_vol_cdk_loccrh", "smri_vol_cdk_lobfrrh", "smri_vol_cdk_lingualrh",
    "smri_vol_cdk_mobfrrh", "smri_vol_cdk_mdtmrh", "smri_vol_cdk_parahpalrh",
    "smri_vol_cdk_paracnrh", "smri_vol_cdk_parsopcrh", "smri_vol_cdk_parsobisrh",
    "smri_vol_cdk_parstgrisrh", "smri_vol_cdk_periccrh", "smri_vol_cdk_postcnrh",
    "smri_vol_cdk_ptcaterh", "smri_vol_cdk_precnrh", "smri_vol_cdk_pcrh",
    "smri_vol_cdk_rracaterh", "smri_vol_cdk_rrmdfrrh", "smri_vol_cdk_sufrrh",
    "smri_vol_cdk_suplrh", "smri_vol_cdk_sutmrh", "smri_vol_cdk_smrh",
    "smri_vol_cdk_frpolerh", "smri_vol_cdk_tmpolerh", "smri_vol_cdk_trvtmrh",
    "smri_vol_cdk_insularh"
  ),
  region_name = c(
    "Left-Cerebral_Cortex", "Right-Cerebral-Cortex", "Total-Cerebral-Cortex",
    "Total_Cerebral-WM", "Total_Cerebellum-WM", "Total-Cerebellum-Cortex",
    
    "Left-Cerebral-White-Matter", "Left-Lateral-Ventricle", "Left-Inf-Lat-Vent",
    "Left-Cerebellum-White-Matter", "Left-Cerebellum-Cortex", "Left-Thalamus-Proper",
    "Left-Caudate-Nucleus", "Left-Putamen", "Left-Pallidum",
    "x3rd-ventricle", "x4th-ventricle", "Brain-Stem",
    "Left-Hippocampus", "Left-Amygdala", "Cerebrospinal-Fluid",
    "Left-Lesion", "Left-Accumbens-Area", "Left-VentralDC",
    
   "Right-Cerebral-White-Matter", "Right-Lateral-Ventricle", "Right-Inf-Lat-Vent",
    "Right-Cerebellum-White-Matter", "Right-Cerebellum-Cortex", "Right-Thalamus-Proper",
    "Right-Caudate-Nucleus", "Right-Putamen", "Right-Pallidum",
    "Right-Hippocampus", "Right-Amygdala",
    "Right-Lesion", "Right-Accumbens-Area", "Right-VentralDC",
    
    "WM-Hypointensities","Left-WM-Hypointensities", "Right-WM-Hypointensities",
   
   "CC_Posterior","CC_Mid_Posterior", "CC_Central", "CC_Mid_Anterior",
    "CC_Anterior", 
   
   "WholeBrain", "LatVentricles","AllVentricles", "IntracranialVolume", 
   "SupratentorialVolume", "SubcorticalGrayVolume",
   
     "lh_bankssts", "lh_caudalanteriorcingulate", "lh_caudalmiddlefrontal",
    "lh_cuneus", "lh_entorhinal", "lh_fusiform",
    "lh_inferiorparietal", "lh_inferiortemporal", "lh_isthmuscingulate",
    "lh_lateraloccipital", "lh_lateralorbitofrontal", "lh_lingual",
    "lh_medialorbitofrontal", "lh_middletemporal", "lh_parahippocampal",
    "lh_paracentral", "lh_parsopercularis", "lh_parsorbitalis",
    "lh_parstriangularis", "lh_pericalcarine", "lh_postcentral",
    "lh_posteriorcingulate", "lh_precentral", "lh_precuneus", "lh_rostralanteriorcingulate",
    "lh_rostralmiddlefrontal", "lh_superiorfrontal", "lh_superiorparietal",
    "lh_superiortemporal", "lh_supramarginal", "lh_frontalpole",
    "lh_temporalpole", "lh_transversetemporal", "lh_insula",
   
     "rh_bankssts", "rh_caudalanteriorcingulate", "rh_caudalmiddlefrontal",
    "rh_cuneus", "rh_entorhinal", "rh_fusiform",
    "rh_inferiorparietal", "rh_inferiortemporal", "rh_isthmuscingulate",
    "rh_lateraloccipital", "rh_lateralorbitofrontal", "rh_lingual",
    "rh_medialorbitofrontal", "rh_middletemporal", "rh_parahippocampal",
    "rh_paracentral", "rh_parsopercularis", "rh_parsorbitalis",
    "rh_parstriangularis", "rh_pericalcarine", "rh_postcentral",
    "rh_posteriorcingulate", "rh_precentral", "rh_precuneus", "rh_rostralanteriorcingulate",
    "rh_rostralmiddlefrontal", "rh_superiorfrontal", "rh_superiorparietal",
    "rh_superiortemporal", "rh_supramarginal", "rh_frontalpole",
    "rh_temporalpole", "rh_transversetemporal", "rh_insula"
    )
)
```

#GENERATE Models
```{r}
if (generate==TRUE) {
family_set <- c("GG", "BCTo", "BCT", "BCCG", "BCCGo")

#define phenotype set as all phenotypes at timepoint 2
phenotype_set <- c("smri_vol_cdk_total", "totalWM_cb","smri_vol_scs_subcorticalgv", "smri_vol_scs_allventricles", "smri_vol_scs_wholeb")  %>%
  paste0(.,".t2")

out_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_long_family/"

mu_terms = c("~1", "PCW_between_t1t2", "random(site)", "age", "sex", "nonSingleton")
sigma_terms = c("~1", "age", "sex")
nu_terms = c("~1", "sex")
tau_terms = c("~1")

generate_gamlss_models(phenotype_set = phenotype_set,
                       out_folder = out_folder,
                       family_set = family_set,
                       mu_terms = mu_terms,
                       sigma_terms = sigma_terms,
                       nu_terms = nu_terms,
                       tau_terms = tau_terms,
                       n_crit = 200,
                       long = TRUE, 
                       fixed_terms = TRUE)
}
```

Run fits submitting an array job.
running on both splits (full sample)
sbatch array_script_submit.sh submit_gamlss_fits_ABCD.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_long_family "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_long_family/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_full.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_family/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_family/gamlss_fits_stats"



split 2
sbatch array_script_submit.sh submit_gamlss_fits_ABCD_TWO.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t2_all "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t2_all/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sTwo_train.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_t2_all_TWO/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_t2_all_TWO/gamlss_fits_stats"


#Load data
##Dataframe with data
```{r}
data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_full.csv"

#read in the dataframe
#subset for age (PCW at scan) not being NA (will be NA is gestAge was NA, should be N = 66)
#subset for nonSingleton not being NA(will be NA if the parent questionnaire was NA, should be N = 2 for baseline)
#subset for sex %in% M or F, so no I in the model (should be N = 3 for I for baseline )
df_full <- read.csv(data_filename) %>% select(-1) %>% subset( !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))
df_full$sex <- as.factor(df_full$sex)
df_full$site <- as.factor(df_full$site) 
df_full$age <- as.numeric(df_full$age)
```

##Dataframe with fit stats
```{r}
#path for linear model with site as fixed variable
fits_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_family/"
fits_stats_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_family/gamlss_fits_stats_all.csv"
fits <- inspect_model_fits(fits_folder, fits_stats_filename) %>% arrange(phenotype) %>% arrange(family)
table(fits[which(fits$convergence_warn_end == 1),"family_abbr"])
```
##Load all fitted models
```{r}
models_list <- paste0(fits_folder,"gamlssFIT_",fits[which(fits$error == FALSE),"model_index"],".rds")
models <- lapply(models_list, readRDS)
```
#Diagnostics
## Worm Plots, By Distribution Family
```{r}
if(diagnostics == TRUE){
plot <- TRUE
plots_wp <- vector(mode = "list", length = length(models))
for (i  in 1:length(models)) {
  model <- models[[i]]
  family <- as.character(model$family[1])
  phenotype <- as.character(model$mu.terms[[2]])
  title <- name_mapping$region_name[match(sub(".t2", "",phenotype), name_mapping$abbreviation)]
  ph.t1 <- sub(".t2", ".t1", phenotype)
      df <- df_full %>% 
        select(sex, age, site, nonSingleton, PCW_between_t1t2, phenotype, ph.t1) %>% 
        drop_na()
      plots_wp[[i]] <- wp.taki(model, xlim.worm = 4) + labs(title = paste(family,title, sep = "_"))
    }

if (plot == TRUE){
n <- length(plots_wp)
nCol <- min(c(floor(sqrt(n)), 5))
nRow <- min(ceiling(n/nCol), 1)
breaks <- c(seq(from = 0, to = n , by = (nCol*nRow)))
if(!(n %in% breaks)){
  breaks <- c(breaks, n)
}
print(breaks)
for(k in 1:length(breaks)){
  start <- breaks[k] + 1
  end <- breaks[k+1]
  do.call("grid.arrange", c(plots_wp[start:end], ncol=nCol))
}
}
}
```
## BCT worm plots by sex
```{r}
if(diagnostics == TRUE){
plot <- TRUE
plots_wp_sexBCT <- vector(mode = "list", length = 5)
for (i  in 1:5) {
  model <- models[[i]]
  family <- as.character(model$family[1])
  phenotype <- as.character(model$mu.terms[[2]])
  title <- name_mapping$region_name[match(sub(".t2", "",phenotype), name_mapping$abbreviation)]
  ph.t1 <- sub(".t2", ".t1", phenotype)
      df <- df_full %>% 
        select(sex, age, site, nonSingleton, PCW_between_t1t2, phenotype, ph.t1) %>% 
        drop_na()
      plots_wp_sexBCT[[i]] <- wp.taki(model, xlim.worm = 4, xvar = df$sex) + labs(title = paste(family,title, sep = "_"))
    }

if (plot == TRUE){
n <- length(plots_wp_sexBCT)
nCol <- 1
nRow <- 2
breaks <- c(seq(from = 0, to = n , by = (nCol*nRow)))
if(!(n %in% breaks)){
  breaks <- c(breaks, n)
}
print(breaks)
for(k in 1:length(breaks)){
  start <- breaks[k] + 1
  end <- breaks[k+1]
  do.call("grid.arrange", c(plots_wp_sexBCT[start:end], ncol=nCol))
}
}
}
```

## BCT worm plots by age
```{r}
if(diagnostics == TRUE){
plot <- TRUE
plots_wp_ageBCT <- vector(mode = "list", length = 5)
for (i  in 1:5) {
  model <- models[[i]]
  family <- as.character(model$family[1])
  phenotype <- as.character(model$mu.terms[[2]])
  title <- name_mapping$region_name[match(sub(".t2", "",phenotype), name_mapping$abbreviation)]
  ph.t1 <- sub(".t2", ".t1", phenotype)
      df <- df_full %>% 
        select(age, age, site, nonSingleton, PCW_between_t1t2, phenotype, ph.t1) %>% 
        drop_na()
      plots_wp_ageBCT[[i]] <- wp.taki(model, xlim.worm = 4, xvar = df$age) + labs(title = paste(family,title, sep = "_"))
    }

if (plot == TRUE){
n <- length(plots_wp_ageBCT)
nCol <- 1
nRow <- 2
breaks <- c(seq(from = 0, to = n , by = (nCol*nRow)))
if(!(n %in% breaks)){
  breaks <- c(breaks, n)
}
print(breaks)
for(k in 1:length(breaks)){
  start <- breaks[k] + 1
  end <- breaks[k+1]
  do.call("grid.arrange", c(plots_wp_ageBCT[start:end], ncol=nCol))
}
}
}
```

##BIC plots 
for all phenotypes. Both converged and non-converged models, indicated by fill color.
```{r}
if(diagnostics == TRUE){
#BIC_WMV <- 
  fits %>% filter(phenotype == "totalWM_cb.t2" & error == 0) %>% 
  ggplot(., aes(x = log(BIC - min(BIC)), y = family_abbr, fill = convergence_warn_end)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("WMV, all") + labs(x = "scaled log BIC", y = "Distribution family")

#BIC_GMV <- 
  fits %>% filter(phenotype == "smri_vol_cdk_total.t2" & error == 0) %>% 
  ggplot(., aes(x = log(BIC -min(BIC)), y = family_abbr, fill = convergence_warn_end)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("cort GMV, all") + labs(x = "scaled log BIC", y = "Distribution family")

#BIC_scGMV <- 
  fits %>% filter(phenotype == "smri_vol_scs_subcorticalgv.t2" & error == 0) %>% 
  ggplot(., aes(x = log(BIC -min(BIC)), y = family_abbr, fill = convergence_warn_end)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("subcort GMV, all") + labs(x = "scaled log BIC", y = "Distribution family")

#BIC_Vent <- 
  fits %>% filter(phenotype == "smri_vol_scs_allventricles.t2" & error == 0) %>% 
  ggplot(., aes(x = log(BIC -min(BIC)), y = family_abbr, fill = convergence_warn_end)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Ventricles, all") + labs(x = "scaled log BIC", y = "Distribution family")

#BIC_wholeB <- 
  fits %>% filter(phenotype == "smri_vol_scs_wholeb.t2" & error == 0) %>% 
  ggplot(., aes(x = log(BIC -min(BIC)), y = family_abbr, fill = convergence_warn_end)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Whole Brain, all") + labs(x = "scaled log BIC", y = "Distribution family")
}
```
##cent-cdf
Only applied to BCT models right now.
```{r}
if(diagnostics == TRUE){
print <- TRUE

centcdf <- setNames(data.frame(matrix(ncol = 3, nrow = length(models))), c("ph","family", "cdfcor"))
cdf_expected <- c(0.01, 0.05, 0.10, 0.25, 0.50, 0.75, 0.90, 0.95, 0.99)

for(i in 1:length(models)){
#define models from split one and split two
model <- models[[i]]
family <- as.character(model$family[1])
ph <- as.character(model$mu.formula[[2]])
ph.t1 <- ph %>% gsub(".t2", ".t1", .)
title <- name_mapping$region_name[match(sub(".t2", "",ph), name_mapping$abbreviation)]

#define original df from split one and two, with phenotypes from the current model
og_df <- df_full %>% select(all_of(c("age", "sex", "nonSingleton", "site", "PCW_between_t1t2", ph, ph.t1)))

#calculate predicted centiles distribution for sOne models, using sOne train dataset and sTwo test dataset
#save correlation with expected cdf values
out <- suppressMessages(cent_cdf(model, og_df))$data$fitted
centcdf$ph[i] <- title
centcdf$family[i] <- family
centcdf$cdfcor[i] <- (cor.test(as.numeric(out), cdf_expected)$estimate)


if (print == TRUE){
print(paste0("Correlation Coefficient ", family, title, centcdf$cdfcor[i]))
}
}
}
```

#Centile Plots - adapted but seems to be off
```{r}
model <- models[[5]]
df <- df_full %>% 
        select(sex, age, site, nonSingleton, PCW_between_t1t2, totalWM_cb.t2, totalWM_cb.t1) %>% 
        drop_na()
make_centile_fan(model, df, "age","sex", desiredCentiles = c(0.05, 0.5, 0.95), remove_cent_effect = "totalWM_cb.t1", show_points = FALSE) + labs(title = "Total WM", x = "Age", color = "Sex=Female", fill="Sex=Female")

model <- models[[2]]
df <- df_full %>% 
        select(sex, age, site, nonSingleton, PCW_between_t1t2, smri_vol_scs_allventricles.t2, smri_vol_scs_allventricles.t1) %>% 
        drop_na()
make_centile_fan(model, df, "age","sex", desiredCentiles = c(0.05, 0.5, 0.95), remove_cent_effect = "smri_scs_allventricles.t1", show_points = FALSE) + labs(title = "Ventricles", x = "Age", color = "Sex=Female", fill="Sex=Female")

```
Get centile plots to see the shape of the different models
- 2:5 to avoid cortical gray matter which currently I can't model (because it is negative when resid. effect of t1)
- show_points = FALSE, because I can't residualize the points out (error in the predict function)
- The for loop here does not work with ph.t1 unfortunately - and I don't know why.
##trying to plot centile plot with model ran in the same environment -- currently not working, some error.
```{r}
model <- models[[5]]
df <- df_full %>% 
        select(sex, age, site, nonSingleton, PCW_between_t1t2, totalWM_cb.t2, totalWM_cb.t1) %>% 
        drop_na()
model <- gamlss(formula = totalWM_cb.t2 ~ totalWM_cb.t1 + age + sex + random(site) + PCW_between_t1t2 + nonSingleton,
                  sigma.formula =  ~ age + sex,
                  nu.formula = ~ sex,
                  tau.formula =  ~ 1,
                  family = BCT,
                  method = RS(),
                  data = df,
                  control = gamlss.control(n.cyc = 200))

make_centile_fan(model, df, "age","sex",  remove_point_effect = "totalWM_cb.t1", desiredCentiles = c(0.05, 0.5, 0.95))

+ labs(title = "Total WM", x = "Age", color = "Sex=Female", fill="Sex=Female")

predict(model, what = "mu", type = "terms", data = df, newdata = df)
```
##Looping through the models
```{r}
plot = TRUE
plot_models <- models[2:5]
plots <- vector(mode = "list", length = length(plot_models))

for (i in 1:length(plot_models)) {
  model = plot_models[[i]]
  print(model$mu.formula)
  phenotype <- as.character(plot_models[[i]]$mu.terms[[2]])
  title <- name_mapping$region_name[match(sub(".t2", "",phenotype), name_mapping$abbreviation)]
  ph.t1 <- sub(".t2", ".t1", phenotype)
      df <- df_full %>% 
        select(sex, age, site, nonSingleton, PCW_between_t1t2, phenotype, ph.t1) %>% 
        drop_na()
  plots[[i]] <- make_centile_fan(model, df, "age","sex", desiredCentiles = c(0.05, 0.5, 0.95), remove_point_effect = ph.t1) + labs(title = title, x = "Age", color = "Sex=Female", fill="Sex=Female")
}

if (plot == TRUE){
n <- length(plots)
nCol <- 1
nRow <- 2
breaks <- c(seq(from = 0, to = n , by = (nCol*nRow)))
if(!(n %in% breaks)){
  breaks <- c(breaks, n)
}
print(breaks)
for(k in 1:length(breaks)){
  start <- breaks[k] + 1
  end <- breaks[k+1]
  do.call("grid.arrange", c(plots[start:end], ncol=nCol))
}
}
```


##Looping through the models - t2 vs t1 
```{r}
plot = TRUE
plot_models <- models[1:5]
plots <- vector(mode = "list", length = length(plot_models))

for (i in 1:length(plot_models)) {
  model = plot_models[[i]]
  print(model$mu.formula)
  phenotype <- as.character(plot_models[[i]]$mu.terms[[2]])
  title <- name_mapping$region_name[match(sub(".t2", "",phenotype), name_mapping$abbreviation)]
  ph.t1 <- sub(".t2", ".t1", phenotype)
      df <- df_full %>% 
        select(sex, age, site, nonSingleton, PCW_between_t1t2, phenotype, ph.t1) %>% 
        drop_na()
  plots[[i]] <- make_centile_fan(model, df, ph.t1 ,"sex", desiredCentiles = c(0.05, 0.5, 0.95)) + labs(title = title, x = "timepoint 1", y = "timepoint 2", color = "Sex=Female", fill="Sex=Female")
}

if (plot == TRUE){
n <- length(plots)
nCol <- 1
nRow <- 2
breaks <- c(seq(from = 0, to = n , by = (nCol*nRow)))
if(!(n %in% breaks)){
  breaks <- c(breaks, n)
}
print(breaks)
for(k in 1:length(breaks)){
  start <- breaks[k] + 1
  end <- breaks[k+1]
  do.call("grid.arrange", c(plots[start:end], ncol=nCol))
}
}
```
##Looping through the models - t2 vs t1, age effect removed from centile curves

```{r}
plot = TRUE
plot_models <- models[1:5]
plots <- vector(mode = "list", length = length(plot_models))

for (i in 1:length(plot_models)) {
  model = plot_models[[i]]
  print(model$mu.formula)
  phenotype <- as.character(plot_models[[i]]$mu.terms[[2]])
  title <- name_mapping$region_name[match(sub(".t2", "",phenotype), name_mapping$abbreviation)]
  ph.t1 <- sub(".t2", ".t1", phenotype)
      df <- df_full %>% 
        select(sex, age, site, nonSingleton, PCW_between_t1t2, phenotype, ph.t1) %>% 
        drop_na()
  plots[[i]] <- make_centile_fan(model, df, ph.t1 ,"sex", desiredCentiles = c(0.05, 0.5, 0.95), remove_cent_effect = "age") + labs(title = title, x = "timepoint 1", y = "timepoint 2", color = "Sex=Female", fill="Sex=Female")
}

if (plot == TRUE){
n <- length(plots)
nCol <- 1
nRow <- 2
breaks <- c(seq(from = 0, to = n , by = (nCol*nRow)))
if(!(n %in% breaks)){
  breaks <- c(breaks, n)
}
print(breaks)
for(k in 1:length(breaks)){
  start <- breaks[k] + 1
  end <- breaks[k+1]
  do.call("grid.arrange", c(plots[start:end], ncol=nCol))
}
}
```
#Predict centiles
##Calculate centiles for each model
```{r}
centiles <- vector(mode = "list", length = length(models))

for(i in 1:length(models)){
#define models from split one and split two
model <- models[[i]]
family <- as.character(model$family[1])
ph <- model$mu.formula[[2]]
ph.t1 <- ph %>% gsub(".t2", ".t1", .)
title <- name_mapping$region_name[match(sub(".t2", "",ph), name_mapping$abbreviation)]
ph.t1 <- sub(".t2", ".t1", ph)
#define df, with phenotypes from the current model
df <- df_full %>% 
        select(sex, age, site, nonSingleton, PCW_between_t1t2, ph, ph.t1) %>% 
        drop_na()

#calculate predicted centiles on sOne and sTwo data using sOne model
centiles[[i]] <- suppressMessages(pred_og_centile(model, df))
names(centiles)[i] <- paste(family, ph, "centiles", sep = "_")
}
```
##Save centiles
Save in single dataframe with columns for participant ID and split ID
```{r}
centiles <- cbind(df_full %>% select(src_subject_id), as.data.frame(centiles))

if (save_fits == TRUE){
output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Centile_CSVs/"
filename <- paste0(output_folder, "global_longmodel_volume_centiles.csv")
write.csv(centiles, filename)
}
```
#Refit whole brain and cortical GMV
- try to fix the discrepancy shown in the sex-specific worm plots.
##Whole Brain
```{r}
#define data frame with needed variables
ph <- "smri_vol_scs_wholeb"
model_variables <- c(paste0(ph, ".t2"), paste0(ph, ".t1"), "PCW_between_t1t2", "site", "age", "sex", "nonSingleton")
df <- df_full %>% select(all_of(model_variables))

#remove sex in Nu
bct_nu_NOsex <- gamlss (formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + ",paste0(ph, ".t1")," + PCW_between_t1t2 + age + sex + random(site) + nonSingleton")),
                  sigma.formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + age + sex")),
                  nu.formula = as.formula("~1"),
                  tau.formula = as.formula ("~1"),
                  family = "BCT",
                  method = RS(),
                  data = df,
                  control = gamlss.control(n.cyc = 200))

#inspect worm plots
wp.taki(bct_nu_NOsex, xlim.worm = 4)
wp.taki(bct_nu_NOsex, xlim.worm = 4, xvar = df$sex)

#add sex to tau
bct_tau_sex <- gamlss (formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + ",paste0(ph, ".t1")," + PCW_between_t1t2 + age + sex + random(site) + nonSingleton")),
                  sigma.formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + age + sex")),
                  nu.formula = as.formula("~1 + sex"),
                  tau.formula = as.formula ("~1 + sex"),
                  family = "BCT",
                  method = RS(),
                  data = df,
                  control = gamlss.control(n.cyc = 200))

#inspect worm plots
wp.taki(bct_tau_sex, xlim.worm = 4)
wp.taki(bct_tau_sex, xlim.worm = 4, xvar = df$sex)

#add age to Nu
bct_mu_sexage<- gamlss (formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + ",paste0(ph, ".t1")," + PCW_between_t1t2 + age + sex + sex:age + random(site) + nonSingleton")),
                  sigma.formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + age + sex")),
                  nu.formula = as.formula("~1 + sex"),
                  tau.formula = as.formula ("~1"),
                  family = "BCT",
                  method = RS(),
                  data = df,
                  control = gamlss.control(n.cyc = 200))

#inspect worm plots
wp.taki(bct_mu_sexage, xlim.worm = 4)
wp.taki(bct_mu_sexage, xlim.worm = 4, xvar = df$sex)
```

##Cortical GMV
```{r}
#define data frame with needed variables
ph <- "smri_vol_cdk_total"
model_variables <- c(paste0(ph, ".t2"), paste0(ph, ".t1"), "PCW_between_t1t2", "site", "age", "sex", "nonSingleton")
df <- df_full %>% select(all_of(model_variables))

#remove sex in Nu
bct_nu_NOsex <- gamlss (formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + ",paste0(ph, ".t1")," + PCW_between_t1t2 + age + sex + random(site) + nonSingleton")),
                  sigma.formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + age + sex")),
                  nu.formula = as.formula("~1"),
                  tau.formula = as.formula ("~1"),
                  family = "BCT",
                  method = RS(),
                  data = df,
                  control = gamlss.control(n.cyc = 200))

#inspect worm plots
wp.taki(bct_nu_NOsex, xlim.worm = 4)
wp.taki(bct_nu_NOsex, xlim.worm = 4, xvar = df$sex)

#add sex to tau
bct_tau_sex <- gamlss (formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + ",paste0(ph, ".t1")," + PCW_between_t1t2 + age + sex + random(site) + nonSingleton")),
                  sigma.formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + age + sex")),
                  nu.formula = as.formula("~1 + sex"),
                  tau.formula = as.formula ("~1 + sex"),
                  family = "BCT",
                  method = RS(),
                  data = df,
                  control = gamlss.control(n.cyc = 200))

#inspect worm plots
wp.taki(bct_tau_sex, xlim.worm = 4)
wp.taki(bct_tau_sex, xlim.worm = 4, xvar = df$sex)

#add age to Nu
bct_mu_sexage<- gamlss (formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + ",paste0(ph, ".t1")," + PCW_between_t1t2 + age + sex + sex:age + random(site) + nonSingleton")),
                  sigma.formula = as.formula(paste0(paste0(ph, ".t2"), " ~ 1 + age + sex")),
                  nu.formula = as.formula("~1 + sex"),
                  tau.formula = as.formula ("~1"),
                  family = "BCT",
                  method = RS(),
                  data = df,
                  control = gamlss.control(n.cyc = 200))

#inspect worm plots
wp.taki(bct_mu_sexage, xlim.worm = 4)
wp.taki(bct_mu_sexage, xlim.worm = 4, xvar = df$sex)
```
