---
title: "gamlss_visualization"
author: "Eren Kafadar"
date: "2024-10-04"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library(dplyr)
library(magrittr)
library(readr)
library(stringr)
library(ggplot2)
library(gamlss) #to fit model
require(gamlss.ggplots)
library(tidyr)
library(gamlssTools) #Margaret's package
library(gridExtra)
```

#Setup
##Define paths for data and fitted models
```{r}
#paths for CG method results
folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_allPhen_RS/"
fits_stats_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_allPhen_RS/gamlss_fits_stats_RS_all.csv"
train_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrain_selectVars_famfilter2024-10-04.csv"
test_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTest_selectVars_famfilter2024-10-04.csv"
phenotype_set <- readRDS("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/phenotype_set.rds")

source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/inspect_model_fits.R")
```
## Load data frames and clean them up
```{r}
#define the distribution family and phenotype and whether nonSingleton variable is there to define file name.
#rename some of the variables and select baseline scans
rename_vec <- c(age = "PCW_at_scan", sex = "sex_baseline", site = "site_id_l", nonSingleton = "nonSingleton")

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
train_df <- read.csv(train_data_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
train_df$sex <- as.factor(train_df$sex)
train_df$site <- as.factor(train_df$site)
train_df$age <- as.numeric(train_df$age)

test_df <- read.csv(test_data_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#5347 folks
test_df$sex <- as.factor(test_df$sex)
test_df$site <- as.factor(test_df$site)
test_df$age <- as.numeric(test_df$age)
```


##Load fitted model(s)
reading in models that fit GG and have nonSingleton variable only
```{r}
#fitted_paths <- list.files(path = folder, pattern = "\\.rds$", full.names = TRUE)
fitted_paths <- list.files(path = folder, pattern = "GG.*\\.rds$", full.names = TRUE)
all_models <- lapply(fitted_paths, readRDS)
```
#Check fits
Make a table of error messages, warnings etc
Phenotype set should not have included wmhint, those models gave errors: all wmhint models are deleted.
 
FOR the models with the RS() algorithm:
Fits that haven't been saved due to error:
[1] "Models: smri_vol_cdk_ptcaterh ~ 1 + ns(age, 2) + sex + nonSingleton +      random(site)__GG"
[2] "Models: smri_vol_cdk_sufrrh ~ 1 + ns(age, 2) + sex + nonSingleton + random(site)__GG"       
[3] "Models: smri_vol_cdk_sufrrh ~ 1 + ns(age, 2) + sex + random(site)__GG"                      
[4] "Models: smri_vol_scs_crbwmatterlh ~ 1 + ns(age, 2) + sex + random(site)__GG"

Fits that haven't converged:
[1] "smri_vol_cdk_rracaterh ~ 1 + ns(age, 2) + sex + nonSingleton +      random(site)"    
[2] "smri_vol_cdk_rracaterh ~ 1 + ns(age, 2) + sex + random(site)"                        
[3] "smri_vol_scs_allventricles ~ 1 + ns(age, 2) + sex + nonSingleton +      random(site)"
[4] "smri_vol_scs_allventricles ~ 1 + ns(age, 2) + sex + random(site)"                    
[5] "smri_vol_scs_latventricles ~ 1 + ns(age, 2) + sex + nonSingleton +      random(site)"
[6] "smri_vol_scs_latventricles ~ 1 + ns(age, 2) + sex + random(site)"                    
[7] "smri_vol_scs_ltventriclelh ~ 1 + ns(age, 2) + sex + nonSingleton +      random(site)"
[8] "smri_vol_scs_ltventriclelh ~ 1 + ns(age, 2) + sex + random(site)"                    
[9] "smri_vol_scs_ltventriclerh ~ 1 + ns(age, 2) + sex + random(site)" 


```{r}
fits <- inspect_model_fits(folder, fits_stats_filename)
not_converge <- all_models[sapply(all_models, function(x){x$converged == FALSE})]

# worm plots for fits that did not converge
wp_notconverge <- lapply(seq_along(not_converge), function(i){ print(Reduce(paste,deparse(not_converge[[i]]$mu.formula))); wp.taki(not_converge[[i]])})

# look at centiles for fits that did not converge
centile_notconverge_plots <- lapply(seq_along(not_converge), function(i){model = not_converge[[i]]; make_centile_fan(model, train_df, "age", "sex", desiredCentiles = c(0.05, 0.5, 0.95)) + labs(title = print(Reduce(paste,deparse(model$mu.formula))), x = "Age", y = model$mu.formula[[2]], color = "Sex=Female", fill="Sex=Female")})

centile_notconverge_plots <- vector(mode = "list", length = length(not_converge))

for (i in 1:length(not_converge)) {
  model = not_converge[[i]]
  centile_notconverge_plots[[i]] <- make_centile_fan(model, train_df, "age", "sex", desiredCentiles = c(0.05, 0.5, 0.95)) + labs(title = print(Reduce(paste,deparse(model$mu.formula))), x = "Age", y = model$mu.formula[[2]], color = "Sex=Female", fill="Sex=Female")
}

n <- length(not_converge)
nCol <- floor(sqrt(n))
do.call("grid.arrange", c(centile_notconverge_plots, ncol=nCol))
```


#Choose which model(s)
-- global volumes ends up including totallh and totalrh because of pattern matching. This is OK.
```{r}
global_phenotypes <- c("smri_vol_cdk_total", "totalWM_cb","smri_vol_scs_subcorticalgv",
                   "smri_vol_scs_allventricles","smri_vol_scs_wholeb","smri_vol_scs_intracranialv","smri_vol_scs_bstem")
global_models <- all_models[sapply(all_models, function(x){grepl(paste(global_phenotypes, collapse = "|"),x$mu.formula[[2]])})]
```

#Plots
##Diagnostic plots
Global phenotypes
```{r}
#Worm plots for global models
lapply(seq_along(global_models), function(i){ print(Reduce(paste,deparse(global_models[[i]]$mu.formula))); wp.taki(global_models[[i]]) + labs(title = print(Reduce(paste,deparse(global_models[[i]]$mu.formula))))})
#Centile plots for global models
lapply(seq_along(global_models), function(i, model = global_models[[i]]){make_centile_fan(model, train_df, "age", "sex", desiredCentiles = c(0.05, 0.5, 0.95)) + labs(title = print(Reduce(paste,deparse(global_models[[i]]$mu.formula))), x = "Age", y = global_models[[i]]$mu.formula[[2]], color = "Sex=Female", fill="Sex=Female")})
```

##Plot centiles on the test dataset
```{r}
#Centile plots for global models
lapply(seq_along(global_models), function(i, model = global_models[[i]]){make_centile_fan(model, test_df, "age", "sex", desiredCentiles = c(0.05, 0.5, 0.95)) + labs(title = print(Reduce(paste,deparse(global_models[[i]]$mu.formula))), x = "Age", y = global_models[[i]]$mu.formula[[2]], color = "Sex=Female", fill="Sex=Female")})
```


## Centile plots
I can't really make anything from the gamlss.ggplots package work :(
data frame needs to be identical to the one that was used to fit the model? doesn't seem to work with anything different ..... 
```{r}
make_centile_fan(model, train, "age")
#pe_param(model, "age") ##DOES NOT WORK!
#fitted_terms(model, parameter = "mu") ##ALSO DOES NOT WORK!
```

