---
title: "gamlss_visualization"
author: "Eren Kafadar"
date: "2024-10-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library(dplyr)
library(magrittr)
library(readr)
library(stringr)
library(ggplot2)
library(gamlss) #to fit model
require(gamlss.ggplots)
library(tidyr)
library(gamlssTools) #Margaret's package
```

#Setup
##Define paths for data and fitted models
```{r}
#paths for CG method results
folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_allPhen"
train_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrain_selectVars_famfilter2024-10-04.csv"
test_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTest_selectVars_famfilter2024-10-04.csv"
```
## Load data frames and clean them up
```{r}
#define the distribution family and phenotype and whether nonSingleton variable is there to define file name.
#rename some of the variables and select baseline scans
rename_vec <- c(age = "PCW_at_scan", sex = "sex_baseline", site = "site_id_l", nonSingleton = "nonSingleton")

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
train_df <- read.csv(train_data_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
train_df$sex <- as.factor(train_df$sex)
train_df$site <- as.factor(train_df$site)
train_df$age <- as.numeric(train_df$age)

test_df <- read.csv(test_data_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
test_df$sex <- as.factor(test_df$sex)
test_df$site <- as.factor(test_df$site)
test_df$age <- as.numeric(test_df$age)
```


##Load fitted model(s) and select the correct variables from the dataframes
reading in models that fit GG and have nonSingleton variable only
```{r}
#fitted_paths <- list.files(path = folder, pattern = "\\.rds$", full.names = TRUE)
fitted_paths <- list.files(path = folder, pattern = "GG.*\\.rds$", full.names = TRUE)
all_models <- lapply(fitted_paths, readRDS)
### for now define model as the first one in the list ### later this might be input if I make it into a loop or function.
model <- all_models[[2]]
###
print(paste(Reduce(paste, deparse(model$mu.formula)),model$fam, sep = "__"))
nonSingleton <- ifelse(sum(grepl("nonSingleton", as.character(model$mu.formula))) != 0, "nonSingleton", NA)
phenotype <- model$mu.formula[[2]]
#select variables for gamlss, including phenotype specified by the loaded model
train <- train_df %>% select(sex, age, site, nonSingleton, phenotype)
test <- test_df %>% select(sex, age, site, nonSingleton, phenotype)
```

#Plots
## Centile plots
I can't really make anything from the gamlss.ggplots package work :(
data frame needs to beidentical to the one that was used to fit the model? doesn't seem to work with anything different ..... 
```{r}
make_centile_fan(model, train, "age", "sex")
#pe_param(model, "age") ##DOES NOT WORK!
#fitted_terms(model, parameter = "mu") ##ALSO DOES NOT WORK!
```

##Diagnostic plots
```{r}
plot(model)
model_GAIC(all_models[[1]], all_models[[2]])
cohens_f2_local(all_models[[2]], all_models[[1]])
```
