---
  title: "model_selection_longitudinal"
author: "Eren Kafadar"
date: "2024-11-29"
output: html_document
---
  
``` {r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library(dplyr)
library(magrittr)
library(readr)
library(stringr)
library(ggplot2)
library(gamlss) #to fit model
require(gamlss.ggplots)
library(tidyr)
library(gamlssTools) #Margaret's package
library(gridExtra)

source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/inspect_model_fits.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/gamlss_functions_EK.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/data_functions.R")
```

#GENERATE Models
generate basic models without the first time point
``` {r}
family_set <- c("GG")
#smri_vol_cdk_total is for total cortical GM, this is from the Desikan parcellation. The rest are from Aseg parcellation. 
phenotype_set <- c("smri_vol_cdk_total.t2", "totalWM_cb.t2","smri_vol_scs_subcorticalgv.t2", "smri_vol_scs_allventricles.t2", "smri_vol_scs_wholeb.t2")

out_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2/"

terms_all = c("~1", "PCW_between_t1t2", "random(site)", "age", "sex", "nonSingleton")

generate_gamlss_models(phenotype_set, 
                       out_folder, 
                       family_set = family_set,
                       mu_terms = terms_all,
                       sigma_terms = terms_all,
                       nu_terms = terms_all,
                       tau_terms = NULL,
                       n_crit = 200,
                       long = TRUE)
```

** I edited the generate_gamlss_models function to handle longitudinal models, so this part is not needed anymore.
read in the models generated above,
save another version with the t1 phenotype added to the predictors (will produce 3 new models, with t1 phenotype added to mu, mu and sigma, mu and sigma and nu)
save these new versions
```{r}
models_list_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2/"
models_list <-  lapply(list.files(models_list_folder, pattern = "\\.rds$", full.names = TRUE),readRDS)

for(n in 1:length(models_list)){
model <- models_list[[n]]
ph.t1 <- model$phenotype %>% gsub(".t2", ".t1", .)
new_model_mu <- model
new_model_mu$mu.formula <- as.formula(paste(deparse(model$mu.formula),"+", ph.t1))
new_model_sigma <- model
new_model_sigma$mu.formula <- as.formula(paste(deparse(model$mu.formula),"+", ph.t1))
new_model_sigma$sigma.formula <- as.formula(paste(deparse(model$sigma.formula),"+", ph.t1))
new_model_nu <- model
new_model_nu$mu.formula <- as.formula(paste(deparse(model$mu.formula),"+", ph.t1))
new_model_nu$sigma.formula <- as.formula(paste(deparse(model$sigma.formula),"+", ph.t1))
new_model_nu$nu.formula <- as.formula(paste(deparse(model$nu.formula), "+",ph.t1))
#save three new models
mu_modelname <- paste("gamlss_model",
                     "MU", paste0("~1", ".t1.", paste(labels(terms(model$mu.formula)), collapse = ".")),
                     "SIGMA", paste("~1", paste(labels(terms(model$sigma.formula)), collapse = ".")),
                     "NU", paste("~1", paste(labels(terms(model$nu.formula)), collapse = ".")),
                    model$fam,
                    model$phenotype, sep = "_")
mu_filename <- paste0(models_list_folder,mu_modelname,".rds")
saveRDS(new_model_mu, file = mu_filename)
#
sigma_modelname <- paste("gamlss_model",
                     "MU", paste("~1", ".t1.",paste(labels(terms(model$mu.formula)), collapse = ".")),
                     "SIGMA", paste("~1", ".t1.",paste(labels(terms(model$sigma.formula)), collapse = ".")),
                     "NU", paste("~1", paste(labels(terms(model$nu.formula)), collapse = ".")),
                    model$fam,
                    model$phenotype, sep = "_")
sigma_filename <- paste0(models_list_folder,sigma_modelname,".rds")
saveRDS(new_model_sigma, file = sigma_filename)
#
nu_modelname <- paste("gamlss_model",
                     "MU", paste("~1", ".t1.",paste(labels(terms(model$mu.formula)), collapse = ".")),
                     "SIGMA", paste("~1", ".t1.",paste(labels(terms(model$sigma.formula)), collapse = ".")),
                     "NU", paste("~1", ".t1.",paste(labels(terms(model$nu.formula)), collapse = ".")),
                    model$fam,
                    model$phenotype, sep = "_")
nu_filename <- paste0(models_list_folder,nu_modelname,".rds")
saveRDS(new_model_nu, file = nu_filename)
#
rm(model, ph.t1, new_model_mu, new_model_sigma, new_model_nu, mu_filename, sigma_filename, nu_filename, mu_modelname, sigma_modelname, nu_modelname)
}

```


Run fits submitting an array job.
With the specifications below:

#Global fits GG, RS, model selection split 1
sbatch array_script_submit.sh submit_gamlss_fits_ABCD.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2 "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sOne_train.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_ONE/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_ONE/gamlss_fits_stats"

#Global fits GG, RS, model selection split 2
sbatch array_script_submit.sh submit_gamlss_fits_ABCD.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2 "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sTwo_train.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_TWO/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_TWO/gamlss_fits_stats"

#FITS ANALYSIS

##Define files
``` {r}
#file paths
splitOne_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_ONE/"
splitTwo_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_TWO/"
sOne_fits_stats_filename <- paste0(splitOne_folder, "gamlss_fits_stats_all.csv")
sTwo_fits_stats_filename <- paste0(splitTwo_folder, "gamlss_fits_stats_all.csv")
splitOne_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sOne_train.csv"
splitTwo_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sTwo_train.csv"
splitOne_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sOne_test.csv"
splitTwo_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sTwo_test.csv"
phenotype_set <- readRDS("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/phenotype_set.rds")
```
## Load data frames and clean them up
``` {r}
#define the distribution family and phenotype and whether nonSingleton variable is there to define file name.
#rename some of the variables and select baseline scans
#rename_vec <- c(age = "PCW_at_scan", sex = "sex_baseline", site = "site_id_l", nonSingleton = "nonSingleton")

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_df <- read.csv(splitOne_data_filename)  %>% select(-1) %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sOne_df$sex <- as.factor(sOne_df$sex)
sOne_df$site <- as.factor(sOne_df$site)
sOne_df$age <- as.numeric(sOne_df$age)

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_df <- read.csv(splitTwo_data_filename)  %>% select(-1) %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sTwo_df$sex <- as.factor(sTwo_df$sex)
sTwo_df$site <- as.factor(sTwo_df$site)
sTwo_df$age <- as.numeric(sTwo_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_test_df <- read.csv(splitOne_test_filename)  %>% select(-1)  %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sOne_test_df$sex <- as.factor(sOne_test_df$sex)
sOne_test_df$site <- as.factor(sOne_test_df$site)
sOne_test_df$age <- as.numeric(sOne_test_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_test_df <- read.csv(splitTwo_test_filename)  %>% select(-1) %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sTwo_test_df$sex <- as.factor(sTwo_test_df$sex)
sTwo_test_df$site <- as.factor(sTwo_test_df$site)
sTwo_test_df$age <- as.numeric(sTwo_test_df$age)
```
##Load fitted model(s)
reading in models fit to both split halves (separately)
``` {r}
sOne_models <- lapply(list.files(path = splitOne_folder, pattern = "\\.rds$", full.names = TRUE), readRDS)
sTwo_models <- lapply(list.files(path = splitTwo_folder, pattern = "\\.rds$", full.names = TRUE), readRDS)

#sOne_models <- lapply(list.files(path = splitOne_folder, pattern = "\\.RData$", full.names = TRUE), load)
#sTwo_models <- lapply(list.files(path = splitTwo_folder, pattern = "\\.RData$", full.names = TRUE), load)
```

#Check fits
Make a table of error messages, warnings etc
Phenotype set should not have included wmhint, those models gave errors: all wmhint models are deleted.
```{r}
sOne_fits <- inspect_model_fits(splitOne_folder, sOne_fits_stats_filename)
sOne_not_converge <- sOne_models[sapply(sOne_models, function(x){x$converged == FALSE})]

sTwo_fits <- inspect_model_fits(splitTwo_folder, sTwo_fits_stats_filename)
sTwo_not_converge <- sTwo_models[sapply(sTwo_models, function(x){x$converged == FALSE})]
```
workaround because the above inspect_model_fits fct doesn't work with the longitudinal model outputs
```{r}
sOne_fits <- read.csv(sOne_fits_stats_filename)
sOne_fits$modelFam <- paste(fits_stats$mu_formula, 
                             fits_stats$sigma_formula, 
                             fits_stats$nu_formula, 
                             fits_stats$family_abbr, sep = "__")
sOne_fits$phenotype <- as.character(lapply(sOne_fits$mu_formula, str_extract, pattern = ".*(?= ~)"))
```
#BIC
##BIC plots for each phenotype
sOne
```{r}
sOne_fits$ylabel <- paste("MU",gsub(".*~", "", sOne_fits$sigma_formula), "SIGMA", gsub(".*~", "", sOne_fits$sigma_formula), "NU", gsub(".*~", "", sOne_fits$nu_formula), sep = ".")

sOne_fits <- sOne_fits %>% 
  filter(!is.na(BIC)) %>%
  group_by(phenotype) %>%
  mutate(scaled_log_BIC = log(BIC - min(BIC)))

#RANK TOP 20 models and only plot those!!!
BIC_WMV <- 
  sOne_fits %>% filter(phenotype == "totalWM_cb.t2") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("WMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_GMV <- 
  sOne_fits %>% filter(phenotype == "smri_vol_cdk_total") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("cort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_scGMV <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_subcorticalgv") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("subcort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))


BIC_Vent <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_allventricles") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Ventricles, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_wholeB <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_wholeb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Whole Brain, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

```

sTwo
``` {r}
sTwo_fits$ylabel <- paste("MU",gsub(".*~", "", sTwo_fits$sigma_formula), "SIGMA", gsub(".*~", "", sTwo_fits$sigma_formula), "NU", gsub(".*~", "", sTwo_fits$nu_formula), sep = ".")

sTwo_fits <- sTwo_fits %>% 
  filter(!is.na(BIC)) %>%
  group_by(phenotype) %>%
  mutate(scaled_log_BIC = log(BIC - min(BIC)))

sTwo_BIC_WMV <- 
  sTwo_fits %>% filter(phenotype == "totalWM_cb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("WMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_GMV <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_cdk_total") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("cort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_scGMV <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_subcorticalgv") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("subcort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))


sTwo_BIC_Vent <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_allventricles") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Ventricles, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_wholeB <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_wholeb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Whole Brain, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

```
##get table of BIC within each phenotype
-- adapt code from family selection notebook
```{r}
sOne_best <- sOne_fits %>%
  group_by(phenotype) %>%
  slice_min(BIC, n = 1)

sTwo_best <- sTwo_fits %>%
  group_by(phenotype) %>%
  slice_min(BIC, n = 1)
```
