---
title: "model_selection"
author: "Eren Kafadar"
date: "2024-11-26"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library(dplyr)
library(magrittr)
library(readr)
library(stringr)
library(ggplot2)
library(gamlss) #to fit model
require(gamlss.ggplots)
library(tidyr)
library(gamlssTools) #Margaret's package
library(gridExtra)

source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/inspect_model_fits.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/gamlss_functions_EK.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/data_functions.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/pred_og_centile_EK.R")

#df to map variable names onto names displayed on figures
name_mapping <- data.frame(
variables = c("smri_vol_cdk_total","smri_vol_scs_allventricles","smri_vol_scs_subcorticalgv","smri_vol_scs_wholeb", "totalWM_cb"), 
labels = c("Cortical GMV", "Total Ventricular Volume", "Subcortical GMV", "Whole Brain Volume", "Total WMV"))
```

#GENERATE Models

```{r}
family_set <- c("GG")
#smri_vol_cdk_total is for total cortical GM, this is from the Desikan parcellation. The rest are from Aseg parcellation. 
phenotype_set <- c("smri_vol_cdk_total", "totalWM_cb","smri_vol_scs_subcorticalgv", "smri_vol_scs_allventricles", "smri_vol_scs_wholeb")
out_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_GG_global/"

terms_all = c("~1", "age", "sex", "random(site)", "nonSingleton")

generate_gamlss_models(phenotype_set, 
                                   out_folder, 
                                   family_set = family_set,
                                   mu_terms = terms_all,
                                   sigma_terms = terms_all,
                                   nu_terms = terms_all,
                                   tau_terms = NULL,
                                   n_crit = 200)
```

Run fits submitting an array job.
#Global fits GG, RS, model selection split 2
#sbatch array_script_submit.sh submit_gamlss_fits_ABCD.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_GG_global "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_GG_global/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrainTwo_selectVars_famfilter2024-11-26.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_GG_global_TWO/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_GG_global_TWO/gamlss_fits_stats"


#Global fits GG, RS, model selection split 1
#sbatch array_script_submit.sh submit_gamlss_fits_ABCD.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_GG_global "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_GG_global/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrainOne_selectVars_famfilter2024-11-26.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_GG_global_ONE/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_GG_global_ONE/gamlss_fits_stats"

#FITS ANALYSIS

##Define files
```{r}
#file paths
splitOne_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_GG_global_ONE/"
splitTwo_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_GG_global_TWO/"
sOne_fits_stats_filename <- paste0(splitOne_folder, "gamlss_fits_stats_all.csv")
sTwo_fits_stats_filename <- paste0(splitTwo_folder, "gamlss_fits_stats_all.csv")
splitOne_data_filename <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrainOne_selectVars_famfilter2024-11-26.csv"
# splitOne_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrain_selectVars_famfilter2024-10-04.csv"
splitTwo_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrainTwo_selectVars_famfilter2024-11-26.csv"
splitOne_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTestOne_selectVars_famfilter2024-11-26.csv"
splitTwo_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTestTwo_selectVars_famfilter2024-11-26.csv"
phenotype_set <- readRDS("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/phenotype_set.rds")
```
## Load data frames and clean them up
```{r}
#define the distribution family and phenotype and whether nonSingleton variable is there to define file name.
#rename some of the variables and select baseline scans
rename_vec <- c(age = "PCW_at_scan", sex = "sex_baseline", site = "site_id_l", nonSingleton = "nonSingleton")

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_df <- read.csv(splitOne_data_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sOne_df$sex <- as.factor(sOne_df$sex)
sOne_df$site <- as.factor(sOne_df$site)
sOne_df$age <- as.numeric(sOne_df$age)

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_df <- read.csv(splitTwo_data_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))
sTwo_df$sex <- as.factor(sTwo_df$sex)
sTwo_df$site <- as.factor(sTwo_df$site)
sTwo_df$age <- as.numeric(sTwo_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_test_df <- read.csv(splitOne_test_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))
sOne_test_df$sex <- as.factor(sOne_test_df$sex)
sOne_test_df$site <- as.factor(sOne_test_df$site)
sOne_test_df$age <- as.numeric(sOne_test_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_test_df <- read.csv(splitTwo_test_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))
sTwo_test_df$sex <- as.factor(sTwo_test_df$sex)
sTwo_test_df$site <- as.factor(sTwo_test_df$site)
sTwo_test_df$age <- as.numeric(sTwo_test_df$age)
```
##Load fitted model(s)
reading in models fit to both split halves (separately)
```{r}
sOne_models <- lapply(list.files(path = splitOne_folder, pattern = "\\.rds$", full.names = TRUE), readRDS)
sTwo_models <- lapply(list.files(path = splitTwo_folder, pattern = "\\.rds$", full.names = TRUE), readRDS)

#per discussion with Taki, remove the models that don't have random(site) in mu
sOne_models <- sOne_models[sapply(sOne_models, function(x){any(grepl("site",x$mu.terms))})]
sTwo_models <- sTwo_models[sapply(sTwo_models, function(x){any(grepl("site",x$mu.terms))})]
#sOne_models <- lapply(list.files(path = splitOne_folder, pattern = "\\.RData$", full.names = TRUE), load)
#sTwo_models <- lapply(list.files(path = splitTwo_folder, pattern = "\\.RData$", full.names = TRUE), load)
```

#Check fits
Make a table of error messages, warnings etc
Phenotype set should not have included wmhint, those models gave errors: all wmhint models are deleted.
```{r}
sOne_fits <- inspect_model_fits(splitOne_folder, sOne_fits_stats_filename)
sOne_not_converge <- sOne_models[sapply(sOne_models, function(x){x$converged == FALSE})]

sTwo_fits <- inspect_model_fits(splitTwo_folder, sTwo_fits_stats_filename)
sTwo_not_converge <- sTwo_models[sapply(sTwo_models, function(x){x$converged == FALSE})]

#per discussion with Taki, remove the models that don't have random(site) in mu
sOne_fits <- sOne_fits %>% filter(grepl("site", mu_formula))
sTwo_fits <- sTwo_fits %>% filter(grepl("site", mu_formula))
```

#BIC
##BIC plots for each phenotype
sOne
```{r}
sOne_fits$ylabel <- paste("MU",gsub(".*~", "", sOne_fits$mu_formula), "SIGMA", gsub(".*~", "", sOne_fits$sigma_formula), "NU", gsub(".*~", "", sOne_fits$nu_formula), sep = ".")
  
sOne_fits <- sOne_fits %>% 
  filter(!is.na(BIC)) %>%
  group_by(phenotype) %>%
  mutate(scaled_log_BIC = log(BIC - min(BIC)))

BIC_WMV <- 
  sOne_fits %>% filter(phenotype == "totalWM_cb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("WMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_GMV <- 
  sOne_fits %>% filter(phenotype == "smri_vol_cdk_total") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("cort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_scGMV <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_subcorticalgv") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("subcort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))


BIC_Vent <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_allventricles") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Ventricles, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_wholeB <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_wholeb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Whole Brain, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

```

sTwo
```{r}
sTwo_fits$ylabel <- paste("MU",gsub(".*~", "", sTwo_fits$mu_formula), "SIGMA", gsub(".*~", "", sTwo_fits$sigma_formula), "NU", gsub(".*~", "", sTwo_fits$nu_formula), sep = ".")
  
sTwo_fits <- sTwo_fits %>% 
  filter(!is.na(BIC)) %>%
  group_by(phenotype) %>%
  mutate(scaled_log_BIC = log(BIC - min(BIC)))

sTwo_BIC_WMV <- 
  sTwo_fits %>% filter(phenotype == "totalWM_cb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("WMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_GMV <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_cdk_total") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("cort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_scGMV <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_subcorticalgv") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("subcort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))


sTwo_BIC_Vent <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_allventricles") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Ventricles, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_wholeB <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_wholeb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Whole Brain, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

```
##get table of BIC within each phenotype
-- adapt code from family selection notebook
```{r}
sOne_best <- sOne_fits %>%
  group_by(phenotype) %>%
 slice_min(BIC, n = 1)

sTwo_best <- sTwo_fits %>%
  group_by(phenotype) %>%
  slice_min(BIC, n = 1)
```
#Plots
##Worm plots-Centile plots
get worm plots & centile plots for best BIC within each phenotype, for each split
```{r}
plot <- FALSE
plots_wp <- vector(mode = "list", length = dim(sOne_best)[1])
plots_cent <- vector(mode = "list", length = dim(sOne_best)[1])
best_models_One <- vector(mode = "list", length = dim(sOne_best)[1])
i = 0
titles <- c("Cortical GMV", "Total Ventricular Volume", "Subcortical GMV", "Whole Brain Volume", "Total WMV")
for (model in sOne_models) {
  #print(deparse(model$mu.formula))
  phenotype <- as.character(model$mu.terms[[2]])
  fit <- sOne_best[which(sOne_best$phenotype == phenotype),]
 # model <- sOne_models[[i]]
  if (identical(deparse(model$mu.formula), deparse(as.formula(fit$mu_formula))) &&
    identical(deparse(model$sigma.formula), deparse(as.formula(fit$sigma_formula))) &&
    identical(deparse(model$sigma.formula), deparse(as.formula(fit$sigma_formula)))) {
    i= i+1
    if (plot == TRUE){
      plots_wp[[i]] <- wp.taki(model) + labs(title = titles[i])
      
      #(title = eval(parse(text=paste0("plot_models[[i]]$",title_field))))
      df <- sOne_df %>% 
        select(sex, age, site, nonSingleton, phenotype) %>% 
        drop_na()
     plots_cent[[i]] <- make_centile_fan(model, df, "age", "sex", desiredCentiles = c(0.05, 0.5, 0.95)) + 
       labs(title = titles[i],x = "Age", y = NULL, color = "Sex=Female", fill="Sex=Female")
      }
   best_models_One[[i]] <- model
    }
}

if (plot == TRUE){
n <- length(plots_wp)
nCol <- floor(sqrt(n))
do.call("grid.arrange", c(plots_wp, ncol=nCol))
do.call("grid.arrange", c(plots_cent, ncol=3))
}

```

```{r}
plots_wp_two <- vector(mode = "list", length = dim(sTwo_best)[1])
plots_cent_two <- vector(mode = "list", length = dim(sTwo_best)[1])
best_models_Two <- vector(mode = "list", length = dim(sTwo_best)[1])
i = 0
titles <- c("Cortical GMV", "Total Ventricular Volume", "Subcortical GMV", "Whole Brain Volume", "Total WMV")
for (model in sTwo_models) {
  #print(deparse(model$mu.formula))
  phenotype <- as.character(model$mu.terms[[2]])
  fit <- sTwo_best[which(sOne_best$phenotype == phenotype),]
 # model <- sOne_models[[i]]
  if (identical(deparse(model$mu.formula), deparse(as.formula(fit$mu_formula))) &&
    identical(deparse(model$sigma.formula), deparse(as.formula(fit$sigma_formula))) &&
    identical(deparse(model$sigma.formula), deparse(as.formula(fit$sigma_formula)))) {
    i= i+1
    plots_wp_two[[i]] <- wp.taki(model) + labs(title = titles[i],                                                                               x = "Age", y = NULL, color = "Sex=Female", fill="Sex=Female")
    
    #(title = eval(parse(text=paste0("plot_models[[i]]$",title_field))))
    df <- sTwo_df %>% 
      select(sex, age, site, nonSingleton, phenotype) %>% 
      drop_na()
   plots_cent_two[[i]] <- make_centile_fan(model, df, "age", "sex", desiredCentiles = c(0.05, 0.5, 0.95)) + labs(title = titles[i],                                                                               x = "Age", y = NULL, color = "Sex=Female", fill="Sex=Female")
   best_models_Two[[i]] <- model
    }
}

n <- length(plots_wp_two)
nCol <- floor(sqrt(n))
do.call("grid.arrange", c(plots_wp_two, ncol=nCol))
do.call("grid.arrange", c(plots_cent_two, ncol=nCol))

```
##Predicting on test data
predict centile scores for split TWO using model trained on split ONE
```{r}
plot <- FALSE

centiles_pred_one <- vector(mode = "list", length = dim(sOne_best)[1])
centiles_pred_two <- vector(mode = "list", length = dim(sTwo_best)[1])

for(i in 1:length(best_models_One)){
#define models from split one and split two
model_one <- best_models_One[[i]]
model_two <- best_models_Two[[i]]

#define labels for phenotypes based on name_mapping df
title_one <- name_mapping$labels[name_mapping$variables == as.character(model_one$mu.formula[[2]])]
title_two <- name_mapping$labels[name_mapping$variables == as.character(model_two$mu.formula[[2]])]
stopifnot(title_one == title_two)

#define original df from split one and two, with phenotypes from the current model
og_df_one <- sOne_df %>% select(c("age", "sex", "nonSingleton", "site", model_one$mu.formula[[2]]))
og_df_two <- sTwo_df %>% select(c("age", "sex", "nonSingleton", "site", model_two$mu.formula[[2]]))

#calculate predicted centiles on sOne data using sOne and sTwo models
sOne_centiles_1 <- pred_og_centile_EK(model_one, sOne_df)
sOne_centiles_2 <- pred_og_centile_EK(model_two, og_df_two, new.data = sOne_df)
centiles_pred_one[[i]] <- pred_og_centile(model_two, og_df_two, new.data = sOne_test_df)
names(centiles_pred_one)[i] <- paste(title_one, "centiles", sep = "_")

#calculate predicted centiles on sTwo data using sOne and sTwo models
sTwo_centiles_1 <- pred_og_centile_EK(model_one, og_df_one, new.data = sTwo_df)
sTwo_centiles_2 <- pred_og_centile_EK(model_two, sTwo_df)
centiles_pred_two[[i]] <- pred_og_centile_EK(model_one, og_df_one, new.data = sTwo_test_df)
names(centiles_pred_two)[i] <- paste(title_two, "centiles", sep = "_")

if(plot == TRUE) {
  #Plotting sOne and sTwo from two predictions
  plot(sOne_centiles_1, sOne_centiles_2, main = paste0("split One: ", title_one) , ylab = "predictions from Model 1", xlab = "predictions from Model 2")
  abline(a = 0, b = 1, col = "red", lwd = 2, lty = 2)
  plot(sTwo_centiles_1, sTwo_centiles_2, main = paste0("split Two: ", title_two) , ylab = "predictions from Model 1", xlab = "predictions from Model 2")
  abline(a = 0, b = 1, col = "red", lwd = 2, lty = 2)
  }

#Correlation coefficients
cor_one <- cor.test(sOne_centiles_1, sOne_centiles_2)
cor_two <- cor.test(sTwo_centiles_1, sTwo_centiles_2)
print(paste0("Correlation Coefficient Split One, ", title_one, cor_one$estimate, " , ", cor_one$p.value))
print(paste0("Correlation Coefficient Split Two, ", title_two, cor_two$estimate, " , ", cor_two$p.value))
}
```

#Gestational Age
Look at the predicted centiles (from cross model?) per PTB, and per gestational age
```{r}
sOne_test_df <- cbind(sOne_test_df, as.data.frame(centiles_pred_one))
sTwo_test_df <- cbind(sTwo_test_df, as.data.frame(centiles_pred_two))
rm(centiles_pred_one, centiles_pred_two)

ggplot(sOne_test_df, aes(x = gestAge, y = Cortical.GMV_centiles, color = sex)) +
  geom_point() +
  theme_minimal()

#Correlations of centiles with gest Age
cor.test(sOne_test_df$Cortical.GMV_centiles, sOne_test_df$gestAge)
cor.test(sTwo_test_df$Cortical.GMV_centiles, sTwo_test_df$gestAge)

cor.test(sOne_test_df$Total.Ventricular.Volume_centiles, sOne_test_df$gestAge)
cor.test(sTwo_test_df$Total.Ventricular.Volume_centiles, sTwo_test_df$gestAge)

cor.test(sOne_test_df$Subcortical.GMV_centiles, sOne_test_df$gestAge)
cor.test(sTwo_test_df$Subcortical.GMV_centiles, sTwo_test_df$gestAge)

cor.test(sOne_test_df$Whole.Brain.Volume_centiles, sOne_test_df$gestAge)
cor.test(sTwo_test_df$Whole.Brain.Volume_centiles, sTwo_test_df$gestAge)

cor.test(sOne_test_df$Total.WMV_centiles, sOne_test_df$gestAge)
cor.test(sTwo_test_df$Total.WMV_centiles, sTwo_test_df$gestAge)
```

predict the phenotype
```{r}
predictor_list <- list_predictors(model)
newData <- subset(sTwo_df, select = names(sTwo_df) %in% predictor_list)
sTwo_preds <- predModel <- predictAll(model, newdata=newData, data=og_df, type= "response")
sTwo_smri_vol_cdk_total_resids <- sTwo_df$smri_vol_cdk_total - sTwo_preds$mu
#plot wp with the predicted residuals on the split half
wp.taki(xvar = sTwo_df$smri_vol_cdk_total, resid = sTwo_smri_vol_cdk_total_resids, n.inter = 1, ylim = 100)
wp.taki(model)
qqnorm(sTwo_smri_vol_cdk_total_resids, main = "QQ Plot of Residuals", pch = 19, col = "blue")
qqline(sTwo_smri_vol_cdk_total_resids, col = "red", lwd = 2)

```
