---
title: "model_selection_long_regional"
author: "Eren Kafadar"
date: "2025-01-27"
output: html_document
---
``` {r setup, include=FALSE}
diagnostics <- FALSE
generate <- FALSE
save_fits <- FALSE
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library(dplyr)
library(magrittr)
library(readr)
library(stringr)
library(ggplot2)
library(gamlss) #to fit model
require(gamlss.ggplots)
library(tidyr)
library(gamlssTools) #Margaret's package
library(gridExtra)

source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/inspect_model_fits.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/gamlss_functions_EK.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/data_functions.R")

phenotypes <- readRDS("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/phenotype_set.rds")

#df to map variable names onto names displayed on figures
name_mapping <- data.frame(
  abbreviation = c(
     "smri_vol_cdk_totallh", "smri_vol_cdk_totalrh", "smri_vol_cdk_total",   
     "totalWM_cb", "totalWM_crb", "totalGM_crb",
     
    "smri_vol_scs_cbwmatterlh", "smri_vol_scs_ltventriclelh", "smri_vol_scs_inflatventlh",
    "smri_vol_scs_crbwmatterlh", "smri_vol_scs_crbcortexlh", "smri_vol_scs_tplh",
    "smri_vol_scs_caudatelh", "smri_vol_scs_putamenlh", "smri_vol_scs_pallidumlh",
    "smri_vol_scs_3rdventricle", "smri_vol_scs_4thventricle", "smri_vol_scs_bstem",
    "smri_vol_scs_hpuslh", "smri_vol_scs_amygdalalh", "smri_vol_scs_csf",
    "smri_vol_scs_lesionlh", "smri_vol_scs_aal", "smri_vol_scs_vedclh",
    
    "smri_vol_scs_cbwmatterrh", "smri_vol_scs_ltventriclerh", "smri_vol_scs_inflatventrh",
    "smri_vol_scs_crbwmatterrh", "smri_vol_scs_crbcortexrh", "smri_vol_scs_tprh",
    "smri_vol_scs_caudaterh", "smri_vol_scs_putamenrh", "smri_vol_scs_pallidumrh",
    "smri_vol_scs_hpusrh", "smri_vol_scs_amygdalarh", "smri_vol_scs_lesionrh",
    "smri_vol_scs_aar", "smri_vol_scs_vedcrh", 
    
    "smri_vol_scs_wmhint",
    "smri_vol_scs_wmhintlh", "smri_vol_scs_wmhintrh", 
    
    "smri_vol_scs_ccps",
    "smri_vol_scs_ccmidps", "smri_vol_scs_ccct", "smri_vol_scs_ccmidat",
    "smri_vol_scs_ccat", 
    
    "smri_vol_scs_wholeb", "smri_vol_scs_latventricles",
    "smri_vol_scs_allventricles", "smri_vol_scs_intracranialv", "smri_vol_scs_suprateialv",
    "smri_vol_scs_subcorticalgv",
    
    "smri_vol_cdk_banksstslh", "smri_vol_cdk_cdacatelh", "smri_vol_cdk_cdmdfrlh",
    "smri_vol_cdk_cuneuslh", "smri_vol_cdk_ehinallh", "smri_vol_cdk_fusiformlh",
    "smri_vol_cdk_ifpllh", "smri_vol_cdk_iftmlh", "smri_vol_cdk_ihcatelh",
    "smri_vol_cdk_locclh", "smri_vol_cdk_lobfrlh", "smri_vol_cdk_linguallh",
    "smri_vol_cdk_mobfrlh", "smri_vol_cdk_mdtmlh", "smri_vol_cdk_parahpallh",
    "smri_vol_cdk_paracnlh", "smri_vol_cdk_parsopclh", "smri_vol_cdk_parsobislh",
    "smri_vol_cdk_parstgrislh", "smri_vol_cdk_pericclh", "smri_vol_cdk_postcnlh",
    "smri_vol_cdk_ptcatelh", "smri_vol_cdk_precnlh", "smri_vol_cdk_pclh",
    "smri_vol_cdk_rracatelh", "smri_vol_cdk_rrmdfrlh", "smri_vol_cdk_sufrlh",
    "smri_vol_cdk_supllh", "smri_vol_cdk_sutmlh", "smri_vol_cdk_smlh",
    "smri_vol_cdk_frpolelh", "smri_vol_cdk_tmpolelh", "smri_vol_cdk_trvtmlh",
    "smri_vol_cdk_insulalh",
    
     "smri_vol_cdk_banksstsrh", "smri_vol_cdk_cdacaterh", "smri_vol_cdk_cdmdfrrh",
    "smri_vol_cdk_cuneusrh", "smri_vol_cdk_ehinalrh", "smri_vol_cdk_fusiformrh",
    "smri_vol_cdk_ifplrh", "smri_vol_cdk_iftmrh", "smri_vol_cdk_ihcaterh",
    "smri_vol_cdk_loccrh", "smri_vol_cdk_lobfrrh", "smri_vol_cdk_lingualrh",
    "smri_vol_cdk_mobfrrh", "smri_vol_cdk_mdtmrh", "smri_vol_cdk_parahpalrh",
    "smri_vol_cdk_paracnrh", "smri_vol_cdk_parsopcrh", "smri_vol_cdk_parsobisrh",
    "smri_vol_cdk_parstgrisrh", "smri_vol_cdk_periccrh", "smri_vol_cdk_postcnrh",
    "smri_vol_cdk_ptcaterh", "smri_vol_cdk_precnrh", "smri_vol_cdk_pcrh",
    "smri_vol_cdk_rracaterh", "smri_vol_cdk_rrmdfrrh", "smri_vol_cdk_sufrrh",
    "smri_vol_cdk_suplrh", "smri_vol_cdk_sutmrh", "smri_vol_cdk_smrh",
    "smri_vol_cdk_frpolerh", "smri_vol_cdk_tmpolerh", "smri_vol_cdk_trvtmrh",
    "smri_vol_cdk_insularh"
  ),
  region_name = c(
    "Left-Cerebral_Cortex", "Right-Cerebral-Cortex", "Total-Cerebral-Cortex",
    "Total_Cerebral-WM", "Total_Cerebellum-WM", "Total-Cerebellum-Cortex",
    
    "Left-Cerebral-White-Matter", "Left-Lateral-Ventricle", "Left-Inf-Lat-Vent",
    "Left-Cerebellum-White-Matter", "Left-Cerebellum-Cortex", "Left-Thalamus-Proper",
    "Left-Caudate-Nucleus", "Left-Putamen", "Left-Pallidum",
    "x3rd-ventricle", "x4th-ventricle", "Brain-Stem",
    "Left-Hippocampus", "Left-Amygdala", "Cerebrospinal-Fluid",
    "Left-Lesion", "Left-Accumbens-Area", "Left-VentralDC",
    
   "Right-Cerebral-White-Matter", "Right-Lateral-Ventricle", "Right-Inf-Lat-Vent",
    "Right-Cerebellum-White-Matter", "Right-Cerebellum-Cortex", "Right-Thalamus-Proper",
    "Right-Caudate-Nucleus", "Right-Putamen", "Right-Pallidum",
    "Right-Hippocampus", "Right-Amygdala",
    "Right-Lesion", "Right-Accumbens-Area", "Right-VentralDC",
    
    "WM-Hypointensities","Left-WM-Hypointensities", "Right-WM-Hypointensities",
   
   "CC_Posterior","CC_Mid_Posterior", "CC_Central", "CC_Mid_Anterior",
    "CC_Anterior", 
   
   "WholeBrain", "LatVentricles","AllVentricles", "IntracranialVolume", 
   "SupratentorialVolume", "SubcorticalGrayVolume",
   
     "lh_bankssts", "lh_caudalanteriorcingulate", "lh_caudalmiddlefrontal",
    "lh_cuneus", "lh_entorhinal", "lh_fusiform",
    "lh_inferiorparietal", "lh_inferiortemporal", "lh_isthmuscingulate",
    "lh_lateraloccipital", "lh_lateralorbitofrontal", "lh_lingual",
    "lh_medialorbitofrontal", "lh_middletemporal", "lh_parahippocampal",
    "lh_paracentral", "lh_parsopercularis", "lh_parsorbitalis",
    "lh_parstriangularis", "lh_pericalcarine", "lh_postcentral",
    "lh_posteriorcingulate", "lh_precentral", "lh_precuneus", "lh_rostralanteriorcingulate",
    "lh_rostralmiddlefrontal", "lh_superiorfrontal", "lh_superiorparietal",
    "lh_superiortemporal", "lh_supramarginal", "lh_frontalpole",
    "lh_temporalpole", "lh_transversetemporal", "lh_insula",
   
     "rh_bankssts", "rh_caudalanteriorcingulate", "rh_caudalmiddlefrontal",
    "rh_cuneus", "rh_entorhinal", "rh_fusiform",
    "rh_inferiorparietal", "rh_inferiortemporal", "rh_isthmuscingulate",
    "rh_lateraloccipital", "rh_lateralorbitofrontal", "rh_lingual",
    "rh_medialorbitofrontal", "rh_middletemporal", "rh_parahippocampal",
    "rh_paracentral", "rh_parsopercularis", "rh_parsorbitalis",
    "rh_parstriangularis", "rh_pericalcarine", "rh_postcentral",
    "rh_posteriorcingulate", "rh_precentral", "rh_precuneus", "rh_rostralanteriorcingulate",
    "rh_rostralmiddlefrontal", "rh_superiorfrontal", "rh_superiorparietal",
    "rh_superiortemporal", "rh_supramarginal", "rh_frontalpole",
    "rh_temporalpole", "rh_transversetemporal", "rh_insula"
    )
)
```

#GENERATE Models
generate models including the first time point
``` {r}
if (generate == TRUE){
family_set <- c("GG")
#smri_vol_cdk_total is for total cortical GM, this is from the Desikan parcellation. The rest are from Aseg parcellation.
phenotype_set <- phenotypes %>%
  paste0(.,".t2") %>% setdiff(c("smri_vol_cdk_total.t2", "totalWM_cb.t2","smri_vol_scs_subcorticalgv.t2", "smri_vol_scs_allventricles.t2", "smri_vol_scs_wholeb.t2"))

out_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_long_regional/"

terms_all = c("~1", "PCW_between_t1t2", "random(site)", "age", "sex", "nonSingleton")

generate_gamlss_models(phenotype_set = phenotype_set,
                       out_folder = out_folder,
                       family_set = family_set,
                       mu_terms = terms_all,
                       sigma_terms = terms_all,
                       nu_terms = terms_all,
                       tau_terms = NULL,
                       n_crit = 200,
                       long = TRUE)
}
```

Run fits submitting an array job.
With the specifications below:

split 1
sbatch array_script_submit.sh submit_gamlss_fits_ABCD.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_long_regional "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sOne_train.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_regional_ONE/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_regional_ONE/gamlss_fits_stats"

split 2
sbatch array_script_submit.sh submit_gamlss_fits_ABCD.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_long_regional "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sTwo_train.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_regional_TWO/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_regional_TWO/gamlss_fits_stats"

#SETUP-data
##Define files
``` {r}
splitOne_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_regional_ONE/"
splitTwo_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_regional_TWO/"
sOne_fits_stats_filename <- paste0(splitOne_folder, "gamlss_fits_stats_all.csv")
sTwo_fits_stats_filename <- paste0(splitTwo_folder, "gamlss_fits_stats_all.csv")
splitOne_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sOne_train.csv"
splitTwo_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sTwo_train.csv"
splitOne_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sOne_test.csv"
splitTwo_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sTwo_test.csv"
phenotype_set <- readRDS("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/phenotype_set.rds")
```
## Load data frames and clean them up
``` {r}
#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_df <- read.csv(splitOne_data_filename)  %>% select(-1) %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sOne_df$sex <- as.factor(sOne_df$sex)
sOne_df$site <- as.factor(sOne_df$site)
sOne_df$age <- as.numeric(sOne_df$age)

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_df <- read.csv(splitTwo_data_filename)  %>% select(-1) %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sTwo_df$sex <- as.factor(sTwo_df$sex)
sTwo_df$site <- as.factor(sTwo_df$site)
sTwo_df$age <- as.numeric(sTwo_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_test_df <- read.csv(splitOne_test_filename)  %>% select(-1)  %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sOne_test_df$sex <- as.factor(sOne_test_df$sex)
sOne_test_df$site <- as.factor(sOne_test_df$site)
sOne_test_df$age <- as.numeric(sOne_test_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_test_df <- read.csv(splitTwo_test_filename)  %>% select(-1) %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sTwo_test_df$sex <- as.factor(sTwo_test_df$sex)
sTwo_test_df$site <- as.factor(sTwo_test_df$site)
sTwo_test_df$age <- as.numeric(sTwo_test_df$age)
```
#FITS
Make a table of error messages, warnings etc
Phenotype set should not have included wmhint, those models gave errors: all wmhint models are deleted.
```{r}
all_fits_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/longitudinal_regional_fits.csv"
if(save_fits == TRUE){
sOne_fits <- inspect_model_fits(splitOne_folder, sOne_fits_stats_filename)
sOne_fits$label <- name_mapping$region_name[match(sOne_fits$phenotype, name_mapping$abbreviation)]
sTwo_fits <- inspect_model_fits(splitTwo_folder, sTwo_fits_stats_filename)
sTwo_fits$label <- name_mapping$region_name[match(sTwo_fits$phenotype, name_mapping$abbreviation)]


sOne_fits$split_no <- rep("1", dim(sOne_fits)[1])
sTwo_fits$split_no <- rep("2", dim(sTwo_fits)[1])

all_fits <- rbind(sOne_fits, sTwo_fits)

write.csv(all_fits, all_fits_filename)
}
```
##get table of BIC within each phenotype
```{r}
#load saved fits if saved.
if(save_fits == FALSE) {
  all_fits <- read.csv(all_fits_filename) %>% select(-1)
  sOne_fits <- all_fits %>% filter(split_no == 1)
  sTwo_fits <- all_fits %>% filter(split_no == 2)
}

sOne_best <- sOne_fits %>%
  filter(convergence_warn_end == 0) %>%
  group_by(phenotype) %>%
 slice_min(BIC, n = 1)

sTwo_best <- sTwo_fits %>%
  filter(convergence_warn_end == 0) %>%
  group_by(phenotype) %>%
  slice_min(BIC, n = 1)
```

##get table of which vars are chosen for which phenotype & which moment
```{r}
#terms
terms_all = c( "PCW_between_t1t2", "random(site)", "age", "sex", "nonSingleton")
moments = c("mu", "sigma", "nu")
colnames = apply(expand.grid(terms_all, moments), 1, paste, collapse=".")

#sOne
sOne_best_terms <- as.data.frame(matrix(nrow = dim(sOne_best)[1], ncol=length(colnames)))
names(sOne_best_terms) <- colnames
rownames(sOne_best_terms) <- sOne_best$phenotype
  for(i in 1:length(terms_all)) {
      sOne_best_terms[,(i)] <- grepl(terms_all[i], sOne_best$mu_formula)
      sOne_best_terms[,(i+length(terms_all))] <- grepl(terms_all[i], sOne_best$sigma_formula)
      sOne_best_terms[,(i+2*length(terms_all))] <- grepl(terms_all[i], sOne_best$nu_formula)
  }

sTwo_best_terms$label <- name_mapping$region_name[match(sub(".t2","", rownames(sTwo_best_terms)), name_mapping$abbreviation)]

#sTwo
sTwo_best_terms <- as.data.frame(matrix(nrow = dim(sTwo_best)[1], ncol=length(colnames)))
names(sTwo_best_terms) <- colnames
rownames(sTwo_best_terms) <- sTwo_best$phenotype
  for(i in 1:length(terms_all)) {
      sTwo_best_terms[,(i)] <- grepl(terms_all[i], sTwo_best$mu_formula)
      sTwo_best_terms[,(i+length(terms_all))] <- grepl(terms_all[i], sTwo_best$sigma_formula)
      sTwo_best_terms[,(i+2*length(terms_all))] <- grepl(terms_all[i], sTwo_best$nu_formula)
  }

sTwo_best_terms$label <- name_mapping$region_name[match(sub(".t2","", rownames(sTwo_best_terms)), name_mapping$abbreviation)]
```

##Load best model
```{r}
sOne_best_list <- paste0(splitOne_folder,"gamlssFIT_",sOne_best$model_index,".rds")
best_models_One <- lapply(sOne_best_list, readRDS)
sTwo_best_list <- paste0(splitTwo_folder,"gamlssFIT_",sTwo_best$model_index,".rds")
best_models_Two <- lapply(sTwo_best_list, readRDS)
```

#Diagnostics
##BIC plots for each phenotype
###sOne
```{r}
if(diagnostics == TRUE){
sOne_fits$ylabel <- paste("MU",gsub(".*~", "", sOne_fits$mu_formula), "SIGMA", gsub(".*~", "", sOne_fits$sigma_formula), "NU", gsub(".*~", "", sOne_fits$nu_formula), sep = ".")
sOne_fits_all <- sOne_fits

sOne_fits <- sOne_fits_all %>% 
  filter(!is.na(BIC) & convergence_warn_end == FALSE) %>%
  group_by(phenotype) %>%
  mutate(scaled_log_BIC = log(BIC - min(BIC)))

#RANK TOP 20 models and only plot those!!!
BIC_WMV <- 
  sOne_fits %>% filter(phenotype == "totalWM_cb.t2") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("WMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_GMV <- 
  sOne_fits %>% filter(phenotype == "smri_vol_cdk_total.t2") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("cort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_scGMV <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_subcorticalgv") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("subcort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))


BIC_Vent <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_allventricles") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Ventricles, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_wholeB <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_wholeb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Whole Brain, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))
}
```

###sTwo
``` {r}
if(diagnostics == TRUE){
sTwo_fits$ylabel <- paste("MU",gsub(".*~", "", sTwo_fits$sigma_formula), "SIGMA", gsub(".*~", "", sTwo_fits$sigma_formula), "NU", gsub(".*~", "", sTwo_fits$nu_formula), sep = ".")

sTwo_fits <- sTwo_fits %>% 
  filter(!is.na(BIC)) %>%
  group_by(phenotype) %>%
  mutate(scaled_log_BIC = log(BIC - min(BIC)))

sTwo_BIC_WMV <- 
  sTwo_fits %>% filter(phenotype == "totalWM_cb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("WMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_GMV <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_cdk_total") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("cort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_scGMV <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_subcorticalgv") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("subcort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))


sTwo_BIC_Vent <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_allventricles") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Ventricles, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_wholeB <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_wholeb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Whole Brain, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))
}
```

##Worm plots-Centile plots
get worm plots & centile plots for best BIC within each phenotype, for each split
###Split One
```{r}
diagnostics = TRUE
if(diagnostics == TRUE){
plot <- FALSE
plots_wp <- vector(mode = "list", length = dim(sOne_best)[1])
plots_cent <- vector(mode = "list", length = dim(sOne_best)[1])
best_models_One <- vector(mode = "list", length = dim(sOne_best)[1])
i = 0
titles <- c("Cortical GMV", "Total Ventricular Volume", "Subcortical GMV", "Whole Brain Volume", "Total WMV")
for (model in sOne_models) {
  #print(deparse(model$mu.formula))
  phenotype <- as.character(model$mu.terms[[2]])
  fit <- sOne_best[which(sOne_best$phenotype == phenotype),]
 # model <- sOne_models[[i]]
  if (identical(deparse(model$mu.formula), deparse(as.formula(fit$mu_formula))) &&
    identical(deparse(model$sigma.formula), deparse(as.formula(fit$sigma_formula))) &&
    identical(deparse(model$nu.formula), deparse(as.formula(fit$nu_formula)))) {
    i= i+1
    ph.t1 <- phenotype %>% gsub(".t2", ".t1", .)
    if (plot == TRUE){
      plots_wp[[i]] <- wp.taki(model, xvar = sOne_df$age, n = 2) + labs(title = titles[i])
      
      #(title = eval(parse(text=paste0("plot_models[[i]]$",title_field))))
        #ph.t1 <- phenotype %>% gsub(".t2", ".t1", .)
        #df <- sOne_df %>% 
        #select(sex, age, site, nonSingleton, model$phenotype, PCW_between_t1t2, ph.t1) %>% 
        #drop_na()
     #plots_cent[[i]] <- make_centile_fan(model, df, "age", "sex", desiredCentiles = c(0.05, 0.5, 0.95)) + 
       #labs(title = titles[i],x = "Age", y = NULL, color = "Sex=Female", fill="Sex=Female")
      }
   best_models_One[[i]] <- model
    }
}

if (plot == TRUE){
n <- length(plots_wp)
nCol <- floor(sqrt(n))
do.call("grid.arrange", c(plots_wp, ncol=nCol))
#do.call("grid.arrange", c(plots_cent, ncol=3))
}
}
```
###Split Two
```{r}
if(diagnostics == TRUE){
plot <- TRUE
plots_wp <- vector(mode = "list", length = dim(sTwo_best)[1])
plots_cent <- vector(mode = "list", length = dim(sTwo_best)[1])
best_models_Two <- vector(mode = "list", length = dim(sTwo_best)[1])
i = 0
titles <- c("Cortical GMV", "Total Ventricular Volume", "Subcortical GMV", "Whole Brain Volume", "Total WMV")
for (model in sTwo_models) {
  #print(deparse(model$mu.formula))
  phenotype <- as.character(model$mu.terms[[2]])
  fit <- sTwo_best[which(sTwo_best$phenotype == phenotype),]
 # model <- sTwo_models[[i]]
  if (identical(deparse(model$mu.formula), deparse(as.formula(fit$mu_formula))) &&
    identical(deparse(model$sigma.formula), deparse(as.formula(fit$sigma_formula))) &&
    identical(deparse(model$nu.formula), deparse(as.formula(fit$nu_formula)))) {
    i= i+1
    ph.t1 <- phenotype %>% gsub(".t2", ".t1", .)
    if (plot == TRUE){
      plots_wp[[i]] <- wp.taki(model, ylim = 0.7, xvar = sTwo_df[, ph.t1], n = 2) + labs(title = titles[i])
      
      #(title = eval(parse(text=paste0("plot_models[[i]]$",title_field))))
        #ph.t1 <- phenotype %>% gsub(".t2", ".t1", .)
        #df <- sTwo_df %>% 
        #select(sex, age, site, nonSingleton, model$phenotype, PCW_between_t1t2, ph.t1) %>% 
        #drop_na()
     #plots_cent[[i]] <- make_centile_fan(model, df, "age", "sex", desiredCentiles = c(0.05, 0.5, 0.95)) + 
       #labs(title = titles[i],x = "Age", y = NULL, color = "Sex=Female", fill="Sex=Female")
      }
   best_models_Two[[i]] <- model
    }
}

if (plot == TRUE){
n <- length(plots_wp)
nCol <- floor(sqrt(n))
do.call("grid.arrange", c(plots_wp, ncol=nCol))
#do.call("grid.arrange", c(plots_cent, ncol=3))
}
}
```
#Predicting on test data
predict centile scores for split TWO using model trained on split ONE
```{r}
plot <- FALSE
print <- FALSE 

centiles_pred_one <- vector(mode = "list", length = dim(sOne_best)[1])
centiles_pred_two <- vector(mode = "list", length = dim(sTwo_best)[1])
splits_correlations <- setNames(data.frame(matrix(ncol = 4, nrow = dim(sOne_best)[1])), c("ph_one", "cor_est_one", "ph_two", "cor_est_two"))

for(i in 1:length(best_models_One)){
#define models from split one and split two
model_one <- best_models_One[[i]]
model_two <- best_models_Two[sapply(best_models_Two, function(x){any(grepl(as.character(model_one$mu.formula[[2]]),x$mu.formula))})][[1]]

phOne <- model_one$mu.formula[[2]]
phOne.t1 <- phOne %>% gsub(".t2", ".t1", .)
title_one <- as.character(model_one$mu.formula[[2]])
phTwo <- model_two$mu.formula[[2]]
phTwo.t1 <- phTwo%>% gsub(".t2", ".t1", .)
title_two <- as.character(model_two$mu.formula[[2]])
stopifnot(title_one == title_two)

#define original df from split one and two, with phenotypes from the current model
og_df_one <- sOne_df %>% select(c("age", "sex", "nonSingleton", "site", "PCW_between_t1t2", phOne, phOne.t1))
og_df_two <- sTwo_df %>% select(c("age", "sex", "nonSingleton", "site", "PCW_between_t1t2", phTwo, phTwo.t1))

#calculate predicted centiles on sOne and sTwo data using sOne model

model <- model_one
sOne_centiles_1 <- suppressMessages(pred_og_centile_EK(model_one, sOne_df))
sTwo_centiles_1 <- suppressMessages(pred_og_centile_EK(model_one, og_df_one, new.data = sTwo_df))
centiles_pred_two[[i]] <- suppressMessages(pred_og_centile_EK(model_one, og_df_one, new.data = sTwo_test_df))
names(centiles_pred_two)[i] <- paste(title_two, "centiles", sep = "_")
splits_correlations$ph_one[i] <- title_one

#calculate predicted centiles on sOne and sTwo data using sTwo model
model <- model_two
sOne_centiles_2 <- suppressMessages(pred_og_centile_EK(model_two, og_df_two, new.data = sOne_df))
sTwo_centiles_2 <- suppressMessages(pred_og_centile_EK(model_two, sTwo_df))
centiles_pred_one[[i]] <- suppressMessages(pred_og_centile_EK(model_two, og_df_two, new.data = sOne_test_df))
names(centiles_pred_one)[i] <- paste(title_one, "centiles", sep = "_")
splits_correlations$ph_two[i] <- title_two

if(plot == TRUE) {
  #Plotting sOne and sTwo from two predictions
  plot(sOne_centiles_1, sOne_centiles_2, main = paste0("split One: ", title_one) , ylab = "predictions from Model 1", xlab = "predictions from Model 2")
  abline(a = 0, b = 1, col = "red", lwd = 2, lty = 2)
  plot(sTwo_centiles_1, sTwo_centiles_2, main = paste0("split Two: ", title_two) , ylab = "predictions from Model 1", xlab = "predictions from Model 2")
  abline(a = 0, b = 1, col = "red", lwd = 2, lty = 2)
  }

#Correlation coefficients
cor_one <- cor.test(sOne_centiles_1, sOne_centiles_2)
cor_two <- cor.test(sTwo_centiles_1, sTwo_centiles_2)

#Save correlations in dataframe
splits_correlations$cor_est_one[i] <- cor_one$estimate
splits_correlations$cor_est_two[i] <- cor_two$estimate

if (print == TRUE){
print(paste0("Correlation Coefficient Split One, ", title_one, cor_one$estimate, " , ", cor_one$p.value))
print(paste0("Correlation Coefficient Split Two, ", title_two, cor_two$estimate, " , ", cor_two$p.value))
}
}
```
##Save centiles
Save in single dataframe with columns for participant ID and split ID
```{r}
output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Centile_CSVs/"
filename <- paste0(output_folder, "regional_longmodel_global_volume_centiles.csv")

centiles_One <- cbind(sOne_test_df %>% select(src_subject_id), as.data.frame(centiles_pred_one))
centiles_One$split_ID <- rep("1", dim(centiles_One)[1])
                             
centiles_Two <- cbind(sTwo_test_df %>% select(src_subject_id), as.data.frame(centiles_pred_two))
centiles_Two$split_ID <- rep("2", dim(centiles_Two)[1])

centiles_all <- rbind(centiles_One, centiles_Two)

write.csv(centiles_all, filename)
```
#Gestational Age
##within splits
Look at the predicted centiles (from cross model) with GA, within splits
```{r}
sOne_test_df <- cbind(sOne_test_df, as.data.frame(centiles_pred_one))
sTwo_test_df <- cbind(sTwo_test_df, as.data.frame(centiles_pred_two))
#rm(centiles_pred_one, centiles_pred_two)

# cor_table_One <- as.data.frame(t(sapply(sOne_test_df[, grepl("centiles", names(sOne_test_df))], function(x) {
#   cor_test <- cor.test(sOne_test_df$gestAge, x, use = "complete.obs", method = "spearman")
#   c(correlation = cor_test$estimate, p_value = cor_test$p.value)
# })))
# 
# cor_table_One_sig <- cor_table_One %>% filter(p_value < 0.05)
# cor_table_One$p_value_adj <- p.adjust(cor_table_One$p_value, method = "BH")
# cor_table_One_sig_MC <- cor_table_One %>% filter(p_value_adj < 0.05)
# 
# cor_table_Two <- as.data.frame(t(sapply(sTwo_test_df[, grepl("centiles", names(sTwo_test_df))], function(x) {
#   cor_test <- cor.test(sTwo_test_df$gestAge, x, use = "complete.obs", method = "spearman")
#   c(correlation = cor_test$estimate, p_value = cor_test$p.value)
# })))
# 
# cor_table_Two_sig <- cor_table_Two %>% filter(p_value < 0.05)
# cor_table_Two$p_value_adj <- p.adjust(cor_table_Two$p_value, method = "BH")
# cor_table_Two_sig_MC <- cor_table_Two %>% filter(p_value_adj < 0.05)

```

Get phenotypes significant in both splits
```{r}
# rownames(cor_table_One_sig)[which(rownames(cor_table_One_sig) %in% rownames(cor_table_Two_sig))]
# 
# cor_intersect <- cor_table_One_sig[which(rownames(cor_table_One_sig) %in% rownames(cor_table_Two_sig_MC)),]
```

##whole sample
Look at the predicted centiles (from cross model) with GA, whole sample
```{r}
if(sum(grepl("centiles",names(sOne_test_df)))== 0) {
sOne_test_df <- cbind(sOne_test_df, as.data.frame(centiles_pred_one))
sTwo_test_df <- cbind(sTwo_test_df, as.data.frame(centiles_pred_two))
}
full_test_df <- rbind(sOne_test_df,sTwo_test_df)

#regression (to be able to include covariates later)
ga_zscore <- z_score(full_test_df$gestAge)
reg_table_full <- as.data.frame(t(sapply(full_test_df[, grepl("centiles", names(full_test_df))], function(x) {
  x_zscore <- z_score(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4])
})))

reg_table_full_sig <- reg_table_full %>% filter(ga_p < 0.05)
reg_table_full$ga_p_adj <- p.adjust(reg_table_full$ga_p, method = "BH")
reg_table_full_sig_MC <- reg_table_full %>% filter(ga_p_adj < 0.05)
```

##Visualize on the brain -- nothing is significant

```{r}
library(ggsegDKT)
library(ggseg)

reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
reg_table_full_sig_MC[!(reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

#Setting manual limits (could match the colorbar limits between different variables)
# Plot using ggseg
# ggplot(plot_data) +
#   geom_brain(atlas = dk, 
#              position = position_brain(hemi ~ side),
#              aes(fill = correlation.rho)) +
#   scale_fill_gradient2(limits = c(-0.2, 0.2)) +
#   theme_void() +
#   labs(title = "Regions with GA")

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with GA")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with GA")
```
