---
  title: "model_selection_longitudinal"
author: "Eren Kafadar"
date: "2024-11-29"
output: html_document
---
  
``` {r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library(dplyr)
library(magrittr)
library(readr)
library(stringr)
library(ggplot2)
library(gamlss) #to fit model
require(gamlss.ggplots)
library(tidyr)
library(gamlssTools) #Margaret's package
library(gridExtra)

source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/inspect_model_fits.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/gamlss_functions_EK.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/data_functions.R")
```

#GENERATE Models
generate models including the first time point
``` {r}
# family_set <- c("GG")
# #smri_vol_cdk_total is for total cortical GM, this is from the Desikan parcellation. The rest are from Aseg parcellation.
# phenotype_set <- c("smri_vol_cdk_total.t2", "totalWM_cb.t2","smri_vol_scs_subcorticalgv.t2", "smri_vol_scs_allventricles.t2", "smri_vol_scs_wholeb.t2")
# 
# out_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2/"
# 
# terms_all = c("~1", "PCW_between_t1t2", "random(site)", "age", "sex", "nonSingleton")
# 
# generate_gamlss_models(phenotype_set = phenotype_set,
#                        out_folder = out_folder,
#                        family_set = family_set,
#                        mu_terms = terms_all,
#                        sigma_terms = terms_all,
#                        nu_terms = terms_all,
#                        tau_terms = NULL,
#                        n_crit = 200,
#                        long = TRUE)
```

Run fits submitting an array job.
With the specifications below:

#Global fits GG, RS, model selection split 1
sbatch array_script_submit.sh submit_gamlss_fits_ABCD.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2 "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sOne_train.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_ONE/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_ONE/gamlss_fits_stats"

#Global fits GG, RS, model selection split 2
sbatch array_script_submit.sh submit_gamlss_fits_ABCD.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2 "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_t1t2/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sTwo_train.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_TWO/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_TWO/gamlss_fits_stats"

#FITS ANALYSIS

##Define files
``` {r}
#file paths
splitOne_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_ONE/"
splitTwo_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_long_global_TWO/"
sOne_fits_stats_filename <- paste0(splitOne_folder, "gamlss_fits_stats_all.csv")
sTwo_fits_stats_filename <- paste0(splitTwo_folder, "gamlss_fits_stats_all.csv")
splitOne_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sOne_train.csv"
splitTwo_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sTwo_train.csv"
splitOne_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sOne_test.csv"
splitTwo_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_t1t2_wide_sTwo_test.csv"
phenotype_set <- readRDS("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/phenotype_set.rds")
```
## Load data frames and clean them up
``` {r}
#define the distribution family and phenotype and whether nonSingleton variable is there to define file name.
#rename some of the variables and select baseline scans
#rename_vec <- c(age = "PCW_at_scan", sex = "sex_baseline", site = "site_id_l", nonSingleton = "nonSingleton")

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_df <- read.csv(splitOne_data_filename)  %>% select(-1) %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sOne_df$sex <- as.factor(sOne_df$sex)
sOne_df$site <- as.factor(sOne_df$site)
sOne_df$age <- as.numeric(sOne_df$age)

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_df <- read.csv(splitTwo_data_filename)  %>% select(-1) %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sTwo_df$sex <- as.factor(sTwo_df$sex)
sTwo_df$site <- as.factor(sTwo_df$site)
sTwo_df$age <- as.numeric(sTwo_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_test_df <- read.csv(splitOne_test_filename)  %>% select(-1)  %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sOne_test_df$sex <- as.factor(sOne_test_df$sex)
sOne_test_df$site <- as.factor(sOne_test_df$site)
sOne_test_df$age <- as.numeric(sOne_test_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_test_df <- read.csv(splitTwo_test_filename)  %>% select(-1) %>% 
  subset(!is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sTwo_test_df$sex <- as.factor(sTwo_test_df$sex)
sTwo_test_df$site <- as.factor(sTwo_test_df$site)
sTwo_test_df$age <- as.numeric(sTwo_test_df$age)
```
##Load fitted model(s)
reading in models fit to both split halves (separately)
``` {r}
sOne_models <- lapply(list.files(path = splitOne_folder, pattern = "\\.rds$", full.names = TRUE), readRDS)
sTwo_models <- lapply(list.files(path = splitTwo_folder, pattern = "\\.rds$", full.names = TRUE), readRDS)

#sOne_models <- lapply(list.files(path = splitOne_folder, pattern = "\\.RData$", full.names = TRUE), load)
#sTwo_models <- lapply(list.files(path = splitTwo_folder, pattern = "\\.RData$", full.names = TRUE), load)
```

#Check fits
Make a table of error messages, warnings etc
Phenotype set should not have included wmhint, those models gave errors: all wmhint models are deleted.
```{r}
sOne_fits <- inspect_model_fits(splitOne_folder, sOne_fits_stats_filename)
sOne_not_converge <- sOne_models[sapply(sOne_models, function(x){x$converged == FALSE})]

sTwo_fits <- inspect_model_fits(splitTwo_folder, sTwo_fits_stats_filename)
sTwo_not_converge <- sTwo_models[sapply(sTwo_models, function(x){x$converged == FALSE})]
```
workaround because the above inspect_model_fits fct doesn't work with the longitudinal model outputs
FIXED THE FUNCTION TO WORK with longitudinal models.
```{r}
# sOne_fits <- read.csv(sOne_fits_stats_filename)
# sOne_fits$modelFam <- paste(fits_stats$mu_formula, 
#                              fits_stats$sigma_formula, 
#                              fits_stats$nu_formula, 
#                              fits_stats$family_abbr, sep = "__")
# sOne_fits$phenotype <- as.character(lapply(sOne_fits$mu_formula, str_extract, pattern = ".*(?= ~)"))
```
#BIC
##get table of BIC within each phenotype
-- adapt code from family selection notebook
```{r}
sOne_best <- sOne_fits %>%
  group_by(phenotype) %>%
  slice_min(BIC, n = 1)

sTwo_best <- sTwo_fits %>%
  group_by(phenotype) %>%
  slice_min(BIC, n = 1)
```
##BIC plots for each phenotype
sOne
```{r}
sOne_fits$ylabel <- paste("MU",gsub(".*~", "", sOne_fits$mu_formula), "SIGMA", gsub(".*~", "", sOne_fits$sigma_formula), "NU", gsub(".*~", "", sOne_fits$nu_formula), sep = ".")
sOne_fits_all <- sOne_fits

sOne_fits <- sOne_fits_all %>% 
  filter(!is.na(BIC) & convergence_warn_end == FALSE) %>%
  group_by(phenotype) %>%
  mutate(scaled_log_BIC = log(BIC - min(BIC)))

#RANK TOP 20 models and only plot those!!!
BIC_WMV <- 
  sOne_fits %>% filter(phenotype == "totalWM_cb.t2") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("WMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_GMV <- 
  sOne_fits %>% filter(phenotype == "smri_vol_cdk_total.t2") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("cort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_scGMV <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_subcorticalgv") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("subcort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))


BIC_Vent <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_allventricles") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Ventricles, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_wholeB <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_wholeb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Whole Brain, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

```

sTwo
``` {r}
sTwo_fits$ylabel <- paste("MU",gsub(".*~", "", sTwo_fits$sigma_formula), "SIGMA", gsub(".*~", "", sTwo_fits$sigma_formula), "NU", gsub(".*~", "", sTwo_fits$nu_formula), sep = ".")

sTwo_fits <- sTwo_fits %>% 
  filter(!is.na(BIC)) %>%
  group_by(phenotype) %>%
  mutate(scaled_log_BIC = log(BIC - min(BIC)))

sTwo_BIC_WMV <- 
  sTwo_fits %>% filter(phenotype == "totalWM_cb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("WMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_GMV <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_cdk_total") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("cort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_scGMV <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_subcorticalgv") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("subcort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))


sTwo_BIC_Vent <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_allventricles") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Ventricles, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_wholeB <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_wholeb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Whole Brain, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

```
##Predicting on test data
predict centile scores for split TWO using model trained on split ONE
```{r}
plot <- FALSE

centiles_pred_one <- vector(mode = "list", length = dim(sOne_best)[1])
centiles_pred_two <- vector(mode = "list", length = dim(sTwo_best)[1])

for(i in 1:length(best_models_One)){
#define models from split one and split two
model_one <- best_models_One[[i]]
model_two <- best_models_Two[[i]]

#define labels for phenotypes based on name_mapping df
title_one <- name_mapping$labels[name_mapping$variables == as.character(model_one$mu.formula[[2]])]
title_two <- name_mapping$labels[name_mapping$variables == as.character(model_two$mu.formula[[2]])]
stopifnot(title_one == title_two)

#define original df from split one and two, with phenotypes from the current model
og_df_one <- sOne_df %>% select(c("age", "sex", "nonSingleton", "site", model_one$mu.formula[[2]]))
og_df_two <- sTwo_df %>% select(c("age", "sex", "nonSingleton", "site", model_two$mu.formula[[2]]))

#calculate predicted centiles on sOne data using sOne and sTwo models
sOne_centiles_1 <- pred_og_centile_EK(model_one, sOne_df)
sOne_centiles_2 <- pred_og_centile_EK(model_two, og_df_two, new.data = sOne_df)
centiles_pred_one[[i]] <- pred_og_centile(model_two, og_df_two, new.data = sOne_test_df)
names(centiles_pred_one)[i] <- paste(title_one, "centiles", sep = "_")

#calculate predicted centiles on sTwo data using sOne and sTwo models
sTwo_centiles_1 <- pred_og_centile_EK(model_one, og_df_one, new.data = sTwo_df)
sTwo_centiles_2 <- pred_og_centile_EK(model_two, sTwo_df)
centiles_pred_two[[i]] <- pred_og_centile_EK(model_one, og_df_one, new.data = sTwo_test_df)
names(centiles_pred_two)[i] <- paste(title_two, "centiles", sep = "_")

if(plot == TRUE) {
  #Plotting sOne and sTwo from two predictions
  plot(sOne_centiles_1, sOne_centiles_2, main = paste0("split One: ", title_one) , ylab = "predictions from Model 1", xlab = "predictions from Model 2")
  abline(a = 0, b = 1, col = "red", lwd = 2, lty = 2)
  plot(sTwo_centiles_1, sTwo_centiles_2, main = paste0("split Two: ", title_two) , ylab = "predictions from Model 1", xlab = "predictions from Model 2")
  abline(a = 0, b = 1, col = "red", lwd = 2, lty = 2)
  }

#Correlation coefficients
cor_one <- cor.test(sOne_centiles_1, sOne_centiles_2)
cor_two <- cor.test(sTwo_centiles_1, sTwo_centiles_2)
print(paste0("Correlation Coefficient Split One, ", title_one, cor_one$estimate, " , ", cor_one$p.value))
print(paste0("Correlation Coefficient Split Two, ", title_two, cor_two$estimate, " , ", cor_two$p.value))
}
```
