---
title: "model_selection"
author: "Eren Kafadar"
date: "2024-11-26"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
diagnostics <- FALSE
generate <- FALSE
save_fits <- FALSE
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library(dplyr)
library(magrittr)
library(readr)
library(stringr)
library(ggplot2)
library(gamlss) #to fit model
require(gamlss.ggplots)
library(tidyr)
library(gamlssTools) #Margaret's package
library(gridExtra)

source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/inspect_model_fits.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/gamlss_functions_EK.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/data_functions.R")

source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/pred_og_centile_EK.R")

phenotypes <- readRDS("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/phenotype_set.rds")

#df to map variable names onto names displayed on figures
name_mapping <- data.frame(
  abbreviation = c(
     "smri_vol_cdk_totallh", "smri_vol_cdk_totalrh", "smri_vol_cdk_total",   
     "totalWM_cb", "totalWM_crb", "totalGM_crb",
     
    "smri_vol_scs_cbwmatterlh", "smri_vol_scs_ltventriclelh", "smri_vol_scs_inflatventlh",
    "smri_vol_scs_crbwmatterlh", "smri_vol_scs_crbcortexlh", "smri_vol_scs_tplh",
    "smri_vol_scs_caudatelh", "smri_vol_scs_putamenlh", "smri_vol_scs_pallidumlh",
    "smri_vol_scs_3rdventricle", "smri_vol_scs_4thventricle", "smri_vol_scs_bstem",
    "smri_vol_scs_hpuslh", "smri_vol_scs_amygdalalh", "smri_vol_scs_csf",
    "smri_vol_scs_lesionlh", "smri_vol_scs_aal", "smri_vol_scs_vedclh",
    
    "smri_vol_scs_cbwmatterrh", "smri_vol_scs_ltventriclerh", "smri_vol_scs_inflatventrh",
    "smri_vol_scs_crbwmatterrh", "smri_vol_scs_crbcortexrh", "smri_vol_scs_tprh",
    "smri_vol_scs_caudaterh", "smri_vol_scs_putamenrh", "smri_vol_scs_pallidumrh",
    "smri_vol_scs_hpusrh", "smri_vol_scs_amygdalarh", "smri_vol_scs_lesionrh",
    "smri_vol_scs_aar", "smri_vol_scs_vedcrh", 
    
    "smri_vol_scs_wmhint",
    "smri_vol_scs_wmhintlh", "smri_vol_scs_wmhintrh", 
    
    "smri_vol_scs_ccps",
    "smri_vol_scs_ccmidps", "smri_vol_scs_ccct", "smri_vol_scs_ccmidat",
    "smri_vol_scs_ccat", 
    
    "smri_vol_scs_wholeb", "smri_vol_scs_latventricles",
    "smri_vol_scs_allventricles", "smri_vol_scs_intracranialv", "smri_vol_scs_suprateialv",
    "smri_vol_scs_subcorticalgv",
    
    "smri_vol_cdk_banksstslh", "smri_vol_cdk_cdacatelh", "smri_vol_cdk_cdmdfrlh",
    "smri_vol_cdk_cuneuslh", "smri_vol_cdk_ehinallh", "smri_vol_cdk_fusiformlh",
    "smri_vol_cdk_ifpllh", "smri_vol_cdk_iftmlh", "smri_vol_cdk_ihcatelh",
    "smri_vol_cdk_locclh", "smri_vol_cdk_lobfrlh", "smri_vol_cdk_linguallh",
    "smri_vol_cdk_mobfrlh", "smri_vol_cdk_mdtmlh", "smri_vol_cdk_parahpallh",
    "smri_vol_cdk_paracnlh", "smri_vol_cdk_parsopclh", "smri_vol_cdk_parsobislh",
    "smri_vol_cdk_parstgrislh", "smri_vol_cdk_pericclh", "smri_vol_cdk_postcnlh",
    "smri_vol_cdk_ptcatelh", "smri_vol_cdk_precnlh", "smri_vol_cdk_pclh",
    "smri_vol_cdk_rracatelh", "smri_vol_cdk_rrmdfrlh", "smri_vol_cdk_sufrlh",
    "smri_vol_cdk_supllh", "smri_vol_cdk_sutmlh", "smri_vol_cdk_smlh",
    "smri_vol_cdk_frpolelh", "smri_vol_cdk_tmpolelh", "smri_vol_cdk_trvtmlh",
    "smri_vol_cdk_insulalh",
    
     "smri_vol_cdk_banksstsrh", "smri_vol_cdk_cdacaterh", "smri_vol_cdk_cdmdfrrh",
    "smri_vol_cdk_cuneusrh", "smri_vol_cdk_ehinalrh", "smri_vol_cdk_fusiformrh",
    "smri_vol_cdk_ifplrh", "smri_vol_cdk_iftmrh", "smri_vol_cdk_ihcaterh",
    "smri_vol_cdk_loccrh", "smri_vol_cdk_lobfrrh", "smri_vol_cdk_lingualrh",
    "smri_vol_cdk_mobfrrh", "smri_vol_cdk_mdtmrh", "smri_vol_cdk_parahpalrh",
    "smri_vol_cdk_paracnrh", "smri_vol_cdk_parsopcrh", "smri_vol_cdk_parsobisrh",
    "smri_vol_cdk_parstgrisrh", "smri_vol_cdk_periccrh", "smri_vol_cdk_postcnrh",
    "smri_vol_cdk_ptcaterh", "smri_vol_cdk_precnrh", "smri_vol_cdk_pcrh",
    "smri_vol_cdk_rracaterh", "smri_vol_cdk_rrmdfrrh", "smri_vol_cdk_sufrrh",
    "smri_vol_cdk_suplrh", "smri_vol_cdk_sutmrh", "smri_vol_cdk_smrh",
    "smri_vol_cdk_frpolerh", "smri_vol_cdk_tmpolerh", "smri_vol_cdk_trvtmrh",
    "smri_vol_cdk_insularh"
  ),
  region_name = c(
    "Left-Cerebral_Cortex", "Right-Cerebral-Cortex", "Total-Cerebral-Cortex",
    "Total_Cerebral-WM", "Total_Cerebellum-WM", "Total-Cerebellum-Cortex",
    
    "Left-Cerebral-White-Matter", "Left-Lateral-Ventricle", "Left-Inf-Lat-Vent",
    "Left-Cerebellum-White-Matter", "Left-Cerebellum-Cortex", "Left-Thalamus-Proper",
    "Left-Caudate-Nucleus", "Left-Putamen", "Left-Pallidum",
    "x3rd-ventricle", "x4th-ventricle", "Brain-Stem",
    "Left-Hippocampus", "Left-Amygdala", "Cerebrospinal-Fluid",
    "Left-Lesion", "Left-Accumbens-Area", "Left-VentralDC",
    
   "Right-Cerebral-White-Matter", "Right-Lateral-Ventricle", "Right-Inf-Lat-Vent",
    "Right-Cerebellum-White-Matter", "Right-Cerebellum-Cortex", "Right-Thalamus-Proper",
    "Right-Caudate-Nucleus", "Right-Putamen", "Right-Pallidum",
    "Right-Hippocampus", "Right-Amygdala",
    "Right-Lesion", "Right-Accumbens-Area", "Right-VentralDC",
    
    "WM-Hypointensities","Left-WM-Hypointensities", "Right-WM-Hypointensities",
   
   "CC_Posterior","CC_Mid_Posterior", "CC_Central", "CC_Mid_Anterior",
    "CC_Anterior", 
   
   "WholeBrain", "LatVentricles","AllVentricles", "IntracranialVolume", 
   "SupratentorialVolume", "SubcorticalGrayVolume",
   
     "lh_bankssts", "lh_caudalanteriorcingulate", "lh_caudalmiddlefrontal",
    "lh_cuneus", "lh_entorhinal", "lh_fusiform",
    "lh_inferiorparietal", "lh_inferiortemporal", "lh_isthmuscingulate",
    "lh_lateraloccipital", "lh_lateralorbitofrontal", "lh_lingual",
    "lh_medialorbitofrontal", "lh_middletemporal", "lh_parahippocampal",
    "lh_paracentral", "lh_parsopercularis", "lh_parsorbitalis",
    "lh_parstriangularis", "lh_pericalcarine", "lh_postcentral",
    "lh_posteriorcingulate", "lh_precentral", "lh_precuneus", "lh_rostralanteriorcingulate",
    "lh_rostralmiddlefrontal", "lh_superiorfrontal", "lh_superiorparietal",
    "lh_superiortemporal", "lh_supramarginal", "lh_frontalpole",
    "lh_temporalpole", "lh_transversetemporal", "lh_insula",
   
     "rh_bankssts", "rh_caudalanteriorcingulate", "rh_caudalmiddlefrontal",
    "rh_cuneus", "rh_entorhinal", "rh_fusiform",
    "rh_inferiorparietal", "rh_inferiortemporal", "rh_isthmuscingulate",
    "rh_lateraloccipital", "rh_lateralorbitofrontal", "rh_lingual",
    "rh_medialorbitofrontal", "rh_middletemporal", "rh_parahippocampal",
    "rh_paracentral", "rh_parsopercularis", "rh_parsorbitalis",
    "rh_parstriangularis", "rh_pericalcarine", "rh_postcentral",
    "rh_posteriorcingulate", "rh_precentral", "rh_precuneus", "rh_rostralanteriorcingulate",
    "rh_rostralmiddlefrontal", "rh_superiorfrontal", "rh_superiorparietal",
    "rh_superiortemporal", "rh_supramarginal", "rh_frontalpole",
    "rh_temporalpole", "rh_transversetemporal", "rh_insula"
    )
)
```

#GENERATE Models

```{r}
if (generate == TRUE){
family_set <- c("GG")
#smri_vol_cdk_total is for total cortical GM, this is from the Desikan parcellation. The rest are from Aseg parcellation. 
phenotype_set <- c("smri_vol_cdk_total", "totalWM_cb","smri_vol_scs_subcorticalgv", "smri_vol_scs_allventricles", "smri_vol_scs_wholeb")
out_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_globa0.01157932
	
2.315459e-01
	
2.315459e-01l_all/"

terms_all = c("~1", "age", "sex", "random(site)", "nonSingleton")

generate_gamlss_models(phenotype_set, 
                                   out_folder, 
                                   family_set = family_set,
                                   mu_terms = terms_all,
                                   sigma_terms = terms_all,
                                   nu_terms = terms_all,
                                   tau_terms = NULL,
                                   n_crit = 200)
}
```

Run fits submitting an array job.
split 1
sbatch array_script_submit.sh submit_gamlss_fits_ABCD.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_global_all "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_global_all/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrainOne_selectVars_famfilter2024-11-26.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_baseline_full_ONE/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_baseline_full_ONE/gamlss_fits_stats"

split 2
sbatch array_script_submit.sh submit_gamlss_fits_ABCD.sh /mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_global_all "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_models_global_all/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrainTwo_selectVars_famfilter2024-11-26.csv" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_baseline_full_TWO/" "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_baseline_full_TWO/gamlss_fits_stats"


#SETUP Data

##Define files
```{r}
#file paths
splitOne_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_baseline_full_ONE/"
splitTwo_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_baseline_full_TWO/"
sOne_fits_stats_filename <- paste0(splitOne_folder, "gamlss_fits_stats_all.csv")
sTwo_fits_stats_filename <- paste0(splitTwo_folder, "gamlss_fits_stats_all.csv")
splitOne_data_filename <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrainOne_selectVars_famfilter2024-11-26.csv"
# splitOne_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrain_selectVars_famfilter2024-10-04.csv"
splitTwo_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrainTwo_selectVars_famfilter2024-11-26.csv"
splitOne_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTestOne_selectVars_famfilter2024-11-26.csv"
splitTwo_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTestTwo_selectVars_famfilter2024-11-26.csv"
phenotype_set <- readRDS("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/phenotype_set.rds")
```
## Load data frames and clean them up
```{r}
#define the distribution family and phenotype and whether nonSingleton variable is there to define file name.
#rename some of the variables and select baseline scans
rename_vec <- c(age = "PCW_at_scan", sex = "sex_baseline", site = "site_id_l", nonSingleton = "nonSingleton")

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_df <- read.csv(splitOne_data_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sOne_df$sex <- as.factor(sOne_df$sex)
sOne_df$site <- as.factor(sOne_df$site)
sOne_df$age <- as.numeric(sOne_df$age)

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_df <- read.csv(splitTwo_data_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))
sTwo_df$sex <- as.factor(sTwo_df$sex)
sTwo_df$site <- as.factor(sTwo_df$site)
sTwo_df$age <- as.numeric(sTwo_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_test_df <- read.csv(splitOne_test_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))
sOne_test_df$sex <- as.factor(sOne_test_df$sex)
sOne_test_df$site <- as.factor(sOne_test_df$site)
sOne_test_df$age <- as.numeric(sOne_test_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_test_df <- read.csv(splitTwo_test_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))
sTwo_test_df$sex <- as.factor(sTwo_test_df$sex)
sTwo_test_df$site <- as.factor(sTwo_test_df$site)
sTwo_test_df$age <- as.numeric(sTwo_test_df$age)
```
#FITS
##load all fits and save
Make a table of error messages, warnings etc
Phenotype set should not have included wmhint, those models gave errors: all wmhint models are deleted.
```{r}
all_fits_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/baseline_global_fits.csv"
if(save_fits == TRUE){
sOne_fits <- inspect_model_fits(splitOne_folder, sOne_fits_stats_filename)
sOne_fits$label <- name_mapping$region_name[match(sOne_fits$phenotype, name_mapping$abbreviation)]
sTwo_fits <- inspect_model_fits(splitTwo_folder, sTwo_fits_stats_filename)
sTwo_fits$label <- name_mapping$region_name[match(sTwo_fits$phenotype, name_mapping$abbreviation)]


sOne_fits$split_no <- rep("1", dim(sOne_fits)[1])
sTwo_fits$split_no <- rep("2", dim(sTwo_fits)[1])

all_fits <- rbind(sOne_fits, sTwo_fits)

write.csv(all_fits, all_fits_filename)
}
```
##get table of BIC within each phenotype
```{r}
#load saved fits if saved.
if(save_fits == FALSE) {
  all_fits <- read.csv(all_fits_filename) %>% select(-1)
  sOne_fits <- all_fits %>% filter(split_no == 1)
  sTwo_fits <- all_fits %>% filter(split_no == 2)
}

sOne_best <- sOne_fits %>%
  filter(convergence_warn_end == 0) %>%
  group_by(phenotype) %>%
 slice_min(BIC, n = 1)

sTwo_best <- sTwo_fits %>%
  filter(convergence_warn_end == 0) %>%
  group_by(phenotype) %>%
  slice_min(BIC, n = 1)
```

##get table of which vars are chosen for which phenotype & which moment
```{r}
#terms
terms_all = c("age", "sex", "random(site)", "nonSingleton")
moments = c("mu", "sigma", "nu")
colnames = apply(expand.grid(terms_all, moments), 1, paste, collapse=".")

#sOne
sOne_best_terms <- as.data.frame(matrix(nrow = dim(sOne_best)[1], ncol=length(colnames)))
names(sOne_best_terms) <- colnames
rownames(sOne_best_terms) <- sOne_best$phenotype
  for(i in 1:length(terms_all)) {
      sOne_best_terms[,(i)] <- grepl(terms_all[i], sOne_best$mu_formula)
      sOne_best_terms[,(i+length(terms_all))] <- grepl(terms_all[i], sOne_best$sigma_formula)
      sOne_best_terms[,(i+2*length(terms_all))] <- grepl(terms_all[i], sOne_best$nu_formula)
  }

sOne_best_terms$label <- name_mapping$region_name[match(rownames(sOne_best_terms), name_mapping$abbreviation)]

#sTwo
sTwo_best_terms <- as.data.frame(matrix(nrow = dim(sTwo_best)[1], ncol=length(colnames)))
names(sTwo_best_terms) <- colnames
rownames(sTwo_best_terms) <- sTwo_best$phenotype
  for(i in 1:length(terms_all)) {
      sTwo_best_terms[,(i)] <- grepl(terms_all[i], sTwo_best$mu_formula)
      sTwo_best_terms[,(i+length(terms_all))] <- grepl(terms_all[i], sTwo_best$sigma_formula)
      sTwo_best_terms[,(i+2*length(terms_all))] <- grepl(terms_all[i], sTwo_best$nu_formula)
  }

sTwo_best_terms$label <- name_mapping$region_name[match(rownames(sTwo_best_terms), name_mapping$abbreviation)]
```

##Load best model
```{r}
sOne_best_list <- paste0(splitOne_folder,"gamlssFIT_",sOne_best$model_index,".rds")
best_models_One <- lapply(sOne_best_list, readRDS)
sTwo_best_list <- paste0(splitTwo_folder,"gamlssFIT_",sTwo_best$model_index,".rds")
best_models_Two <- lapply(sTwo_best_list, readRDS)
```
##Load all fitted model(s) --deprecated
reading in models fit to both split halves (separately)
``` {r}
# sOne_models <- lapply(list.files(path = splitOne_folder, pattern = "\\.rds$", full.names = TRUE), readRDS)
#sOne_not_converge <- sOne_models[sapply(sOne_models, function(x){x$converged == FALSE})]

# sTwo_models <- lapply(list.files(path = splitTwo_folder, pattern = "\\.rds$", full.names = TRUE), readRDS)
#sTwo_not_converge <- sTwo_models[sapply(sTwo_models, function(x){x$converged == FALSE})]
```
#Diagnostics
##BIC plots for each phenotype
###sOne
```{r}
if(diagnostics == TRUE){
sOne_fits$ylabel <- paste("MU",gsub(".*~", "", sOne_fits$mu_formula), "SIGMA", gsub(".*~", "", sOne_fits$sigma_formula), "NU", gsub(".*~", "", sOne_fits$nu_formula), sep = ".")
  
sOne_fits <- sOne_fits %>% 
  filter(!is.na(BIC)) %>%
  group_by(phenotype) %>%
  mutate(scaled_log_BIC = log(BIC - min(BIC)))

BIC_WMV <- 
  sOne_fits %>% filter(phenotype == "totalWM_cb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("WMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_GMV <- 
  sOne_fits %>% filter(phenotype == "smri_vol_cdk_total") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("cort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_scGMV <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_subcorticalgv") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("subcort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))


BIC_Vent <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_allventricles") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Ventricles, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

BIC_wholeB <- 
  sOne_fits %>% filter(phenotype == "smri_vol_scs_wholeb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Whole Brain, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))
}
```

###sTwo
```{r}
if(diagnostics == TRUE){
sTwo_fits$ylabel <- paste("MU",gsub(".*~", "", sTwo_fits$mu_formula), "SIGMA", gsub(".*~", "", sTwo_fits$sigma_formula), "NU", gsub(".*~", "", sTwo_fits$nu_formula), sep = ".")
  
sTwo_fits <- sTwo_fits %>% 
  filter(!is.na(BIC)) %>%
  group_by(phenotype) %>%
  mutate(scaled_log_BIC = log(BIC - min(BIC)))

sTwo_BIC_WMV <- 
  sTwo_fits %>% filter(phenotype == "totalWM_cb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("WMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_GMV <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_cdk_total") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("cort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_scGMV <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_subcorticalgv") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("subcort GMV, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))


sTwo_BIC_Vent <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_allventricles") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Ventricles, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))

sTwo_BIC_wholeB <- 
  sTwo_fits %>% filter(phenotype == "smri_vol_scs_wholeb") %>% 
  ggplot(., aes(x = scaled_log_BIC, y = ylabel, fill = BIC)) + 
  geom_histogram(stat = "identity") + 
  ggtitle("Whole Brain, all") + labs(x = "scaled log BIC", y = "Model") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 6))
}
```

##Worm plots-Centile plots
get worm plots & centile plots for best BIC within each phenotype, for each split
###sOne
```{r}
diagnostics = FALSE
if(diagnostics == TRUE){
plot <- FALSE
plots_wp <- vector(mode = "list", length = dim(sOne_best)[1])
#plots_cent <- vector(mode = "list", length = dim(sOne_best)[1])
for (i  in 1:length(best_models_One)) {
  #print(deparse(model$mu.formula))
  model <- best_models_One[[i]]
  phenotype <- as.character(model$mu.terms[[2]])
  title <- name_mapping$region_name[match(phenotype, name_mapping$abbreviation)]
      plots_wp[[i]] <- wp.taki(model) + labs(title = title)
      df <- sOne_df %>% 
        select(sex, age, site, nonSingleton, phenotype) %>% 
        drop_na()
     #plots_cent[[i]] <- make_centile_fan(model, df, "age", "sex", desiredCentiles = c(0.05, 0.5, 0.95)) + 
       #labs(title = titles[i],x = "Age", y = NULL, color = "Sex=Female", fill="Sex=Female")
    }

if (plot == TRUE){
n <- length(plots_wp)
nCol <- min(c(floor(sqrt(n)), 4))
nRow <- min(ceiling(n/nCol), 4)
breaks <- c(seq(from = 0, to = n , by = (nCol*nRow)), n)
for(k in 1:length(breaks)){
  start <- breaks[k] + 1
  end <- breaks[k+1]
  do.call("grid.arrange", c(plots_wp[start:end], ncol=nCol))
}
}
}
```
###sTwo
```{r}
diagnostics = FALSE
if(diagnostics == TRUE){
plot <- FALSE
plots_wp <- vector(mode = "list", length = dim(sTwo_best)[1])
#plots_cent <- vector(mode = "list", length = dim(stwo_best)[1])
for (i  in 1:length(best_models_Two)) {
  #print(deparse(model$mu.formula))
  model <- best_models_Two[[i]]
  phenotype <- as.character(model$mu.terms[[2]])
  title <- name_mapping$region_name[match(phenotype, name_mapping$abbreviation)]
      plots_wp[[i]] <- wp.taki(model) + labs(title = title)
      df <- sTwo_df %>% 
        select(sex, age, site, nonSingleton, phenotype) %>% 
        drop_na()
     #plots_cent[[i]] <- make_centile_fan(model, df, "age", "sex", desiredCentiles = c(0.05, 0.5, 0.95)) + 
       #labs(title = titles[i],x = "Age", y = NULL, color = "Sex=Female", fill="Sex=Female")
    }

if (plot == TRUE){
n <- length(plots_wp)
nCol <- min(c(floor(sqrt(n)), 4))
nRow <- min(ceiling(n/nCol), 4)
breaks <- c(seq(from = 0, to = n , by = (nCol*nRow)), n)
for(k in 1:length(breaks)){
  start <- breaks[k] + 1
  end <- breaks[k+1]
  do.call("grid.arrange", c(plots_wp[start:end], ncol=nCol))
}

#do.call("grid.arrange", c(plots_cent, ncol=3))
}
}
```
##cent-cdf
!! even though I edited the cent_cdf to point to pred_og_centile_EK to bypass the "incompatible dimensions warning"
```{r}
print <- TRUE

centcdf_one <- setNames(data.frame(matrix(ncol = 3, nrow = dim(sOne_best)[1])), c("ph", "cdfcor_train", "cdfcor_test"))
centcdf_two <- setNames(data.frame(matrix(ncol = 3, nrow = dim(sTwo_best)[1])), c("ph", "cdfcor_train", "cdfcor_test"))
cdf_expected <- c(0.01, 0.05, 0.10, 0.25, 0.50, 0.75, 0.90, 0.95, 0.99)

for(i in 1:length(best_models_One)){
#define models from split one and split two
model_one <- best_models_One[[i]]
model_two <- best_models_Two[sapply(best_models_Two, function(x){any(grepl(as.character(model_one$mu.formula[[2]]),x$mu.formula))})][[1]]

#define labels for phenotypes based on name_mapping df
# title_one <- name_mapping$labels[name_mapping$variables == as.character(model_one$mu.formula[[2]])]
# title_two <- name_mapping$labels[name_mapping$variables == as.character(model_two$mu.formula[[2]])]

title_one <- as.character(model_one$mu.formula[[2]])
title_two <- as.character(model_two$mu.formula[[2]])
stopifnot(title_one == title_two)

#define original df from split one and two, with phenotypes from the current model
og_df_one <- sOne_df %>% select(c("age", "sex", "nonSingleton", "site", model_one$mu.formula[[2]]))
og_df_two <- sTwo_df %>% select(c("age", "sex", "nonSingleton", "site", model_two$mu.formula[[2]]))

#calculate predicted centiles distribution for sOne models, using sOne train dataset and sTwo test dataset
#save correlation with expected cdf values
model <- model_one 
out_train_one <- suppressMessages(cent_cdf(model_one, og_df_one))
#out_test_one <- suppressMessages(cent_cdf(model_one, sTwo_test_df))
centcdf_one$ph[i] <- title_one
centcdf_one$cdfcor_train[i] <- (cor.test(as.numeric(out_train_one[1,]), cdf_expected)$estimate)
#centcdf_one$cdfcor_test[i] <- (cor.test(as.numeric(out_test_one[1,]), cdf_expected)$estimate)

#calculate predicted centiles distribution for sTwo models, using sTwo train dataset, and sOne test dataset
#save correlation with expected cdf values
model <- model_two
out_train_two <- suppressMessages(cent_cdf(model_two, og_df_two))
#out_test_two <- suppressMessages(cent_cdf(model_two, sOne_test_df))
centcdf_two$ph[i] <- title_two
centcdf_two$cdfcor_train[i] <- (cor.test(as.numeric(out_train_two[1,]), cdf_expected)$estimate)
#centcdf_two$cdfcor_test[i] <- (cor.test(as.numeric(out_test_two[1,]), cdf_expected)$estimate)


if (print == TRUE){
print(paste0("Correlation Coefficient Split One, Train Data ", title_one, centcdf_one$cdfcor_train[i]))
print(paste0("Correlation Coefficient Split Two, Train Data ", title_two, centcdf_two$cdfcor_train[i]))
}
}
```

#Predicting centiles
predict centile scores for split TWO using model trained on split ONE
```{r}
plot <- FALSE
print <- FALSE 

centiles_pred_one <- vector(mode = "list", length = dim(sOne_best)[1])
centiles_pred_two <- vector(mode = "list", length = dim(sTwo_best)[1])
splits_correlations <- setNames(data.frame(matrix(ncol = 4, nrow = dim(sOne_best)[1])), c("ph_one", "cor_est_one", "ph_two", "cor_est_two"))

for(i in 1:length(best_models_One)){
#define models from split one and split two
model_one <- best_models_One[[i]]
model_two <- best_models_Two[sapply(best_models_Two, function(x){any(grepl(as.character(model_one$mu.formula[[2]]),x$mu.formula))})][[1]]

#define labels for phenotypes based on name_mapping df
# title_one <- name_mapping$labels[name_mapping$variables == as.character(model_one$mu.formula[[2]])]
# title_two <- name_mapping$labels[name_mapping$variables == as.character(model_two$mu.formula[[2]])]

title_one <- as.character(model_one$mu.formula[[2]])
title_two <- as.character(model_two$mu.formula[[2]])
stopifnot(title_one == title_two)

#define original df from split one and two, with phenotypes from the current model
og_df_one <- sOne_df %>% select(c("age", "sex", "nonSingleton", "site", model_one$mu.formula[[2]]))
og_df_two <- sTwo_df %>% select(c("age", "sex", "nonSingleton", "site", model_two$mu.formula[[2]]))

#calculate predicted centiles on sOne and sTwo data using sOne model

model <- model_one
sOne_centiles_1 <- suppressMessages(pred_og_centile_EK(model_one, sOne_df))
sTwo_centiles_1 <- suppressMessages(pred_og_centile_EK(model_one, og_df_one, new.data = sTwo_df))
centiles_pred_two[[i]] <- suppressMessages(pred_og_centile_EK(model_one, og_df_one, new.data = sTwo_test_df))
names(centiles_pred_two)[i] <- paste(title_two, "centiles", sep = "_")
splits_correlations$ph_one[i] <- title_one

#calculate predicted centiles on sOne and sTwo data using sTwo model
model <- model_two
sOne_centiles_2 <- suppressMessages(pred_og_centile_EK(model_two, og_df_two, new.data = sOne_df))
sTwo_centiles_2 <- suppressMessages(pred_og_centile_EK(model_two, sTwo_df))
centiles_pred_one[[i]] <- suppressMessages(pred_og_centile_EK(model_two, og_df_two, new.data = sOne_test_df))
names(centiles_pred_one)[i] <- paste(title_one, "centiles", sep = "_")
splits_correlations$ph_two[i] <- title_two

if(plot == TRUE) {
  #Plotting sOne and sTwo from two predictions
  plot(sOne_centiles_1, sOne_centiles_2, main = paste0("split One: ", title_one) , ylab = "predictions from Model 1", xlab = "predictions from Model 2")
  abline(a = 0, b = 1, col = "red", lwd = 2, lty = 2)
  plot(sTwo_centiles_1, sTwo_centiles_2, main = paste0("split Two: ", title_two) , ylab = "predictions from Model 1", xlab = "predictions from Model 2")
  abline(a = 0, b = 1, col = "red", lwd = 2, lty = 2)
  }

#Correlation coefficients
cor_one <- cor.test(sOne_centiles_1, sOne_centiles_2)
cor_two <- cor.test(sTwo_centiles_1, sTwo_centiles_2)

#Save correlations in dataframe
splits_correlations$cor_est_one[i] <- cor_one$estimate
splits_correlations$cor_est_two[i] <- cor_two$estimate

if (print == TRUE){
print(paste0("Correlation Coefficient Split One, ", title_one, cor_one$estimate, " , ", cor_one$p.value))
print(paste0("Correlation Coefficient Split Two, ", title_two, cor_two$estimate, " , ", cor_two$p.value))
}
}
```
##Save centiles
Save in single dataframe with columns for participant ID and split ID
```{r}
if(save_fits == TRUE){
output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Centile_CSVs/"
filename <- paste0(output_folder, "global_baseline_volume_centiles.csv")

centiles_One <- cbind(sOne_test_df %>% select(src_subject_id), as.data.frame(centiles_pred_one))
centiles_One$split_ID <- rep("1", dim(centiles_One)[1])
                             
centiles_Two <- cbind(sTwo_test_df %>% select(src_subject_id), as.data.frame(centiles_pred_two))
centiles_Two$split_ID <- rep("2", dim(centiles_Two)[1])

centiles_all <- rbind(centiles_One, centiles_Two)

write.csv(centiles_all, filename)
}
```
##centiles fit metrics
###test uniformity
```{r}
if(sum(grepl("centiles",names(sOne_test_df)))== 0) {
sOne_test_df <- cbind(sOne_test_df, as.data.frame(centiles_pred_one))
sTwo_test_df <- cbind(sTwo_test_df, as.data.frame(centiles_pred_two))
}
full_test_df <- rbind(sOne_test_df,sTwo_test_df)

#sOne
kstest_one <- as.data.frame(t(sapply(sOne_test_df[, grepl("centiles", names(sOne_test_df))], function(x) {
  #jitter data with small noise to avoid "ties" warning
  x <- x + runif(length(x), -1e-6, 1e-6)
  test <- ks.test(x, "punif", 0, 1)

  c(p_value = test$p.value[1], test = "uniformity")
})))


#sTwo
kstest_two <- as.data.frame(t(sapply(sTwo_test_df[, grepl("centiles", names(sTwo_test_df))], function(x) {
  #jitter data with small noise to avoid "ties" warning
  x <- x + runif(length(x), -1e-6, 1e-6)
  test <- ks.test(x, "punif", 0, 1)

  c(p_value = test$p.value[1], test = "uniformity")
})))
```
#Gestational Age
Additional results should be in a different document.

Look at the predicted centiles (from cross model) with GA, whole sample
```{r}
if(sum(grepl("centiles",names(sOne_test_df)))== 0) {
sOne_test_df <- cbind(sOne_test_df, as.data.frame(centiles_pred_one))
sTwo_test_df <- cbind(sTwo_test_df, as.data.frame(centiles_pred_two))
}
full_test_df <- rbind(sOne_test_df,sTwo_test_df)


#regression (to be able to include covariates later)
ga_zscore <- z_score(full_test_df$gestAge)
reg_table_full <- as.data.frame(t(sapply(full_test_df[, grepl("centiles", names(full_test_df))], function(x) {
  x_zscore <- z_score(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4])
})))

reg_table_full_sig <- reg_table_full %>% filter(ga_p < 0.05)
reg_table_full$ga_p_adj <- p.adjust(reg_table_full$ga_p, method = "BH")
reg_table_full_sig_MC <- reg_table_full %>% filter(ga_p_adj < 0.05)
```

##Visualize on the brain
```{r}
library(ggsegDKT)
library(ggseg)

reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
reg_table_full_sig_MC[!(reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with GA")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with GA")
```