---
title: "t1_results_newMC"
author: "Eren Kafadar"
date: "2025-03-26"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
diagnostics <- FALSE
generate <- FALSE
save_tables <- FALSE
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library(dplyr)
library(magrittr)
library(readr)
library(stringr)
library(gamlss) #to fit model
require(gamlss.ggplots)
library(splines)
library(tidyr)
library(gamlssTools) #Margaret's package
#For figures/plotting
library(ggplot2)
library(gridExtra)
library(ggsegDKT)
library(ggseg)
library(ggcorrplot)
library(interactions)
library(growthstandards)

source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/inspect_model_fits.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/gamlss_functions_EK.R")
source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/data_functions.R")

source("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/pred_og_centile_EK.R")

#df to map variable names onto names displayed on figures
name_mapping <- data.frame(
  abbreviation = c(
     "smri_vol_cdk_totallh", "smri_vol_cdk_totalrh", "smri_vol_cdk_total",   
     "totalWM_cb", "totalWM_crb", "totalGM_crb",
     
    "smri_vol_scs_cbwmatterlh", "smri_vol_scs_ltventriclelh", "smri_vol_scs_inflatventlh",
    "smri_vol_scs_crbwmatterlh", "smri_vol_scs_crbcortexlh", "smri_vol_scs_tplh",
    "smri_vol_scs_caudatelh", "smri_vol_scs_putamenlh", "smri_vol_scs_pallidumlh",
    "smri_vol_scs_3rdventricle", "smri_vol_scs_4thventricle", "smri_vol_scs_bstem",
    "smri_vol_scs_hpuslh", "smri_vol_scs_amygdalalh", "smri_vol_scs_csf",
    "smri_vol_scs_lesionlh", "smri_vol_scs_aal", "smri_vol_scs_vedclh",
    
    "smri_vol_scs_cbwmatterrh", "smri_vol_scs_ltventriclerh", "smri_vol_scs_inflatventrh",
    "smri_vol_scs_crbwmatterrh", "smri_vol_scs_crbcortexrh", "smri_vol_scs_tprh",
    "smri_vol_scs_caudaterh", "smri_vol_scs_putamenrh", "smri_vol_scs_pallidumrh",
    "smri_vol_scs_hpusrh", "smri_vol_scs_amygdalarh", "smri_vol_scs_lesionrh",
    "smri_vol_scs_aar", "smri_vol_scs_vedcrh", 
    
    "smri_vol_scs_wmhint",
    "smri_vol_scs_wmhintlh", "smri_vol_scs_wmhintrh", 
    
    "smri_vol_scs_ccps",
    "smri_vol_scs_ccmidps", "smri_vol_scs_ccct", "smri_vol_scs_ccmidat",
    "smri_vol_scs_ccat", 
    
    "smri_vol_scs_wholeb", "smri_vol_scs_latventricles",
    "smri_vol_scs_allventricles", "smri_vol_scs_intracranialv", "smri_vol_scs_suprateialv",
    "smri_vol_scs_subcorticalgv",
    
    "smri_vol_cdk_banksstslh", "smri_vol_cdk_cdacatelh", "smri_vol_cdk_cdmdfrlh",
    "smri_vol_cdk_cuneuslh", "smri_vol_cdk_ehinallh", "smri_vol_cdk_fusiformlh",
    "smri_vol_cdk_ifpllh", "smri_vol_cdk_iftmlh", "smri_vol_cdk_ihcatelh",
    "smri_vol_cdk_locclh", "smri_vol_cdk_lobfrlh", "smri_vol_cdk_linguallh",
    "smri_vol_cdk_mobfrlh", "smri_vol_cdk_mdtmlh", "smri_vol_cdk_parahpallh",
    "smri_vol_cdk_paracnlh", "smri_vol_cdk_parsopclh", "smri_vol_cdk_parsobislh",
    "smri_vol_cdk_parstgrislh", "smri_vol_cdk_pericclh", "smri_vol_cdk_postcnlh",
    "smri_vol_cdk_ptcatelh", "smri_vol_cdk_precnlh", "smri_vol_cdk_pclh",
    "smri_vol_cdk_rracatelh", "smri_vol_cdk_rrmdfrlh", "smri_vol_cdk_sufrlh",
    "smri_vol_cdk_supllh", "smri_vol_cdk_sutmlh", "smri_vol_cdk_smlh",
    "smri_vol_cdk_frpolelh", "smri_vol_cdk_tmpolelh", "smri_vol_cdk_trvtmlh",
    "smri_vol_cdk_insulalh",
    
     "smri_vol_cdk_banksstsrh", "smri_vol_cdk_cdacaterh", "smri_vol_cdk_cdmdfrrh",
    "smri_vol_cdk_cuneusrh", "smri_vol_cdk_ehinalrh", "smri_vol_cdk_fusiformrh",
    "smri_vol_cdk_ifplrh", "smri_vol_cdk_iftmrh", "smri_vol_cdk_ihcaterh",
    "smri_vol_cdk_loccrh", "smri_vol_cdk_lobfrrh", "smri_vol_cdk_lingualrh",
    "smri_vol_cdk_mobfrrh", "smri_vol_cdk_mdtmrh", "smri_vol_cdk_parahpalrh",
    "smri_vol_cdk_paracnrh", "smri_vol_cdk_parsopcrh", "smri_vol_cdk_parsobisrh",
    "smri_vol_cdk_parstgrisrh", "smri_vol_cdk_periccrh", "smri_vol_cdk_postcnrh",
    "smri_vol_cdk_ptcaterh", "smri_vol_cdk_precnrh", "smri_vol_cdk_pcrh",
    "smri_vol_cdk_rracaterh", "smri_vol_cdk_rrmdfrrh", "smri_vol_cdk_sufrrh",
    "smri_vol_cdk_suplrh", "smri_vol_cdk_sutmrh", "smri_vol_cdk_smrh",
    "smri_vol_cdk_frpolerh", "smri_vol_cdk_tmpolerh", "smri_vol_cdk_trvtmrh",
    "smri_vol_cdk_insularh"
  ),
  region_name = c(
    "Left-Cerebral_Cortex", "Right-Cerebral-Cortex", "Total-Cerebral-Cortex",
    "Total_Cerebral-WM", "Total_Cerebellum-WM", "Total-Cerebellum-Cortex",
    
    "Left-Cerebral-White-Matter", "Left-Lateral-Ventricle", "Left-Inf-Lat-Vent",
    "Left-Cerebellum-White-Matter", "Left-Cerebellum-Cortex", "Left-Thalamus-Proper",
    "Left-Caudate", "Left-Putamen", "Left-Pallidum",
    "x3rd-ventricle", "x4th-ventricle", "Brain-Stem",
    "Left-Hippocampus", "Left-Amygdala", "Cerebrospinal-Fluid",
    "Left-Lesion", "Left-Accumbens-Area", "Left-VentralDC",
    
   "Right-Cerebral-White-Matter", "Right-Lateral-Ventricle", "Right-Inf-Lat-Vent",
    "Right-Cerebellum-White-Matter", "Right-Cerebellum-Cortex", "Right-Thalamus-Proper",
    "Right-Caudate", "Right-Putamen", "Right-Pallidum",
    "Right-Hippocampus", "Right-Amygdala",
    "Right-Lesion", "Right-Accumbens-Area", "Right-VentralDC",
    
    "WM-Hypointensities","Left-WM-Hypointensities", "Right-WM-Hypointensities",
   
   "CC_Posterior","CC_Mid_Posterior", "CC_Central", "CC_Mid_Anterior",
    "CC_Anterior", 
   
   "WholeBrain", "LatVentricles","AllVentricles", "IntracranialVolume", 
   "SupratentorialVolume", "SubcorticalGrayVolume",
   
     "lh_bankssts", "lh_caudalanteriorcingulate", "lh_caudalmiddlefrontal",
    "lh_cuneus", "lh_entorhinal", "lh_fusiform",
    "lh_inferiorparietal", "lh_inferiortemporal", "lh_isthmuscingulate",
    "lh_lateraloccipital", "lh_lateralorbitofrontal", "lh_lingual",
    "lh_medialorbitofrontal", "lh_middletemporal", "lh_parahippocampal",
    "lh_paracentral", "lh_parsopercularis", "lh_parsorbitalis",
    "lh_parstriangularis", "lh_pericalcarine", "lh_postcentral",
    "lh_posteriorcingulate", "lh_precentral", "lh_precuneus", "lh_rostralanteriorcingulate",
    "lh_rostralmiddlefrontal", "lh_superiorfrontal", "lh_superiorparietal",
    "lh_superiortemporal", "lh_supramarginal", "lh_frontalpole",
    "lh_temporalpole", "lh_transversetemporal", "lh_insula",
   
     "rh_bankssts", "rh_caudalanteriorcingulate", "rh_caudalmiddlefrontal",
    "rh_cuneus", "rh_entorhinal", "rh_fusiform",
    "rh_inferiorparietal", "rh_inferiortemporal", "rh_isthmuscingulate",
    "rh_lateraloccipital", "rh_lateralorbitofrontal", "rh_lingual",
    "rh_medialorbitofrontal", "rh_middletemporal", "rh_parahippocampal",
    "rh_paracentral", "rh_parsopercularis", "rh_parsorbitalis",
    "rh_parstriangularis", "rh_pericalcarine", "rh_postcentral",
    "rh_posteriorcingulate", "rh_precentral", "rh_precuneus", "rh_rostralanteriorcingulate",
    "rh_rostralmiddlefrontal", "rh_superiorfrontal", "rh_superiorparietal",
    "rh_superiortemporal", "rh_supramarginal", "rh_frontalpole",
    "rh_temporalpole", "rh_transversetemporal", "rh_insula"
    )
)

phenotypes_for_MC <- c(
   "smri_vol_scs_cbwmatterlh", "smri_vol_scs_ltventriclelh", "smri_vol_scs_inflatventlh",
    "smri_vol_scs_crbwmatterlh", "smri_vol_scs_crbcortexlh", "smri_vol_scs_tplh",
    "smri_vol_scs_caudatelh", "smri_vol_scs_putamenlh", "smri_vol_scs_pallidumlh",
    "smri_vol_scs_3rdventricle", "smri_vol_scs_4thventricle", "smri_vol_scs_bstem",
    "smri_vol_scs_hpuslh", "smri_vol_scs_amygdalalh", "smri_vol_scs_aal", "smri_vol_scs_vedclh",
    
    "smri_vol_scs_cbwmatterrh", "smri_vol_scs_ltventriclerh", "smri_vol_scs_inflatventrh",
    "smri_vol_scs_crbwmatterrh", "smri_vol_scs_crbcortexrh", "smri_vol_scs_tprh",
    "smri_vol_scs_caudaterh", "smri_vol_scs_putamenrh", "smri_vol_scs_pallidumrh",
    "smri_vol_scs_hpusrh", "smri_vol_scs_amygdalarh",
    "smri_vol_scs_aar", "smri_vol_scs_vedcrh", 
    
    "smri_vol_scs_ccps",
    "smri_vol_scs_ccmidps", "smri_vol_scs_ccct", "smri_vol_scs_ccmidat",
    "smri_vol_scs_ccat",
    
    "smri_vol_cdk_banksstslh", "smri_vol_cdk_cdacatelh", "smri_vol_cdk_cdmdfrlh",
    "smri_vol_cdk_cuneuslh", "smri_vol_cdk_ehinallh", "smri_vol_cdk_fusiformlh",
    "smri_vol_cdk_ifpllh", "smri_vol_cdk_iftmlh", "smri_vol_cdk_ihcatelh",
    "smri_vol_cdk_locclh", "smri_vol_cdk_lobfrlh", "smri_vol_cdk_linguallh",
    "smri_vol_cdk_mobfrlh", "smri_vol_cdk_mdtmlh", "smri_vol_cdk_parahpallh",
    "smri_vol_cdk_paracnlh", "smri_vol_cdk_parsopclh", "smri_vol_cdk_parsobislh",
    "smri_vol_cdk_parstgrislh", "smri_vol_cdk_pericclh", "smri_vol_cdk_postcnlh",
    "smri_vol_cdk_ptcatelh", "smri_vol_cdk_precnlh", "smri_vol_cdk_pclh",
    "smri_vol_cdk_rracatelh", "smri_vol_cdk_rrmdfrlh", "smri_vol_cdk_sufrlh",
    "smri_vol_cdk_supllh", "smri_vol_cdk_sutmlh", "smri_vol_cdk_smlh",
    "smri_vol_cdk_frpolelh", "smri_vol_cdk_tmpolelh", "smri_vol_cdk_trvtmlh",
    "smri_vol_cdk_insulalh",
    
     "smri_vol_cdk_banksstsrh", "smri_vol_cdk_cdacaterh", "smri_vol_cdk_cdmdfrrh",
    "smri_vol_cdk_cuneusrh", "smri_vol_cdk_ehinalrh", "smri_vol_cdk_fusiformrh",
    "smri_vol_cdk_ifplrh", "smri_vol_cdk_iftmrh", "smri_vol_cdk_ihcaterh",
    "smri_vol_cdk_loccrh", "smri_vol_cdk_lobfrrh", "smri_vol_cdk_lingualrh",
    "smri_vol_cdk_mobfrrh", "smri_vol_cdk_mdtmrh", "smri_vol_cdk_parahpalrh",
    "smri_vol_cdk_paracnrh", "smri_vol_cdk_parsopcrh", "smri_vol_cdk_parsobisrh",
    "smri_vol_cdk_parstgrisrh", "smri_vol_cdk_periccrh", "smri_vol_cdk_postcnrh",
    "smri_vol_cdk_ptcaterh", "smri_vol_cdk_precnrh", "smri_vol_cdk_pcrh",
    "smri_vol_cdk_rracaterh", "smri_vol_cdk_rrmdfrrh", "smri_vol_cdk_sufrrh",
    "smri_vol_cdk_suplrh", "smri_vol_cdk_sutmrh", "smri_vol_cdk_smrh",
    "smri_vol_cdk_frpolerh", "smri_vol_cdk_tmpolerh", "smri_vol_cdk_trvtmrh",
    "smri_vol_cdk_insularh"
  )

global_phenotypes <- c("smri_vol_cdk_total", "totalWM_cb", "smri_vol_scs_allventricles", "smri_vol_scs_subcorticalgv")

```
#SETUP-data
##Define files
```{r}
#file paths
splitOne_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_regional_ONE/"
splitTwo_folder <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/gamlss_fits_regional_TWO/"

splitOne_data_filename <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrainOne_selectVars_famfilter2024-11-26.csv"
splitTwo_data_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTrainTwo_selectVars_famfilter2024-11-26.csv"

splitOne_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTestOne_selectVars_famfilter2024-11-26.csv"
splitTwo_test_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd_baseline_matchedTestTwo_selectVars_famfilter2024-11-26.csv"

phenotype_set <- readRDS("/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/ABCD_premie_code/phenotype_set.rds")

reg_centiles_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Centile_CSVs/regional_baseline_volume_centiles.csv"
global_centiles_filename <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Centile_CSVs/global_baseline_volume_centiles.csv"
```
## Load data frames and clean them up
```{r}
#define the distribution family and phenotype and whether nonSingleton variable is there to define file name.
#rename some of the variables and select baseline scans
rename_vec <- c(age = "PCW_at_scan", sex = "sex_baseline", site = "site_id_l", nonSingleton = "nonSingleton")

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_df <- read.csv(splitOne_data_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))#4512 folks
sOne_df$sex <- as.factor(sOne_df$sex)
sOne_df$site <- as.factor(sOne_df$site)
sOne_df$nonSingleton <- as.factor(sOne_df$nonSingleton)
sOne_df$age <- as.numeric(sOne_df$age)

#read in the dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_df <- read.csv(splitTwo_data_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))
sTwo_df$sex <- as.factor(sTwo_df$sex)
sTwo_df$site <- as.factor(sTwo_df$site)
sTwo_df$nonSingleton <- as.factor(sTwo_df$nonSingleton)
sTwo_df$age <- as.numeric(sTwo_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sOne_test_df <- read.csv(splitOne_test_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))
sOne_test_df$sex <- as.factor(sOne_test_df$sex)
sOne_test_df$site <- as.factor(sOne_test_df$site)
sOne_test_df$nonSingleton <- as.factor(sOne_test_df$nonSingleton)
sOne_test_df$age <- as.numeric(sOne_test_df$age)

#read in the test dataframes and set variable types, remove NAs in age nonSingleton and sex not M or F.
sTwo_test_df <- read.csv(splitTwo_test_filename)  %>% select(-1) %>% rename(., all_of(rename_vec)) %>% 
  subset(eventname == "baseline_year_1_arm_1" & !is.na(age) & !is.na(nonSingleton) & (sex %in% c("M", "F")))
sTwo_test_df$sex <- as.factor(sTwo_test_df$sex)
sTwo_test_df$site <- as.factor(sTwo_test_df$site)
sTwo_test_df$nonSingleton <- as.factor(sTwo_test_df$nonSingleton)
sTwo_test_df$age <- as.numeric(sTwo_test_df$age)

centiles_reg <- read.csv(reg_centiles_filename)  %>% select(-1)
centiles_global <- read.csv(global_centiles_filename)  %>% select(-1)
centiles_all <- merge(centiles_reg, centiles_global, by = c("src_subject_id", "split_ID"))
rm(centiles_reg, centiles_global)
full_test_df <- rbind(sOne_test_df,sTwo_test_df)
full_test_df <- merge(centiles_all, full_test_df, by = "src_subject_id")
```
#Analyses
##Save scale image
```{r}
library(ggplot2)

# Create dummy data just to generate the colorbar
df <- data.frame(x = 1, y = 1, beta = 0)  # value within the -0.2 to 0.2 range

ggplot(df, aes(x, y, fill = beta)) +
  geom_tile() +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    limits = c(-0.2, 0.2),
    guide = guide_colorbar(
      barwidth = 20,   # length of colorbar
      barheight = 1    # thickness
    )
  ) +
  theme_void() +  # remove axes, grid, etc.
  theme(
    legend.position = "bottom"
  )
```
##Merge data
Get PRS, neonatal complications, birthweight in the same data tables
scrn_birthcomp - any birth complications for >1 month hospitalization?
birth_weight_lbs - birth weight in pounds?
full_abcd
  race_ethinicity variable (to check PRS calculated sample)
  1 - White, 2 - Black, 3 - Hispanic, 4 - Asian, 5 - Other
```{r}
filename_fullfile <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/process_tables_5.1/abcd5.1_long_full_2024-10-04.csv"
filename_prs <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/abcd_clean.csv"
filename_psych1 <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/abcd_longitudinal_psychopathology_factors_scores_full_sample.csv"
filename_psych2 <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/psy_var.RData"
filename_anthro_vars <- "/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/raw_tables_5.1/ph_y_anthro.csv"
full_abcd <- read.csv(filename_fullfile) %>% select(-1) %>% filter(eventname == "baseline_year_1_arm_1")
abcd_prs <- read.csv(filename_prs)
abcd_psych <- read.csv(filename_psych1)
load(filename_psych2)
abcd_anthro <- read.csv(filename_anthro_vars)

#Get composite variable for neonatal complications
neonatal_vars <- c("devhx_14a3_p", "devhx_14b3_p", "devhx_14c3_p", "devhx_14d3_p", "devhx_14e3_p", "devhx_14f3_p", "devhx_14g3_p", "devhx_14h3_p")
#4 rows NAs initially (presumably did not respond to the question)
full_abcd[neonatal_vars] <- lapply(full_abcd[neonatal_vars], function(x) replace(x, x==999, NA))
full_abcd$neonatal_comp_total <- rowSums(full_abcd[neonatal_vars], na.rm = TRUE)

#Regress out the first ten PCs from the PRS scores
model_bw <- lm(bw_pgs ~ PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10, data = abcd_prs)
model_ga <- lm(ga_pgs ~ PC1 + PC2 + PC3 + PC4 + PC5 + PC6 + PC7 + PC8 + PC9 + PC10, data = abcd_prs)
abcd_prs$bw_pgs_resd <- model_bw$residuals
abcd_prs$ga_pgs_resd <- model_ga$residuals
ten_PCs <- paste0("PC", 1:10)

#Match participant names to other dataframes for merge
abcd_prs$participant <- sub("sub-NDAR", "NDAR_", abcd_prs$participant)

#Merge dataframes
test <- merge(full_test_df, full_abcd[,c("scrn_birthcomp","birth_weight_lbs", "birth_weight_oz", "neonatal_comp_total","race_ethnicity", "src_subject_id")], by = c("src_subject_id"), all.x = TRUE)

test <- merge(test, abcd_psych %>% filter(eventname == 1) %>% select(-c("rel_family_id", "interview_age", "eventname")), by = c("src_subject_id"), all.x = TRUE)

test <- merge(test, psy %>% select (-c("age", "sex")), by.x = "src_subject_id", by.y = "IID", all.x = TRUE)

test <- merge(test, abcd_anthro %>% filter(eventname == "baseline_year_1_arm_1"), by = c("src_subject_id"), all.x = TRUE)

test_prs <- merge(test, abcd_prs[,c("bw_pgs", "ga_pgs","ga_pgs_resd", "bw_pgs_resd", "bw", ten_PCs, "participant")], by.x = "src_subject_id", by.y = "participant", all.x = TRUE)
test_prs$birth_weight_sum_oz <- test_prs$birth_weight_lbs*16 + test_prs$birth_weight_oz

#convert birthweight into percentiles using the gitHub growthstandards package which use the intergrowth charts
test_prs <- test_prs %>%
  mutate(birth_weight_kg = birth_weight_sum_oz * 0.0283495) %>%
  mutate(gestAge_days = gestAge*7+3) %>%
  mutate(sexLong = recode(sex, "M" = "Male", "F" = "Female"))

test_prs$bweight_percentile <- igb_wtkg2centile(test_prs$gestAge_days, test_prs$birth_weight_kg, sex = test_prs$sexLong)/100

test_prs$bw_category <- ifelse(test_prs$bweight_percentile < 0.10, "SGA", ifelse(test_prs$bweight_percentile > 0.90, "LGA", "AGA"))
```
##Inter-variable correlations
```{r}
#correlation matrix and visualization
cor_matrix <- cor(test_prs[,c("gestAge", "bw", "bweight_percentile", "neonatal_comp_total", "ga_pgs", "bw_pgs", "General_p")], use = "pairwise.complete.obs")
p_mat <- cor_pmat(test_prs[,c("gestAge", "bw", "bweight_percentile", "neonatal_comp_total", "ga_pgs", "bw_pgs", "General_p")])

ggcorrplot(
  cor_matrix,
  p.mat = p_mat,
  type = "lower",
  insig = "blank",
  lab = TRUE
)
#Fewer Variables
new_df <- test_prs %>% rename(Gestational_Age = gestAge, Total_Neonatal_Comp = neonatal_comp_total, P_factor = General_p, Birthweight = bw)
cor_matrix <- cor(new_df[,c("Gestational_Age", "Birthweight", "Total_Neonatal_Comp", "P_factor")], use = "pairwise.complete.obs")
p_mat <- cor_pmat(new_df[,c("Gestational_Age", "Birthweight", "Total_Neonatal_Comp", "P_factor")])

ggcorrplot(
  cor_matrix,
  p.mat = p_mat,
  type = "lower",
  insig = "blank",
  lab = TRUE
)
```

##Correlations with centile scores
###Gestational Age
```{r}
sum(!is.na(test_prs$gestAge))
ga_zscore <- z_score(test_prs$gestAge)

#Global phenotypes
reg_table_global <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], ga_se = summary$coefficients[2,2])
})))

reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(reg_table_global)), name_mapping$abbreviation)]

reg_table_global_sig <- reg_table_global %>% filter(ga_p < 0.05)
reg_table_global$ga_p_adj <- p.adjust(reg_table_global$ga_p, method = "BH")
reg_table_global_sig_MC <- reg_table_global %>% filter(ga_p_adj < 0.05)

reg_table_global_sig_MC

#Regional phenotypes
reg_table_full <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], ga_se = summary$coefficients[2,2])
})))

reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(reg_table_full)), name_mapping$abbreviation)]

reg_table_full_sig <- reg_table_full %>% filter(ga_p < 0.05)
reg_table_full$ga_p_adj <- p.adjust(reg_table_full$ga_p, method = "BH")
reg_table_full_sig_MC <- reg_table_full %>% filter(ga_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "bw_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_gestAge_all.csv")
  filename_sig <- paste0(output_folder, "dsk_gestAge_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```
####visualization of betas on surface maps
```{r}
#merge with atlas data
plot_data_dkt <- merge(reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
reg_table_full_sig_MC[!(reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

#Setting manual limits (could match the colorbar limits between different variables)
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void()+
  labs(title = "Gestational Age") + 
  theme (plot.title = element_text(hjust = 0.5, size = 20))

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Gestational Age") + 
  theme (plot.title = element_text(hjust = 0.5, size = 20))
```
###birth weight - storing models in list to compare linear and non-linear across phenotypes
```{r}
sum(!is.na(test_prs$birth_weight_sum_oz))
df <- as.data.frame(test_prs[,"src_subject_id"])
df$bw_zscore <- z_score(test_prs$birth_weight_sum_oz)

#Global models save
bw_global_models_list <- lapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  df$x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore, data = df)
})
  
#Global phenotypes -- save betas and p-values
bw_reg_table_global <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  df$x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore, data = df)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4], bw_se = summary$coefficients[2,2])
})))

bw_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bw_reg_table_global)), name_mapping$abbreviation)]

bw_reg_table_global_sig <- bw_reg_table_global %>% filter(bw_p < 0.05)
bw_reg_table_global$bw_p_adj <- p.adjust(bw_reg_table_global$bw_p, method = "BH")
bw_reg_table_global_sig_MC <- bw_reg_table_global %>% filter(bw_p_adj < 0.05)

bw_reg_table_global_sig_MC

#Regional models save
bw_regional_models_list <- lapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  df$x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore, data = df)
})

#Regional phenotypes -- save betas and p-values
bw_reg_table_full <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  df$x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore, data = df)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4], bw_se = summary$coefficients[2,2])
})))

bw_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bw_reg_table_full)), name_mapping$abbreviation)]

bw_reg_table_full_sig <- bw_reg_table_full %>% filter(bw_p < 0.05)
bw_reg_table_full$bw_p_adj <- p.adjust(bw_reg_table_full$bw_p, method = "BH")
bw_reg_table_full_sig_MC <- bw_reg_table_full %>% filter(bw_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- bw_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "bw_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweight_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweight_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```
####visualize on surface
```{r}
#merge with atlas data
plot_data_dkt <- merge(bw_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(bw_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
bw_reg_table_full_sig_MC[!(bw_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(bw_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with BW")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW")
```
####non-linear relationship with birthweight
```{r}
sum(!is.na(test_prs$birth_weight_sum_oz))
df <- as.data.frame(test_prs[,"src_subject_id"])
df$bw_zscore <- z_score(test_prs$birth_weight_sum_oz)

#Global non-linear models save
NLbw_global_models_list <- lapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  df$x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ns(bw_zscore,3), data = df)
})

#Regional non-linear models save
NLbw_regional_models_list <- lapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  df$x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ns(bw_zscore,3), data = df)
})
```

####visualize the nonlinear models
```{r}
##Visualize global models
#Predict on new data
for (i in 1:length(NLbw_global_models_list)){
model <- NLbw_global_models_list[[i]]
x <- test_prs[,names(NLbw_global_models_list)[i]]
df$x_zscore <- qnorm(x)
new_data <- data.frame(bw_zscore = seq(min(df$bw_zscore, na.rm = TRUE), max(df$bw_zscore, na.rm = TRUE), length.out = 100))
new_data$y_pred <- predict(model, newdata = new_data)

#Plot
title <-  as.character(name_mapping$region_name[match(sub("_centiles", "", names(NLbw_global_models_list)[i]), name_mapping$abbreviation)])
p <- ggplot(df, aes(bw_zscore, x_zscore)) +
  geom_point() +
  geom_line(data = new_data, aes(bw_zscore, y_pred), color = "blue", linewidth = 1) + ggtitle(title)
print(p)
}

##Visualize regional models
#Predict on new data
for (i in 1:length(NLbw_regional_models_list)){
model <- NLbw_regional_models_list[[i]]
x <- test_prs[,names(NLbw_regional_models_list)[i]]
df$x_zscore <- qnorm(x)
new_data <- data.frame(bw_zscore = seq(min(df$bw_zscore, na.rm = TRUE), max(df$bw_zscore, na.rm = TRUE), length.out = 100))
new_data$y_pred <- predict(model, newdata = new_data)

#Plot
title <-  as.character(name_mapping$region_name[match(sub("_centiles", "", names(NLbw_regional_models_list)[i]), name_mapping$abbreviation)])
p <- ggplot(df, aes(bw_zscore, x_zscore)) +
  geom_point() +
  geom_line(data = new_data, aes(bw_zscore, y_pred), color = "blue", linewidth = 1) + ggtitle(title)
print(p)
}
```
####Compare linear and non-linear models
```{r}
length_total <- length(NLbw_global_models_list) + length(NLbw_regional_models_list)
bw_modelcompare <- data.frame(label = rep(NA, length_total), phenotype = rep(NA, length_total), pr = rep(NA, length_total))

for(i in 1:length(NLbw_global_models_list)){
 bw_modelcompare$label[i] <- as.character(name_mapping$region_name[match(sub("_centiles", "",names(NLbw_global_models_list)[i]), name_mapping$abbreviation)])
 bw_modelcompare$phenotype[i] <- names(NLbw_global_models_list)[i]
  modelNL <- NLbw_global_models_list[[i]]
  modelOG <- bw_global_models_list[[i]]
  #x <- test_prs[,names(NLbw_global_models_list)[i]]
  #df$x_zscore <- qnorm(x)
  anova <- anova(modelOG, modelNL, test = "LRT")
  bw_modelcompare$pr[i] <- anova$`Pr(>Chi)`[2]
}

for(i in (length(NLbw_global_models_list)+1):length_total){
  j = i - length(NLbw_global_models_list)
 bw_modelcompare$label[i] <- as.character(name_mapping$region_name[match(sub("_centiles", "",names(NLbw_regional_models_list)[j]), name_mapping$abbreviation)])
 bw_modelcompare$phenotype[i] <- names(NLbw_regional_models_list)[j]
  modelNL <- NLbw_regional_models_list[[j]]
  modelOG <- bw_regional_models_list[[j]]
  #x <- test_prs[,names(NLbw_regional_models_list)[i]]
  #df$x_zscore <- qnorm(x)
  anova <- anova(modelOG, modelNL, test = "LRT")
  bw_modelcompare$pr[i] <- anova$`Pr(>Chi)`[2]
}

NL_sig_models <- bw_modelcompare[bw_modelcompare$pr < 0.05,]
```
####Plot models significantly better fit with NL model
```{r}
plot <- TRUE
NLall_models <- c(NLbw_global_models_list, NLbw_regional_models_list)
OGall_models <- c(bw_global_models_list, bw_regional_models_list)
plots_nl <- vector(mode = "list", length = length(NLall_models))
for (i  in 1:length(NLall_models)) {
  modelNL <- NLall_models[[i]]
  modelOG <- OGall_models[[i]]
  if(!(names(NLall_models)[i] %in% NL_sig_models$phenotype)) next
  x <- test_prs[,names(NLall_models)[i]]
 df$x_zscore <- qnorm(x)
 new_data <- data.frame(bw_zscore = seq(min(df$bw_zscore, na.rm = TRUE), max(df$bw_zscore, na.rm = TRUE), length.out = 100))
 new_data$y_predNL <- predict(modelNL, newdata = new_data)
 new_data$y_predOG <- predict(modelOG, newdata = new_data)
 
 #Save plot
 title <-  as.character(name_mapping$region_name[match(sub("_centiles", "", names(NLall_models)[i]),  name_mapping$abbreviation)])
  plots_nl[[i]] <- ggplot(df, aes(bw_zscore, x_zscore)) +
   geom_line(data = new_data, aes(bw_zscore, y_predNL), color = "red", linewidth = 1) + 
    geom_line(data = new_data, aes(bw_zscore, y_predOG), color = "blue", linewidth = 1) +
    ggtitle(title)

}
plots_nl <- Filter(Negate(is.null), plots_nl)
do.call("grid.arrange", c(plots_nl[1:15], ncol=5))

#The code below gives an error ... haven't solved it yet.
if (plot == TRUE){
  n <- length(plots_nl)
  nCol <- min(c(floor(sqrt(n)), 4))
  nRow <- min(ceiling(n/nCol), 4)
  breaks <- c(seq(from = 0, to = n , by = (nCol*nRow)), n)
  for(k in 1:length(breaks)){
    start <- breaks[k] + 1
    end <- breaks[k+1]
    do.call("grid.arrange", c(plots_nl[start:end], ncol=nCol))
  }
}                                



##Visualize models where it is significantly better than linear model
#Predict on new data
for (i in 1:length(NLbw_global_models_list)){
model <- NLbw_global_models_list[[i]]

x <- test_prs[,names(NLbw_global_models_list)[i]]
df$x_zscore <- qnorm(x)
new_data <- data.frame(bw_zscore = seq(min(df$bw_zscore, na.rm = TRUE), max(df$bw_zscore, na.rm = TRUE), length.out = 100))
new_data$y_pred <- predict(model, newdata = new_data)

#Plot
title <-  as.character(name_mapping$region_name[match(sub("_centiles", "", names(NLbw_global_models_list)[i]), name_mapping$abbreviation)])
p <- ggplot(df, aes(bw_zscore, x_zscore)) +
  geom_point() +
  geom_line(data = new_data, aes(bw_zscore, y_pred), color = "blue", linewidth = 1) + ggtitle(title)
print(p)
}

for (i in 1:length(NLbw_regional_models_list)){
model <- NLbw_regional_models_list[[i]]
if(!(names(NLbw_regional_models_list)[i] %in% NL_sig_models$phenotype)){
  stop()
}
x <- test_prs[,names(NLbw_regional_models_list)[i]]
df$x_zscore <- qnorm(x)
new_data <- data.frame(bw_zscore = seq(min(df$bw_zscore, na.rm = TRUE), max(df$bw_zscore, na.rm = TRUE), length.out = 100))
new_data$y_pred <- predict(model, newdata = new_data)

#Plot
title <-  as.character(name_mapping$region_name[match(sub("_centiles", "", names(NLbw_regional_models_list)[i]), name_mapping$abbreviation)])
p <- ggplot(df, aes(bw_zscore, x_zscore)) +
  geom_point() +
  geom_line(data = new_data, aes(bw_zscore, y_pred), color = "blue", linewidth = 1) + ggtitle(title)
print(p)
}
```

###birth weight percentile
```{r}
sum(!is.na(test_prs$bweight_percentile))
bwp_zscore <- qnorm(test_prs$bweight_percentile)

#Global Phenotypes
bwp_reg_table_global <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  
  x_zscore <- qnorm(x)
  x_zscore[is.infinite(x_zscore)] <- NA
  lm <- lm(x_zscore ~ bwp_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4])
})))

bwp_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bwp_reg_table_global)), name_mapping$abbreviation)]

bwp_reg_table_global_sig <- bwp_reg_table_global %>% filter(bw_p < 0.05)
bwp_reg_table_global$bw_p_adj <- p.adjust(bwp_reg_table_global$bw_p, method = "BH")
bwp_reg_table_global_sig_MC <- bwp_reg_table_global %>% filter(bw_p_adj < 0.05)

bwp_reg_table_global_sig_MC

#Regional Phenotypes
bwp_reg_table_full <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  x_zscore[is.infinite(x_zscore)] <- NA
  
  lm <- lm(x_zscore ~ bwp_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4])
})))

bwp_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bwp_reg_table_full)), name_mapping$abbreviation)]

bwp_reg_table_full_sig <- bwp_reg_table_full %>% filter(bw_p < 0.05)
bwp_reg_table_full$bw_p_adj <- p.adjust(bwp_reg_table_full$bw_p, method = "BH")
bwp_reg_table_full_sig_MC <- bwp_reg_table_full %>% filter(bw_p_adj < 0.05)
```
####visualize on surface
```{r}
#merge with atlas data
plot_data_dkt <- merge(bwp_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(bwp_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
bwp_reg_table_full_sig_MC[!(bwp_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(bwp_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with BW - percentile")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW - percentile")
```
###neonatal-comp
```{r}
sum(!is.na(test_prs$neonatal_comp_total))
neo_comp_zscore <- z_score(test_prs$neonatal_comp_total)

#Global Phenotypes
neo_comp_reg_table_global <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ neo_comp_zscore)
  summary <- summary(lm)
  
  c(neo_comp_beta = summary$coefficients[2,1], neo_comp_p = summary$coefficients[2,4])
})))

neo_comp_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(neo_comp_reg_table_global)), name_mapping$abbreviation)]

neo_comp_reg_table_global_sig <- neo_comp_reg_table_global %>% filter(neo_comp_p < 0.05)
neo_comp_reg_table_global$neo_comp_p_adj <- p.adjust(neo_comp_reg_table_global$neo_comp_p, method = "BH")
neo_comp_reg_table_global_sig_MC <- neo_comp_reg_table_global %>% filter(neo_comp_p_adj < 0.05)

neo_comp_reg_table_global_sig_MC 

#Regional phenotypes
neo_comp_reg_table_full <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ neo_comp_zscore)
  summary <- summary(lm)
  
  c(neo_comp_beta = summary$coefficients[2,1], neo_comp_p = summary$coefficients[2,4])
})))

neo_comp_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(neo_comp_reg_table_full)), name_mapping$abbreviation)]

neo_comp_reg_table_full_sig <- neo_comp_reg_table_full %>% filter(neo_comp_p < 0.05)
neo_comp_reg_table_full$neo_comp_p_adj <- p.adjust(neo_comp_reg_table_full$neo_comp_p, method = "BH")
neo_comp_reg_table_full_sig_MC <- neo_comp_reg_table_full %>% filter(neo_comp_p_adj < 0.05)
```
####visualize on surface
```{r}
#merge with atlas data
plot_data_dkt <- merge(neo_comp_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(neo_comp_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
neo_comp_reg_table_full_sig_MC[!(neo_comp_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(neo_comp_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = neo_comp_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with Neonatal Comp.")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = neo_comp_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with Neonatal Comp.")
```
###PRS-bw
```{r}
sum(!is.na(test_prs$bw_pgs))
bw_pgs_zscore <- as.data.frame(sapply(test_prs[,c("bw_pgs", "PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10")], function(x) {z_score(x)}))

#Global Phenotypes
bw_pgs_reg_table_global <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_pgs_zscore$bw_pgs + bw_pgs_zscore$PC1 + bw_pgs_zscore$PC2 + bw_pgs_zscore$PC3 + bw_pgs_zscore$PC4 + bw_pgs_zscore$PC5 + bw_pgs_zscore$PC6 + bw_pgs_zscore$PC7 + bw_pgs_zscore$PC8 + bw_pgs_zscore$PC9 + bw_pgs_zscore$PC10)
  summary <- summary(lm)
  
  c(bw_pgs_beta = summary$coefficients[2,1], bw_pgs_p = summary$coefficients[2,4], bw_pgs_se = summary$coefficients[2,2])
})))

bw_pgs_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bw_pgs_reg_table_global)), name_mapping$abbreviation)]

bw_pgs_reg_table_global_sig <- bw_pgs_reg_table_global %>% filter(bw_pgs_p < 0.05)
bw_pgs_reg_table_global$bw_pgs_p_adj <- p.adjust(bw_pgs_reg_table_global$bw_pgs_p, method = "BH")
bw_pgs_reg_table_global_sig_MC <- bw_pgs_reg_table_global %>% filter(bw_pgs_p_adj < 0.05)

bw_pgs_reg_table_global_sig_MC

#Regional Phenotypes
bw_pgs_reg_table_full <- as.data.frame(t(sapply(test_prs[,which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_pgs_zscore$bw_pgs + bw_pgs_zscore$PC1 + bw_pgs_zscore$PC2 + bw_pgs_zscore$PC3 + bw_pgs_zscore$PC4 + bw_pgs_zscore$PC5 + bw_pgs_zscore$PC6 + bw_pgs_zscore$PC7 + bw_pgs_zscore$PC8 + bw_pgs_zscore$PC9 + bw_pgs_zscore$PC10)
  summary <- summary(lm)
  
  c(bw_pgs_beta = summary$coefficients[2,1], bw_pgs_p = summary$coefficients[2,4], bw_pgs_se = summary$coefficients[2,2])
})))

bw_pgs_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bw_pgs_reg_table_full)), name_mapping$abbreviation)]

bw_pgs_reg_table_full_sig <- bw_pgs_reg_table_full %>% filter(bw_pgs_p < 0.05)
bw_pgs_reg_table_full$bw_pgs_p_adj <- p.adjust(bw_pgs_reg_table_full$bw_pgs_p, method = "BH")
bw_pgs_reg_table_full_sig_MC <- bw_pgs_reg_table_full %>% filter(bw_pgs_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- bw_pgs_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "bw_pgs_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweightPGS_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweightPGS_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```
####visualize on atlas
```{r}
#merge with atlas data
plot_data_dkt <- merge(bw_pgs_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(bw_pgs_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
bw_pgs_reg_table_full_sig_MC[!(bw_pgs_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(bw_pgs_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_pgs_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with BW_pgs")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_pgs_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW_pgs")
```
####correlations with bw
- spin test in Python using neuromaps package
```{r}
bw_bwpgs <- merge(bw_pgs_reg_table_full, bw_reg_table_full, by = c("label"))
#all regions
plot(bw_bwpgs$bw_beta, bw_bwpgs$bw_pgs_beta)
cor.test(bw_bwpgs$bw_beta, bw_bwpgs$bw_pgs_beta)
#only significant post-FDR in both
bw_bwpgs_sig <- bw_bwpgs %>% filter(bw_p_adj < 0.05 & bw_pgs_p_adj < 0.05)
plot(bw_bwpgs_sig$bw_beta, bw_bwpgs_sig$bw_pgs_beta)
cor.test(bw_bwpgs_sig$bw_beta, bw_bwpgs_sig$bw_pgs_beta)
```
###general P-factor
```{r}
sum(!is.na(test_prs$General_p))
gp_zscore <- z_score(test_prs$General_p)

#Global Phenotypes
gp_reg_table_global <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ gp_zscore)
  summary <- summary(lm)
  
  c(gp_beta = summary$coefficients[2,1], gp_p = summary$coefficients[2,4])
})))

gp_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(gp_reg_table_global)), name_mapping$abbreviation)]

gp_reg_table_global_sig <- gp_reg_table_global %>% filter(gp_p < 0.05)
gp_reg_table_global$gp_p_adj <- p.adjust(gp_reg_table_global$gp_p, method = "BH")
gp_reg_table_global_sig_MC <- gp_reg_table_global %>% filter(gp_p_adj < 0.05)

gp_reg_table_global_sig_MC

#Regional Phenotypes
gp_reg_table_full <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ gp_zscore)
  summary <- summary(lm)
  
  c(gp_beta = summary$coefficients[2,1], gp_p = summary$coefficients[2,4])
})))

gp_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(gp_reg_table_full)), name_mapping$abbreviation)]

gp_reg_table_full_sig <- gp_reg_table_full %>% filter(gp_p < 0.05)
gp_reg_table_full$gp_p_adj <- p.adjust(gp_reg_table_full$gp_p, method = "BH")
gp_reg_table_full_sig_MC <- gp_reg_table_full %>% filter(gp_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- gp_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "bw_pgs_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_genP_all.csv")
  filename_sig <- paste0(output_folder, "dsk_genP_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```
####visualize on surface
```{r}
#merge with atlas data
plot_data_dkt <- merge(gp_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(gp_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
gp_reg_table_full_sig_MC[!(gp_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(gp_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = gp_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with P-factor")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = gp_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() 
+
  labs(title = "Subcortical with P-factor")
```
##With Covariates
###GA-BW as cov
```{r}
#regression
ga_zscore <- z_score(test_prs$gestAge)
bw_zscore <- z_score(test_prs$birth_weight_lbs)
neo_comp_zscore <- z_score(test_prs$neonatal_comp_total)
reg_table_full <- as.data.frame(t(sapply(test_prs[, grepl("centiles", names(test_prs))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore + bw_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], bw_beta = summary$coefficients[3,1], bw_p = summary$coefficients[3,4])
})))

reg_table_full_sig <- reg_table_full %>% filter(ga_p < 0.05)
reg_table_full$ga_p_adj <- p.adjust(reg_table_full$ga_p, method = "BH")
reg_table_full_sig_MC <- reg_table_full %>% filter(ga_p_adj < 0.05)
```

####GA coefs
```{r}
reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
reg_table_full_sig_MC[!(reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

#Setting manual limits (could match the colorbar limits between different variables)
# Plot using ggseg
# ggplot(plot_data) +
#   geom_brain(atlas = dk, 
#              position = position_brain(hemi ~ side),
#              aes(fill = correlation.rho)) +
#   scale_fill_gradient2(limits = c(-0.2, 0.2)) +
#   theme_void() +
#   labs(title = "Regions with GA")

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with GA")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with GA")
```
####BW coefs
```{r}
bw_reg_table_full_sig <- reg_table_full %>% filter(bw_p < 0.05)
reg_table_full$bw_p_adj <- p.adjust(reg_table_full$bw_p, method = "BH")
bw_reg_table_full_sig_MC <- reg_table_full %>% filter(bw_p_adj < 0.05)

bw_reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bw_reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(bw_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(bw_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#bw_regions not matched in atlases
bw_reg_table_full_sig_MC[!(bw_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(bw_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with BW")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with BW")
```

###GA-BWpercentile as cov
```{r}
#regression
bwp_ga_reg_table_full <- as.data.frame(t(sapply(test_prs[, grepl("centiles", names(test_prs))], function(x) {
  ga_zscore <- z_score(test_prs$gestAge)
  bwp_zscore <- qnorm(test_prs$bweight_percentile)
  x_zscore <- qnorm(x)
  
  #also omit those cells in ga_zscore and bwp_zscore to match the two vectors
  ga_zscore[is.infinite(x_zscore)] <- NA
  ga_zscore[is.infinite(bwp_zscore)] <- NA
  ga_zscore[is.na(bwp_zscore)] <- NA
  ga_zscore[is.na(x_zscore)] <- NA
  bwp_zscore[is.na(ga_zscore)] <- NA
  x_zscore[is.na(ga_zscore)] <- NA
  ga_zscore <- na.omit(ga_zscore)
  
  bwp_zscore[is.infinite(x_zscore)] <- NA
  bwp_zscore[is.infinite(bwp_zscore)] <- NA
  bwp_zscore[is.na(x_zscore)] <- NA
  x_zscore[is.na(bwp_zscore)] <- NA
  x_zscore[is.infinite(bwp_zscore)] <- NA
  bwp_zscore <- na.omit(bwp_zscore)

  #omit cells with infinite values after applying qnorm
  x_zscore[is.infinite(x_zscore)] <- NA
  x_zscore <- na.omit(x_zscore)
  lm <- lm(x_zscore ~ ga_zscore + bwp_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], bwp_beta = summary$coefficients[3,1], bwp_p = summary$coefficients[3,4])
})))

ga_reg_table_full_sig <- bwp_ga_reg_table_full %>% filter(ga_p < 0.05)
bwp_ga_reg_table_full$ga_p_adj <- p.adjust(bwp_ga_reg_table_full$ga_p, method = "BH")
bwp_ga_reg_table_full$bwp_p_adj <- p.adjust(bwp_ga_reg_table_full$bwp_p, method = "BH")
ga_reg_table_full_sig_MC <- bwp_ga_reg_table_full %>% filter(ga_p_adj < 0.05)
bwpga_reg_table_full_sig <- bwp_ga_reg_table_full %>% filter(bwp_p < 0.05)
bwpga_reg_table_full_sig_MC <- bwp_ga_reg_table_full %>% filter(bwp_p_adj < 0.05)
```
####GA coefs
```{r}
ga_reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(ga_reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(ga_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(ga_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
ga_reg_table_full_sig_MC[!(ga_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(ga_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

#Setting manual limits (could match the colorbar limits between different variables)
# Plot using ggseg
# ggplot(plot_data) +
#   geom_brain(atlas = dk, 
#              position = position_brain(hemi ~ side),
#              aes(fill = correlation.rho)) +
#   scale_fill_gradient2(limits = c(-0.2, 0.2)) +
#   theme_void() +
#   labs(title = "Regions with GA")

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with GA")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with GA")
```
####BWp coefs
```{r}

bwpga_reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bwpga_reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(bwpga_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(bwpga_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#bwpga_regions not matched in atlases
bwpga_reg_table_full_sig_MC[!(bwpga_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(bwpga_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bwp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with BW Percentile")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bwp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with BW Percentile")
```

###GA-NeoComp as cov
Look at the predicted centiles (from cross model) with GA, whole sample
```{r}
#regression
ga_zscore <- z_score(test_prs$gestAge)
bw_zscore <- z_score(test_prs$birth_weight_lbs)
neo_comp_zscore <- z_score(test_prs$neonatal_comp_total)
reg_table_full <- as.data.frame(t(sapply(full_test_df[, grepl("centiles", names(full_test_df))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore + neo_comp_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], neo_comp_beta = summary$coefficients[3,1], neo_comp_p = summary$coefficients[3,4])
})))

reg_table_full_sig <- reg_table_full %>% filter(ga_p < 0.05)
reg_table_full$ga_p_adj <- p.adjust(reg_table_full$ga_p, method = "BH")
reg_table_full$neo_comp_p_adj <- p.adjust(reg_table_full$neo_comp_p, method = "BH")
reg_table_full_sig_MC <- reg_table_full %>% filter(ga_p_adj < 0.05)
```

####GA coefs
```{r}
reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
reg_table_full_sig_MC[!(reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

#Setting manual limits (could match the colorbar limits between different variables)
# Plot using ggseg
# ggplot(plot_data) +
#   geom_brain(atlas = dk, 
#              position = position_brain(hemi ~ side),
#              aes(fill = correlation.rho)) +
#   scale_fill_gradient2(limits = c(-0.2, 0.2)) +
#   theme_void() +
#   labs(title = "Regions with GA")

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with GA")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with GA")
```


####NeoComp coefs
```{r}
neo_comp_reg_table_full_sig <- reg_table_full %>% filter(neo_comp_p < 0.05)
neo_comp_reg_table_full_sig_MC <- reg_table_full %>% filter(neo_comp_p_adj < 0.05)

neo_comp_reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(neo_comp_reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(neo_comp_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(neo_comp_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#neo_comp_regions not matched in atlases
neo_comp_reg_table_full_sig_MC[!(neo_comp_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(neo_comp_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = neo_comp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with Neo Comp")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = neo_comp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with Neo Comp")
```


###GA - BW and Neo Comp as Covar
```{r}
#regression
ga_zscore <- z_score(test_prs$gestAge)
bw_zscore <- z_score(test_prs$birth_weight_lbs)
neo_comp_zscore <- z_score(test_prs$neonatal_comp_total)
reg_table_full <- as.data.frame(t(sapply(full_test_df[, grepl("centiles", names(full_test_df))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore + bw_zscore + neo_comp_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], bw_beta = summary$coefficients[3,1], bw_p = summary$coefficients[3,4], neo_comp_beta = summary$coefficients[4,1], neo_comp_p = summary$coefficients[4,4])
})))

reg_table_full_sig <- reg_table_full %>% filter(ga_p < 0.05)
reg_table_full$ga_p_adj <- p.adjust(reg_table_full$ga_p, method = "BH")
reg_table_full_sig_MC <- reg_table_full %>% filter(ga_p_adj < 0.05)
```
####GA coefs
```{r}
reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
reg_table_full_sig_MC[!(reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

#Setting manual limits (could match the colorbar limits between different variables)
# Plot using ggseg
# ggplot(plot_data) +
#   geom_brain(atlas = dk, 
#              position = position_brain(hemi ~ side),
#              aes(fill = correlation.rho)) +
#   scale_fill_gradient2(limits = c(-0.2, 0.2)) +
#   theme_void() +
#   labs(title = "Regions with GA")

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with GA")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with GA")
```


###BW percentile - BW PGS as covar -- adapted to global/regional MC
```{r}
sum(!is.na(test_prs$bw_pgs))
bw_pgs_zscore <- as.data.frame(sapply(test_prs[,c("bw_pgs", "PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10")], function(x) {z_score(x)}))
bw_pgs_zscore$bw_zscore <- qnorm(test_prs$bweight_percentile)
#bw_pgs_zscore$bw_zscore <- z_score(test_prs$birth_weight_sum_oz)

#Global variables
bw_bwpgs_reg_table_global <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_pgs_zscore$bw_pgs + bw_pgs_zscore$bw_zscore + bw_pgs_zscore$PC1 + bw_pgs_zscore$PC2 + bw_pgs_zscore$PC3 + bw_pgs_zscore$PC4 + bw_pgs_zscore$PC5 + bw_pgs_zscore$PC6 + bw_pgs_zscore$PC7 + bw_pgs_zscore$PC8 + bw_pgs_zscore$PC9 + bw_pgs_zscore$PC10)
  summary <- summary(lm)
  
  c(bw_pgs_beta = summary$coefficients[2,1], bw_pgs_p = summary$coefficients[2,4], bw_pgs_se = summary$coefficients[2,2], bw_beta = summary$coefficients[3,1], bw_p = summary$coefficients[3,4], bw_se = summary$coefficients[3,2])
})))

bw_bwpgs_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bw_bwpgs_reg_table_global)), name_mapping$abbreviation)]

bw_bwpgs_reg_table_global_sig <- bw_bwpgs_reg_table_global %>% filter(bw_pgs_p < 0.05)
bw_bwpgs_reg_table_global$bw_pgs_p_adj <- p.adjust(bw_bwpgs_reg_table_global$bw_pgs_p, method = "BH")
bw_bwpgs_reg_table_global_sig_MC <- bw_bwpgs_reg_table_global %>% filter(bw_pgs_p_adj < 0.05)

bw_bwpgs_reg_table_global_sig_MC


#Regional variables
bw_bwpgs_reg_table_full <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_pgs_zscore$bw_pgs + bw_pgs_zscore$bw_zscore + bw_pgs_zscore$PC1 + bw_pgs_zscore$PC2 + bw_pgs_zscore$PC3 + bw_pgs_zscore$PC4 + bw_pgs_zscore$PC5 + bw_pgs_zscore$PC6 + bw_pgs_zscore$PC7 + bw_pgs_zscore$PC8 + bw_pgs_zscore$PC9 + bw_pgs_zscore$PC10)
  summary <- summary(lm)
  
  c(bw_pgs_beta = summary$coefficients[2,1], bw_pgs_p = summary$coefficients[2,4], bw_pgs_se = summary$coefficients[2,2], bw_beta = summary$coefficients[3,1], bw_p = summary$coefficients[3,4], bw_se = summary$coefficients[3,2])
})))

bw_bwpgs_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bw_bwpgs_reg_table_full)), name_mapping$abbreviation)]

bw_bwpgs_reg_table_full_sig <- bw_bwpgs_reg_table_full %>% filter(bw_pgs_p < 0.05)
bw_bwpgs_reg_table_full$bw_pgs_p_adj <- p.adjust(bw_bwpgs_reg_table_full$bw_pgs_p, method = "BH")
bw_bwpgs_reg_table_full_sig_MC <- bw_bwpgs_reg_table_full %>% filter(bw_pgs_p_adj < 0.05)
```
####surface visualization of bw-pgs beta
```{r}

#merge with atlas data
plot_data_dkt <- merge(bw_bwpgs_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(bw_bwpgs_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
bw_bwpgs_reg_table_full_sig_MC[!(bw_bwpgs_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(bw_bwpgs_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_pgs_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with BW_pgs, covar BWpercentile")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_pgs_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW_pgs, covar BWpercentile")
```
###BW - weight & height as covar
```{r}
cor.test(test_prs$birth_weight_lbs, test_prs$anthroweightcalc)
cor.test(test_prs$birth_weight_lbs, test_prs$anthroheightcalc)
bw_wh_reg_table_full <- as.data.frame(t(sapply(test_prs[, grepl("centiles", names(test_prs))], function(x) {
  weight_zscore <- z_score(test_prs$anthroweightcalc)
  height_zscore <- z_score(test_prs$anthroheightcalc)
  bw_zscore <- z_score(test_prs$birth_weight_lbs)
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore + weight_zscore + height_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4], weight_beta = summary$coefficients[3,1], weight_p = summary$coefficients[3,4], height_beta = summary$coefficients[4,1], height_p = summary$coefficients[4,4])
})))

bw_wh_reg_table_full$bw_p_adj <- p.adjust(bw_wh_reg_table_full$bw_p, method = "BH")
bw_wh_reg_table_full$weight_p_adj <- p.adjust(bw_wh_reg_table_full$weight_p, method = "BH")
bw_wh_reg_table_full$height_p_adj <- p.adjust(bw_wh_reg_table_full$height_p, method = "BH")

bw_reg_table_full_sig_MC <- bw_wh_reg_table_full %>% filter(bw_p_adj < 0.05)
weight_reg_table_full_sig_MC <- bw_wh_reg_table_full %>% filter(weight_p_adj < 0.05)
height_reg_table_full_sig_MC <- bw_wh_reg_table_full %>% filter(height_p_adj < 0.05)
```

```{r}
bw_reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bw_reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(bw_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(bw_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
bw_reg_table_full_sig_MC[!(bw_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(bw_reg_table_full_sig_MC$label %in% plot_data_aseg$label),c("bw_beta", "bw_p_adj", "label")]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with BW")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with BW")
```
##Interactions
###GA*BW
```{r}
ga_zscore <- z_score(test_prs$gestAge)
bw_zscore <- z_score(test_prs$birth_weight_sum_oz)
neo_comp_zscore <- z_score(test_prs$neonatal_comp_total)

#Global phenotypes
gabw_reg_table_global <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore*bw_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], ga_se = summary$coefficients[2,2],
    bw_beta = summary$coefficients[3,1], bw_p = summary$coefficients[3,4], bw_se = summary$coefficients[2,3],
    gabw_beta = summary$coefficients[4,1], gabw_p = summary$coefficients[4,4], gabw_se = summary$coefficients[2,4])
})))

gabw_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(gabw_reg_table_global)), name_mapping$abbreviation)]

#gabw_regional Phenotypes
gabw_reg_table_full <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore*bw_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], ga_se = summary$coefficients[2,2], 
    bw_beta = summary$coefficients[3,1], bw_p = summary$coefficients[3,4], bw_se = summary$coefficients[2,3],
    gabw_beta = summary$coefficients[4,1], gabw_p = summary$coefficients[4,4], gabw_se = summary$coefficients[2,4])
})))

gabw_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(gabw_reg_table_full)), name_mapping$abbreviation)]

gabw_reg_table_full$ga_p_adj <- p.adjust(gabw_reg_table_full$ga_p, method = "BH")
gabw_reg_table_full$bw_p_adj <- p.adjust(gabw_reg_table_full$bw_p, method = "BH")
gabw_reg_table_full$gabw_p_adj <- p.adjust(gabw_reg_table_full$gabw_p, method = "BH")

ga_reg_table_full_sig <- gabw_reg_table_full %>% filter(ga_p < 0.05)
bw_reg_table_full_sig <- gabw_reg_table_full %>% filter(bw_p < 0.05)
gabw_reg_table_full_sig <- gabw_reg_table_full %>% filter(gabw_p < 0.05)

ga_reg_table_full_sig_MC <- gabw_reg_table_full %>% filter(ga_p_adj < 0.05)
bw_reg_table_full_sig_MC <- gabw_reg_table_full %>% filter(bw_p_adj < 0.05)
gabw_reg_table_full_sig_MC <- gabw_reg_table_full %>% filter(gabw_p_adj < 0.05)
```
####GA coefs
```{r}
#merge with atlas data
plot_data_dkt <- merge(ga_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(ga_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#ga_regions not matched in atlases
ga_reg_table_full_sig_MC[!(ga_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(ga_reg_table_full_sig_MC$label %in% plot_data_aseg$label),c ("ga_beta", "ga_p_adj", "label")]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical ga_regions with GA")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with GA")
```
####BW coefs

####interaction effect (surface plots)
13 regions significant, but only 1 after correcting for MC
```{r}
gabw_reg_table_full_sig$label <- name_mapping$region_name[match(sub(".t2_centiles", "", rownames(gabw_reg_table_full_sig)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(gabw_reg_table_full_sig, ggseg::dk, by = "label")
plot_data_aseg <- merge(gabw_reg_table_full_sig, ggseg::aseg, by = "label")

#gabw_regions not matched in atlases
gabw_reg_table_full_sig[!(gabw_reg_table_full_sig$label %in% plot_data_dkt$label) & !(gabw_reg_table_full_sig$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = gabw_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with gabw")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = gabw_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with gabw")
```
####visualize the interaction(interaction plots)
```{r}
vars <- rownames(gabw_reg_table_full_sig[order(-(gabw_reg_table_full_sig$gabw_beta)),])
ga_zscore <- z_score(test_prs$gestAge)
bw_zscore <- z_score(test_prs$birth_weight_lbs)
neo_comp_zscore <- z_score(test_prs$neonatal_comp_total)
interaction_plots <-  vector(mode = "list", length = length(vars))
for (i in 1:length(vars)){
  x <- test_prs[,grepl(vars[i], names(test_prs))]
  y_label <- name_mapping$region_name[match(sub("_centiles", "", vars[i]), name_mapping$abbreviation)]
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore*bw_zscore)
  summary <- summary(lm)
  interaction_plots[[i]] <- interact_plot(lm, pred = bw_zscore, modx = ga_zscore, modx.values = c(-5.48052197636876, -4.11781530029582, -3.20934418291386, -2.30087306553191,  -1.39240194814995,-0.483930830767994 , 0.424540286613962), modx.labels = c("27", "30", "32", "34", "36", "38", "40")) + ylab(y_label) + ggtitle(paste0("gabw beta = ", as.character(signif(summary$coefficients[4,1], 3))))
}

#n <- length(interaction_plots)
nCol <- 4
do.call("grid.arrange", c(interaction_plots[1:8], ncol=nCol))
do.call("grid.arrange", c(interaction_plots[9:13], ncol=nCol))
```
###GA*BWpercentile
```{r}
ga_zscore <- z_score(test_prs$gestAge)
bwp_zscore <- z_score(test_prs$birth_weight_sum_oz)
neo_comp_zscore <- z_score(test_prs$neonatal_comp_total)

#Global phenotypes
gabwp_reg_table_global <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore*bwp_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], ga_se = summary$coefficients[2,2],
    bwp_beta = summary$coefficients[3,1], bwp_p = summary$coefficients[3,4], bwp_se = summary$coefficients[2,3],
    gabwp_beta = summary$coefficients[4,1], gabwp_p = summary$coefficients[4,4], gabwp_se = summary$coefficients[2,4])
})))

gabwp_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(gabwp_reg_table_global)), name_mapping$abbreviation)]

#gabwp_regional Phenotypes
gabwp_reg_table_full <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore*bwp_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], ga_se = summary$coefficients[2,2], 
    bwp_beta = summary$coefficients[3,1], bwp_p = summary$coefficients[3,4], bwp_se = summary$coefficients[2,3],
    gabwp_beta = summary$coefficients[4,1], gabwp_p = summary$coefficients[4,4], gabwp_se = summary$coefficients[2,4])
})))

gabwp_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(gabwp_reg_table_full)), name_mapping$abbreviation)]

gabwp_reg_table_full$ga_p_adj <- p.adjust(gabwp_reg_table_full$ga_p, method = "BH")
gabwp_reg_table_full$bwp_p_adj <- p.adjust(gabwp_reg_table_full$bwp_p, method = "BH")
gabwp_reg_table_full$gabwp_p_adj <- p.adjust(gabwp_reg_table_full$gabwp_p, method = "BH")

ga_reg_table_full_sig <- gabwp_reg_table_full %>% filter(ga_p < 0.05)
bwp_reg_table_full_sig <- gabwp_reg_table_full %>% filter(bwp_p < 0.05)
gabwp_reg_table_full_sig <- gabwp_reg_table_full %>% filter(gabwp_p < 0.05)

ga_reg_table_full_sig_MC <- gabwp_reg_table_full %>% filter(ga_p_adj < 0.05)
bwp_reg_table_full_sig_MC <- gabwp_reg_table_full %>% filter(bwp_p_adj < 0.05)
gabwp_reg_table_full_sig_MC <- gabwp_reg_table_full %>% filter(gabwp_p_adj < 0.05)
```
####GA coefs
```{r}
#merge with atlas data
plot_data_dkt <- merge(ga_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(ga_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#ga_regions not matched in atlases
ga_reg_table_full_sig_MC[!(ga_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(ga_reg_table_full_sig_MC$label %in% plot_data_aseg$label),c("ga_beta", "ga_p_adj", "label")]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical ga_regions with GA")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with GA")
```
####bwp coefs
```{r}
#merge with atlas data
plot_data_dkt <- merge(bwp_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(bwp_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#bwp_regions not matched in atlases
bwp_reg_table_full_sig_MC[!(bwp_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(bwp_reg_table_full_sig_MC$label %in% plot_data_aseg$label),c("bwp_beta", "bwp_p_adj", "label")]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bwp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical bwp_regions with BWp")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bwp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with BWp")
```
####interaction effect (surface plots)
```{r}
#merge with atlas data
plot_data_dkt <- merge(gabwp_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(gabwp_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#gabwp_regions not matched in atlases
gabwp_reg_table_full_sig_MC[!(gabwp_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(gabwp_reg_table_full_sig_MC$label %in% plot_data_aseg$label),c("gabwp_beta", "gabwp_p_adj", "label")]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = gabwp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with GAxBWp")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = gabwp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with GAxBWp")
```
####visualize the interaction(interaction plots)
```{r}
vars <- rownames(gabwp_reg_table_full_sig_MC[order(-abs(gabwp_reg_table_full_sig_MC$gabwp_beta)),])
ga_zscore <- z_score(test_prs$gestAge)
bwp_zscore <- qnorm(test_prs$bweight_percentile)
bwp_zscore[is.infinite(bwp_zscore)] <- NA
interaction_plots <-  vector(mode = "list", length = length(vars))
for (i in 1:length(vars)){
  x <- test_prs[,grepl(vars[i], names(test_prs))]
  y_label <- name_mapping$region_name[match(sub("_centiles", "", vars[i]), name_mapping$abbreviation)]
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore*bwp_zscore)
  summary <- summary(lm)
  interaction_plots[[i]] <- interact_plot(lm, pred = bwp_zscore, modx = ga_zscore, modx.values = c(-5.48052197636876, -4.11781530029582, -3.20934418291386, -2.30087306553191,  -1.39240194814995,-0.483930830767994 , 0.424540286613962), modx.labels = c("27", "30", "32", "34", "36", "38", "40")) + ylab(y_label) + ggtitle(paste0("gabwp beta = ", as.character(signif(summary$coefficients[4,1], 3))))
}

n <- length(interaction_plots)
nCol <- min(c(floor(sqrt(n)), 4))
nRow <- min(ceiling(n/nCol), 4)
breaks <- c(seq(from = 0, to = n , by = (nCol*nRow)), n)
for(k in 1:length(breaks)){
  start <- breaks[k] + 1
  end <- breaks[k+1]
  do.call("grid.arrange", c(interaction_plots[start:end], ncol=nCol))
}
```
###GA*BW
##Behavioral
###Define behavioral variables
```{r}
beh_vars<-c("Factor1","Factor2","Factor3","Factor4","Factor5","Factor6","Factor7","Factor8","General_p","anxdep","withdep","somatic","social","thought","attention","rulebreak","aggressive","totprob")
```
###General P Factor
```{r}
ga_zscore <- z_score(test_prs$gestAge)
bw_zscore <- z_score(test_prs$birth_weight_lbs)
bw_zscore2 <- bw_zscore^2
neo_comp_zscore <- z_score(test_prs$neonatal_comp_total)
lm_ga <- lm(General_p ~ ga_zscore, data = test_prs)
summary(lm_ga)

plot(ga_zscore, test_prs$General_p)

lm_bw <- lm(General_p ~ bw_zscore, data = test_prs)
summary(lm_bw)
plot(lm_bw)

plot(bw_zscore, test_prs$General_p)

lm_neo <- lm(General_p ~ neo_comp_zscore, data = test_prs)
summary(lm_neo)

plot(neo_comp_zscore, test_prs$General_p)

lm_gabw <- lm(General_p ~ ga_zscore + bw_zscore, data = test_prs)
summary(lm_gabw)

lm_gabwneo <- lm(General_p ~ ga_zscore + bw_zscore + neo_comp_zscore, data = test_prs)
summary(lm_gabwneo)

lm_bwneo <- lm(General_p ~  bw_zscore + neo_comp_zscore, data = test_prs)
summary(lm_bwneo)

lm_ganeo <- lm(General_p ~ ga_zscore + neo_comp_zscore, data = test_prs)
summary(lm_ganeo)
```
##Correlations with centile scores - controlling for total brain volume in the regression
###Gestational Age
```{r}
ga_zscore <- z_score(full_test_df$gestAge)
total_volume_zcore <- qnorm(test_prs$smri_vol_scs_intracranialv_centiles)

#Global phenotypes
reg_table_global <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
lm <- lm(x_zscore ~ ga_zscore + total_volume_zcore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], ga_se = summary$coefficients[2,2])
})))

reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(reg_table_global)), name_mapping$abbreviation)]

reg_table_global_sig <- reg_table_global %>% filter(ga_p < 0.05)
reg_table_global$ga_p_adj <- p.adjust(reg_table_global$ga_p, method = "BH")
reg_table_global_sig_MC <- reg_table_global %>% filter(ga_p_adj < 0.05)

reg_table_global_sig_MC

#Regional phenotypes
reg_table_full <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore + total_volume_zcore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4], ga_se = summary$coefficients[2,2])
})))

reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(reg_table_full)), name_mapping$abbreviation)]

reg_table_full_sig <- reg_table_full %>% filter(ga_p < 0.05)
reg_table_full$ga_p_adj <- p.adjust(reg_table_full$ga_p, method = "BH")
reg_table_full_sig_MC <- reg_table_full %>% filter(ga_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "bw_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_gestAge_ICVcorrect_all.csv")
  filename_sig <- paste0(output_folder, "dsk_gestAge_ICVcorrect_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```

```{r}
#merge with atlas data
plot_data_dkt <- merge(reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
reg_table_full_sig_MC[!(reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with GA")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with GA")
```
###birth weight
```{r}
sum(!is.na(test_prs$birth_weight_sum_oz))
df <- as.data.frame(test_prs[,"src_subject_id"])
df$bw_zscore <- z_score(test_prs$birth_weight_sum_oz)
df$total_volume_zcore <- qnorm(test_prs$smri_vol_scs_intracranialv_centiles)

#Global phenotypes -- save betas and p-values
bw_reg_table_global <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  df$x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore + total_volume_zcore, data = df)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4], bw_se = summary$coefficients[2,2])
})))

bw_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bw_reg_table_global)), name_mapping$abbreviation)]

bw_reg_table_global_sig <- bw_reg_table_global %>% filter(bw_p < 0.05)
bw_reg_table_global$bw_p_adj <- p.adjust(bw_reg_table_global$bw_p, method = "BH")
bw_reg_table_global_sig_MC <- bw_reg_table_global %>% filter(bw_p_adj < 0.05)

bw_reg_table_global_sig_MC

#Regional phenotypes -- save betas and p-values
bw_reg_table_full <- as.data.frame(t(sapply(test_prs[, which(names(test_prs) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  df$x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore + total_volume_zcore, data = df)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4], bw_se = summary$coefficients[2,2])
})))

bw_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bw_reg_table_full)), name_mapping$abbreviation)]

bw_reg_table_full_sig <- bw_reg_table_full %>% filter(bw_p < 0.05)
bw_reg_table_full$bw_p_adj <- p.adjust(bw_reg_table_full$bw_p, method = "BH")
bw_reg_table_full_sig_MC <- bw_reg_table_full %>% filter(bw_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- bw_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "bw_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweight_ICVcorrect_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweight_ICVcorrect_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```
####visualize on surface
```{r}
#merge with atlas data
plot_data_dkt <- merge(bw_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(bw_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
bw_reg_table_full_sig_MC[!(bw_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(bw_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with BW")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW")
```
###birth weight percentile
```{r}
bwp_reg_table_full <- as.data.frame(t(sapply(test_prs[, grepl("centiles", names(test_prs))], function(x) {
  bwp_zscore <- qnorm(test_prs$bweight_percentile)
  x_zscore <- qnorm(x)
  #also omit those cells in bwp_zscore to match the two vectors
  bwp_zscore[is.infinite(x_zscore)] <- NA
  bwp_zscore[is.na(x_zscore)] <- NA
  x_zscore[is.infinite(bwp_zscore)] <- NA
  bwp_zscore[is.infinite(bwp_zscore)] <- NA
  x_zscore[is.na(bwp_zscore)] <- NA
  bwp_zscore <- na.omit(bwp_zscore)
  #omit cells with infinite values after applying qnorm
  x_zscore[is.infinite(x_zscore)] <- NA
  x_zscore <- na.omit(x_zscore)
  
  lm <- lm(x_zscore ~ bwp_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4])
})))

bwp_reg_table_full_sig <- bwp_reg_table_full %>% filter(bw_p < 0.05)
bwp_reg_table_full$bw_p_adj <- p.adjust(bwp_reg_table_full$bw_p, method = "BH")
bwp_reg_table_full_sig_MC <- bwp_reg_table_full %>% filter(bw_p_adj < 0.05)
```

```{r}
bwp_reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bwp_reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(bwp_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(bwp_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
bwp_reg_table_full_sig_MC[!(bwp_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(bwp_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with BW - percentile")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with BW - percentile")
```
###neonatal-comp
```{r}
neo_comp_zscore <- z_score(test_prs$neonatal_comp_total)
neo_comp_reg_table_full <- as.data.frame(t(sapply(test_prs[, grepl("centiles", names(test_prs))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ neo_comp_zscore)
  summary <- summary(lm)
  
  c(neo_comp_beta = summary$coefficients[2,1], neo_comp_p = summary$coefficients[2,4])
})))

neo_comp_reg_table_full_sig <- neo_comp_reg_table_full %>% filter(neo_comp_p < 0.05)
neo_comp_reg_table_full$neo_comp_p_adj <- p.adjust(neo_comp_reg_table_full$neo_comp_p, method = "BH")
neo_comp_reg_table_full_sig_MC <- neo_comp_reg_table_full %>% filter(neo_comp_p_adj < 0.05)
```

```{r}
neo_comp_reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(neo_comp_reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(neo_comp_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(neo_comp_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
neo_comp_reg_table_full_sig_MC[!(neo_comp_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(neo_comp_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = neo_comp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with Neonatal Comp.")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = neo_comp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with Neonatal Comp.")
```
###PRS-bw
```{r}
bw_pgs_zscore <- as.data.frame(sapply(test_prs[,c("bw_pgs", "PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10")], function(x) {z_score(x)}))

bw_pgs_reg_table_full <- as.data.frame(t(sapply(test_prs[, grepl("centiles", names(test_prs))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_pgs_zscore$bw_pgs + 
 bw_pgs_zscore$PC1 + bw_pgs_zscore$PC2 + bw_pgs_zscore$PC3 + bw_pgs_zscore$PC4 + bw_pgs_zscore$PC5 + bw_pgs_zscore$PC6 + bw_pgs_zscore$PC7 + bw_pgs_zscore$PC8 + bw_pgs_zscore$PC9 + bw_pgs_zscore$PC10)
  summary <- summary(lm)
  
  c(bw_pgs_beta = summary$coefficients[2,1], bw_pgs_p = summary$coefficients[2,4])
})))

bw_pgs_reg_table_full_sig <- bw_pgs_reg_table_full %>% filter(bw_pgs_p < 0.05)
bw_pgs_reg_table_full$bw_pgs_p_adj <- p.adjust(bw_pgs_reg_table_full$bw_pgs_p, method = "BH")
bw_pgs_reg_table_full_sig_MC <- bw_pgs_reg_table_full %>% filter(bw_pgs_p_adj < 0.05)
```

```{r}
bw_pgs_reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(bw_pgs_reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(bw_pgs_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(bw_pgs_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
bw_pgs_reg_table_full_sig_MC[!(bw_pgs_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(bw_pgs_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_pgs_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with BW_pgs")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_pgs_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with BW_pgs")
```

###general P-factor
```{r}
gp_zscore <- z_score(test_prs$General_p)
gp_reg_table_full <- as.data.frame(t(sapply(test_prs[, grepl("centiles", names(test_prs))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ gp_zscore)
  summary <- summary(lm)
  
  c(gp_beta = summary$coefficients[2,1], gp_p = summary$coefficients[2,4])
})))

gp_reg_table_full_sig <- gp_reg_table_full %>% filter(gp_p < 0.05)
gp_reg_table_full$gp_p_adj <- p.adjust(gp_reg_table_full$gp_p, method = "BH")
gp_reg_table_full_sig_MC <- gp_reg_table_full %>% filter(gp_p_adj < 0.05)
```

```{r}
gp_reg_table_full_sig_MC$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(gp_reg_table_full_sig_MC)), name_mapping$abbreviation)]

#merge with atlas data
plot_data_dkt <- merge(gp_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(gp_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
gp_reg_table_full_sig_MC[!(gp_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(gp_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = gp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Cortical Regions with gp")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = gp_beta)) +
  scale_fill_gradient2() +
  theme_void() +
  labs(title = "Subcortical with gp")
```
##Plot Beta Ranges and Compare Betas
###Gestational Age univariate, Gestational Age + Birth Weight model comparisons
```{r}
#univariate x~ga regression
reg_table_full_sig_MC$ga_lower <- (reg_table_full_sig_MC$ga_beta - 1.96*reg_table_full_sig_MC$ga_se)
reg_table_full_sig_MC$ga_upper <- (reg_table_full_sig_MC$ga_beta + 1.96*reg_table_full_sig_MC$ga_se)
reg_table_full_sig_MC <- reg_table_full_sig_MC %>% mutate(lm = "ga_uni")

#multivariate x~ga*bw regression, significant for ga_beta
ga_reg_table_full_sig_MC$ga_lower <- (ga_reg_table_full_sig_MC$ga_beta - 1.96*ga_reg_table_full_sig_MC$ga_se)
ga_reg_table_full_sig_MC$ga_upper <- (ga_reg_table_full_sig_MC$ga_beta + 1.96*ga_reg_table_full_sig_MC$ga_se)
ga_reg_table_full_sig_MC_plot <- ga_reg_table_full_sig_MC %>% mutate(lm = "gabw_cov") %>% select(all_of(names(reg_table_full_sig_MC)))

#combine tables
combined_reg_table <- rbind(reg_table_full_sig_MC, ga_reg_table_full_sig_MC_plot)
```
####plot betas with 95% CI
```{r}
ggplot() + geom_pointrange(data = reg_table_full_sig_MC, aes(y = label, x = ga_beta, xmin = ga_lower, xmax = ga_upper, color = blue)) +
  geom_pointrange(data = reg_table_full_sig_MC, aes(y = label, x = ga_beta, xmin = ga_lower, xmax = ga_upper, color = red)) +
  theme_minimal() +
  xlab("Beta Coefficient") +
  ggtitle("GA with Centile Scores")

# Plot
ggplot(combined_reg_table, aes(y = label, x = ga_beta, xmin = ga_lower, xmax = ga_upper, color = lm)) +
geom_pointrange(size = 0.3) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 5, margin = margin(r = 10)),  # space labels
        axis.title.y = element_text(margin = margin(r = 15))             # space title
        ) +
  scale_y_discrete(expand = expansion(mult = c(0.1, 0.1))) +
  scale_color_manual(values = c("ga_uni" = "blue", "gabw_cov" = "magenta")) +
  labs(x = "Beta Estimate", y = "Phenotype", color = "Regression Type")

```

###BW univariate, BW + BW+bw-pgs model comparisons
```{r}
#univariate x~ga regression
bw_reg_table_full_sig_MC$bw_lower <- (bw_reg_table_full_sig_MC$bw_beta - 1.96*bw_reg_table_full_sig_MC$bw_se)
bw_reg_table_full_sig_MC$bw_upper <- (bw_reg_table_full_sig_MC$bw_beta + 1.96*bw_reg_table_full_sig_MC$bw_se)
bw_reg_table_full_sig_MC <- bw_reg_table_full_sig_MC %>% mutate(lm = "bw_uni")

#multivariate x~ga*bw regression, significant for ga_beta
bw_pgs_reg_table_full_sig_MC$bw_lower <- (bw_pgs_reg_table_full_sig_MC$bw_beta - 1.96*bw_pgs_reg_table_full_sig_MC$bw_se)
bw_pgs_reg_table_full_sig_MC$bw_upper <- (bw_pgs_reg_table_full_sig_MC$bw_beta + 1.96*bw_pgs_reg_table_full_sig_MC$bw_se)
bw_pgs_reg_table_full_sig_MC_plot <- bw_pgs_reg_table_full_sig_MC %>% mutate(lm = "bwpgs_cov") %>% select(all_of(names(bw_reg_table_full_sig_MC)))

#combine tables
combined_reg_table <- rbind(bw_reg_table_full_sig_MC, bw_pgs_reg_table_full_sig_MC_plot)

# Z-test to statistically test change in betas
shared_phenotypes <- bw_reg_table_full_sig_MC$label[bw_reg_table_full_sig_MC$label %in% bw_pgs_reg_table_full_sig_MC$label]
ztest_df <- data.frame(phenotype = character(length(shared_phenotypes)), 
                        label = character(length(shared_phenotypes)), 
                        p_value = numeric(length(shared_phenotypes)))
for(i in 1:length(shared_phenotypes)){
  beta1 = bw_reg_table_full_sig_MC[which(bw_reg_table_full_sig_MC$label == shared_phenotypes[i]), "bw_beta"]
  se1 = bw_reg_table_full_sig_MC[which(bw_reg_table_full_sig_MC$label == shared_phenotypes[i]), "bw_se"]
  beta2 = bw_pgs_reg_table_full_sig_MC[which(bw_pgs_reg_table_full_sig_MC$label == shared_phenotypes[i]), "bw_beta"]
  se2 = bw_pgs_reg_table_full_sig_MC[which(bw_pgs_reg_table_full_sig_MC$label == shared_phenotypes[i]), "bw_se"]
  z <- (beta1 - beta2) / sqrt(se1^2 + se2^2)
  # One-tailed p-value for testing if beta2 is significantly smaller than beta1 
  #(bw_beta smaller when bw-pgs is included in the model)
  p_value <- pnorm(z)
  # #Two tailed
  # p_value <- 2 * pnorm(-abs(z))
  ztest_df$label[i] <- shared_phenotypes[i]
  ztest_df$phenotype[i] <- rownames(bw_reg_table_full_sig_MC[which(bw_reg_table_full_sig_MC$label == shared_phenotypes[i]),])
  ztest_df$p_value[i] <- p_value
}
```
####plot betas with 95% CI
```{r}
ggplot(combined_reg_table %>% filter(label %in% shared_phenotypes), aes(y = label, x = bw_beta, xmin = bw_lower, xmax = bw_upper, color = lm)) +
geom_pointrange(size = 0.3) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 5, margin = margin(r = 10)),  # space labels
        axis.title.y = element_text(margin = margin(r = 15))             # space title
        ) +
  scale_y_discrete(expand = expansion(mult = c(0.1, 0.1))) +
  scale_color_manual(values = c("bw_uni" = "blue", "bwpgs_cov" = "magenta")) +
  labs(x = "Beta Estimate", y = "Phenotype", color = "Regression Type")

```

###BWpgs univariate, BW-pgs and BW model comparisons
```{r}
#univariate x~bw-pgs regression
bw_pgs_reg_table_full_sig_MC$bw_lower <- (bw_pgs_reg_table_full_sig_MC$bw_pgs_beta - 1.96*bw_pgs_reg_table_full_sig_MC$bw_pgs_se)
bw_pgs_reg_table_full_sig_MC$bw_upper <- (bw_pgs_reg_table_full_sig_MC$bw_pgs_beta + 1.96*bw_pgs_reg_table_full_sig_MC$bw_pgs_se)
bw_pgs_reg_table_full_sig_MC <- bw_pgs_reg_table_full_sig_MC %>% mutate(lm = "bwpgs_uni")

#multivariate x~bw-pgs + bwpercentile regression, significant for ga_beta
bw_bwpgs_reg_table_full_sig_MC$bw_lower <- (bw_bwpgs_reg_table_full_sig_MC$bw_pgs_beta - 1.96*bw_bwpgs_reg_table_full_sig_MC$bw_pgs_se)
bw_bwpgs_reg_table_full_sig_MC$bw_upper <- (bw_bwpgs_reg_table_full_sig_MC$bw_pgs_beta + 1.96*bw_bwpgs_reg_table_full_sig_MC$bw_pgs_se)
bw_bwpgs_reg_table_full_sig_MC_plot <- bw_bwpgs_reg_table_full_sig_MC %>% mutate(lm = "bwpgs_cov") %>% select(all_of(names(bw_pgs_reg_table_full_sig_MC)))

#combine tables
combined_reg_table <- rbind(bw_pgs_reg_table_full_sig_MC, bw_bwpgs_reg_table_full_sig_MC_plot)

# Z-test to statistically test change in betas
shared_phenotypes <- bw_pgs_reg_table_full_sig_MC$label[bw_pgs_reg_table_full_sig_MC$label %in% bw_bwpgs_reg_table_full_sig_MC$label]
ztest_df <- data.frame(phenotype = character(length(shared_phenotypes)), 
                        label = character(length(shared_phenotypes)), 
                        p_value = numeric(length(shared_phenotypes)))
for(i in 1:length(shared_phenotypes)){
  beta1 = bw_pgs_reg_table_full_sig_MC[which(bw_pgs_reg_table_full_sig_MC$label == shared_phenotypes[i]), "bw_pgs_beta"]
  se1 = bw_pgs_reg_table_full_sig_MC[which(bw_pgs_reg_table_full_sig_MC$label == shared_phenotypes[i]), "bw_pgs_se"]
  beta2 = bw_bwpgs_reg_table_full_sig_MC[which(bw_bwpgs_reg_table_full_sig_MC$label == shared_phenotypes[i]), "bw_pgs_beta"]
  se2 = bw_pgs_reg_table_full_sig_MC[which(bw_bwpgs_reg_table_full_sig_MC$label == shared_phenotypes[i]), "bw_pgs_se"]
  z <- (beta1 - beta2) / sqrt(se1^2 + se2^2)
  # One-tailed p-value for testing if beta2 is significantly smaller than beta1 
  #(bw_beta smaller when bw-pgs is included in the model)
  p_value <- pnorm(z)
  # #Two tailed
  # p_value <- 2 * pnorm(-abs(z))
  ztest_df$label[i] <- shared_phenotypes[i]
  ztest_df$phenotype[i] <- rownames(bw_pgs_reg_table_full_sig_MC[which(bw_pgs_reg_table_full_sig_MC$label == shared_phenotypes[i]),])
  ztest_df$p_value[i] <- p_value
}
```
####plot betas with 95% CI
```{r}
ggplot(combined_reg_table %>% filter(label %in% shared_phenotypes), aes(y = label, x = bw_pgs_beta, xmin = bw_lower, xmax = bw_upper, color = lm)) +
geom_pointrange(size = 0.3) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 5, margin = margin(r = 10)),  # space labels
        axis.title.y = element_text(margin = margin(r = 15))             # space title
        ) +
  scale_y_discrete(expand = expansion(mult = c(0.1, 0.1))) +
  scale_color_manual(values = c("bwpgs_uni" = "blue", "bwpgs_cov" = "magenta")) +
  labs(x = "Beta Estimate", y = "Phenotype", color = "Regression Type")

```
###BWpgs univariate, BW-pgs and BW model comparisons -- ALL phenotypes, regardless of significance
```{r}
#univariate x~bw-pgs regression
bw_pgs_reg_table_full$bw_lower <- (bw_pgs_reg_table_full$bw_pgs_beta - 1.96*bw_pgs_reg_table_full$bw_pgs_se)
bw_pgs_reg_table_full$bw_upper <- (bw_pgs_reg_table_full$bw_pgs_beta + 1.96*bw_pgs_reg_table_full$bw_pgs_se)
bw_pgs_reg_table_full <- bw_pgs_reg_table_full %>% mutate(lm = "bwpgs_uni")

#multivariate x~bw-pgs + bwpercentile regression, significant for ga_beta
bw_bwpgs_reg_table_full$bw_lower <- (bw_bwpgs_reg_table_full$bw_pgs_beta - 1.96*bw_bwpgs_reg_table_full$bw_pgs_se)
bw_bwpgs_reg_table_full$bw_upper <- (bw_bwpgs_reg_table_full$bw_pgs_beta + 1.96*bw_bwpgs_reg_table_full$bw_pgs_se)
bw_bwpgs_reg_table_full_plot <- bw_bwpgs_reg_table_full %>% mutate(lm = "bwpgs_cov") %>% select(all_of(names(bw_pgs_reg_table_full)))

#combine tables
combined_reg_table <- rbind(bw_pgs_reg_table_full, bw_bwpgs_reg_table_full_plot)

# Z-test to statistically test change in betas
shared_phenotypes <- bw_pgs_reg_table_full$label[bw_pgs_reg_table_full$label %in% bw_bwpgs_reg_table_full$label]
ztest_df <- data.frame(phenotype = character(length(shared_phenotypes)), 
                        label = character(length(shared_phenotypes)), 
                        p_value = numeric(length(shared_phenotypes)))
for(i in 1:length(shared_phenotypes)){
  beta1 = bw_pgs_reg_table_full[which(bw_pgs_reg_table_full$label == shared_phenotypes[i]), "bw_pgs_beta"]
  se1 = bw_pgs_reg_table_full[which(bw_pgs_reg_table_full$label == shared_phenotypes[i]), "bw_pgs_se"]
  beta2 = bw_bwpgs_reg_table_full[which(bw_bwpgs_reg_table_full$label == shared_phenotypes[i]), "bw_pgs_beta"]
  se2 = bw_pgs_reg_table_full[which(bw_bwpgs_reg_table_full$label == shared_phenotypes[i]), "bw_pgs_se"]
  z <- (beta1 - beta2) / sqrt(se1^2 + se2^2)
  # One-tailed p-value for testing if beta2 is significantly smaller than beta1 
  #(bw_beta smaller when bw-pgs is included in the model)
  p_value <- pnorm(z)
  # #Two tailed
  # p_value <- 2 * pnorm(-abs(z))
  ztest_df$label[i] <- shared_phenotypes[i]
  ztest_df$phenotype[i] <- rownames(bw_pgs_reg_table_full[which(bw_pgs_reg_table_full$label == shared_phenotypes[i]),])
  ztest_df$p_value[i] <- p_value
}
```
####plot betas with 95% CI
```{r}
ggplot(combined_reg_table %>% filter(label %in% shared_phenotypes), aes(y = label, x = bw_pgs_beta, xmin = bw_lower, xmax = bw_upper, color = lm)) +
geom_pointrange(size = 0.3) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 5, margin = margin(r = 10)),  # space labels
        axis.title.y = element_text(margin = margin(r = 15))             # space title
        ) +
  scale_y_discrete(expand = expansion(mult = c(0.1, 0.1))) +
  scale_color_manual(values = c("bwpgs_uni" = "blue", "bwpgs_cov" = "magenta")) +
  labs(x = "Beta Estimate", y = "Phenotype", color = "Regression Type")

```
#BW-GA 2x2 -- BW focus (high GA includes 40weeks only), includes the centile means plotting
```{r}
test_prs$bwga_category <- ifelse(test_prs$birth_weight_sum_oz > median(test_prs$birth_weight_sum_oz, na.rm = TRUE) & test_prs$gestAge <= 36, "highBW_lowGA", ifelse(test_prs$birth_weight_sum_oz < median(test_prs$birth_weight_sum_oz, na.rm = TRUE) & test_prs$gestAge >= 37, "lowBW_highGA", ifelse(test_prs$birth_weight_sum_oz < median(test_prs$birth_weight_sum_oz, na.rm = TRUE) & test_prs$gestAge <=36, "lowBW_lowGA", ifelse(test_prs$birth_weight_sum_oz > median(test_prs$birth_weight_sum_oz, na.rm = TRUE) & test_prs$gestAge >= 37, "highBW_highGA", NA))))

test_prs$bw_highlow <- ifelse(test_prs$birth_weight_sum_oz > median(test_prs$birth_weight_sum_oz, na.rm = TRUE), "highBW", ifelse(test_prs$birth_weight_sum_oz < median(test_prs$birth_weight_sum_oz, na.rm = TRUE), "lowBW", NA))

test_prs$ga_highlow <- ifelse(test_prs$gestAge <= 36, "lowGA", ifelse(test_prs$gestAge >= 37, "highGA", NA))

#birthweight stats by category
test_prs %>% group_by(bwga_category) %>% summarise(mean = mean(birth_weight_sum_oz))

test_prs$bwpga_category <- ifelse(test_prs$bweight_percentile > median(test_prs$bweight_percentile, na.rm = TRUE) & test_prs$gestAge <= 36, "highBW_lowGA", ifelse(test_prs$bweight_percentile < median(test_prs$bweight_percentile, na.rm = TRUE) & test_prs$gestAge >= 37, "lowBW_highGA", ifelse(test_prs$bweight_percentile < median(test_prs$bweight_percentile, na.rm = TRUE) & test_prs$gestAge <=36, "lowBW_lowGA", ifelse(test_prs$bweight_percentile > median(test_prs$bweight_percentile, na.rm = TRUE) & test_prs$gestAge >= 37, "highBW_highGA", NA))))

#birthweight stats by category
test_prs %>% group_by(bwpga_category) %>% summarise(mean = mean(bweight_percentile))

#Separate dataframes for regressions
highBW_lowGA <- test_prs %>% filter(birth_weight_sum_oz > median(birth_weight_sum_oz, na.rm = TRUE) & gestAge <=36) #63

lowBW_highGA <- test_prs %>% filter(birth_weight_sum_oz < median(test_prs$birth_weight_sum_oz, na.rm = TRUE) & gestAge >=37)#3443

lowBW_lowGA <- test_prs %>% filter(birth_weight_sum_oz < median(birth_weight_sum_oz, na.rm = TRUE) & gestAge <=36)#1345

highBW_highGA <- test_prs %>% filter(birth_weight_sum_oz > median(test_prs$birth_weight_sum_oz, na.rm = TRUE) & gestAge >=37)#4590
```
###visualize mean centile score for each region, use birthweight percentile
```{r}
#get table with means for each centile score within each bw-ga category (2x2 categories as above)
centiles_means <- test_prs %>%
  select(bwga_category, contains("centiles")) %>%
  pivot_longer(cols = -bwga_category, names_to = "centiles", values_to = "value") %>%
  group_by(bwga_category, centiles) %>%
  summarise(mean = mean(value, na.rm = TRUE), .groups = "drop")
#add column for label
centiles_means$label <- name_mapping$region_name[match(sub("_centiles", "", centiles_means$centiles), name_mapping$abbreviation)]

#violin plots
# Reshape data
df_long <- test_prs %>%
  pivot_longer(cols = contains("centile"), names_to = "phenotype", values_to = "value")
df_long$label <- name_mapping$region_name[match(sub("_centiles", "", df_long$phenotype), name_mapping$abbreviation)]

# Split centile types into groups of 10
phenotype_groups <- split(unique(df_long$phenotype), ceiling(seq_along(unique(df_long$phenotype)) / 12))

#Anova between categories
anova_twoway_results <- df_long %>%
  filter(!is.na(bw_category)) %>%
  group_by(phenotype) %>%
  summarise(tidy(aov(value ~ bw_highlow * ga_highlow, data = cur_data())), .groups = "drop")

anova_twoway_results %>% filter(term == "bw_highlow:ga_highlow" & p.value < 0.05)

#T test between lowBW lowGA and lowBW high GA
ttest_results <- df_long %>%
  filter(bwga_category %in% c("lowBW_lowGA", "lowBW_highGA")) %>%
  group_by(phenotype) %>%
  summarise(tidy(t.test(value ~ bwga_category)), .groups = "drop")


ttest_results$label <- name_mapping$region_name[match(sub("_centiles", "", ttest_results$phenotype), name_mapping$abbreviation)]

ttest_results$p.value_adj <-  p.adjust(ttest_results$p.value, method = "BH")
ttest_results %>% filter(p.value_adj < 0.05) %>% select(c(label, p.value_adj, estimate))

# Create plots
plot_list <- lapply(phenotype_groups, function(group) {
  ggplot(filter(df_long %>% filter(!is.na(bwga_category)), phenotype %in% group), aes(x = bwga_category, y = value, color = bwga_category, fill = bwga_category)) +
    geom_boxplot(alpha = 0.35) +
    geom_jitter(width = 0.1, size = 0.2, alpha = 0.2) +
    facet_wrap(~ label, scales = "fixed") +
    theme_minimal() +
    theme(axis.text.x =  element_blank())
})

# Display plots
plot_list
```
####surface maps for cortical and subcortical regions
```{r}
#merge with atlas data
plot_data_dkt <- merge(centiles_means, ggseg::dk, by = "label")
plot_data_aseg <- merge(centiles_means, ggseg::aseg, by = "label")

#PLOTS
##Plot highBW lowGA
# Plot using ggseg
ggplot(plot_data_dkt %>% filter(bwga_category == "highBW_lowGA")) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = mean)) +
  scale_fill_gradient(limits = c(0.40, 0.65)) +
  theme_void() +
  labs(title = "Mean, highBW low GA")

ggplot(plot_data_aseg %>% filter(bwga_category == "highBW_lowGA")) +
  geom_brain(atlas = aseg,
             aes(fill = mean)) +
  scale_fill_gradient(limits =  c(0.40, 0.65)) +
  theme_void() +
  labs(title = "Mean, highBW low GA")

##Plot highBW highGA
# Plot using ggseg
ggplot(plot_data_dkt %>% filter(bwga_category == "highBW_highGA")) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = mean)) +
  scale_fill_gradient(limits = c(0.40, 0.65)) +
  theme_void() +
  labs(title = "Mean, highBW high GA")

ggplot(plot_data_aseg %>% filter(bwga_category == "highBW_highGA")) +
  geom_brain(atlas = aseg,
             aes(fill = mean)) +
  scale_fill_gradient(limits =  c(0.40, 0.65)) +
  theme_void() +
  labs(title = "Mean, highBW high GA")

##Plot lowBW highGA
# Plot using ggseg
ggplot(plot_data_dkt %>% filter(bwga_category == "lowBW_highGA")) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = mean)) +
  scale_fill_gradient(limits = c(0.40, 0.65)) +
  theme_void() +
  labs(title = "Mean, lowBW high GA")

ggplot(plot_data_aseg %>% filter(bwga_category == "lowBW_highGA")) +
  geom_brain(atlas = aseg,
             aes(fill = mean)) +
  scale_fill_gradient(limits =  c(0.40, 0.65)) +
  theme_void() +
  labs(title = "Mean, lowBW high GA")

##Plot lowBW lowGA
# Plot using ggseg
ggplot(plot_data_dkt %>% filter(bwga_category == "lowBW_lowGA")) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = mean)) +
  scale_fill_gradient(limits = c(0.40, 0.65)) +
  theme_void() +
  labs(title = "Mean, lowBW lowGA")

ggplot(plot_data_aseg %>% filter(bwga_category == "lowBW_lowGA")) +
  geom_brain(atlas = aseg,
             aes(fill = mean)) +
  scale_fill_gradient(limits =  c(0.40, 0.65)) +
  theme_void() +
  labs(title = "Mean, lowBW lowGA")
```
###birth weight - lowBW high GA
```{r}
sum(!is.na(lowBW_highGA$birth_weight_sum_oz))
bw_zscore <- z_score(lowBW_highGA$birth_weight_sum_oz)

#Global phenotypes
lowBWhighGA_bw_reg_table_global <- as.data.frame(t(sapply(lowBW_highGA[, which(names(lowBW_highGA) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4])
})))

lowBWhighGA_bw_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWhighGA_bw_reg_table_global)), name_mapping$abbreviation)]

lowBWhighGA_bw_reg_table_global_sig <- lowBWhighGA_bw_reg_table_global %>% filter(bw_p < 0.05)

lowBWhighGA_bw_reg_table_global_sig

#Regional phenotypes
lowBWhighGA_bw_reg_table_full <- as.data.frame(t(sapply(lowBW_highGA[, which(names(lowBW_highGA) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4])
})))

lowBWhighGA_bw_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWhighGA_bw_reg_table_full)), name_mapping$abbreviation)]

lowBWhighGA_bw_reg_table_full_sig <- lowBWhighGA_bw_reg_table_full %>% filter(bw_p < 0.05)
lowBWhighGA_bw_reg_table_full$bw_p_adj <- p.adjust(lowBWhighGA_bw_reg_table_full$bw_p, method = "BH")
lowBWhighGA_bw_reg_table_full_sig_MC <- lowBWhighGA_bw_reg_table_full %>% filter(bw_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- lowBWhighGA_bw_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "bw_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweight_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweight_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```

```{r}
#merge with atlas data
plot_data_dkt <- merge(lowBWhighGA_bw_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(lowBWhighGA_bw_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
lowBWhighGA_bw_reg_table_full_sig_MC[!(lowBWhighGA_bw_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(lowBWhighGA_bw_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with BW, lowBW 40 weeks")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW, lowBW 40 weeks")
```

###birth weight - highBW high GA
```{r}
sum(!is.na(highBW_highGA$birth_weight_sum_oz))
bw_zscore <- z_score(highBW_highGA$birth_weight_sum_oz)

#Global phenotypes
highBWhighGA_bw_reg_table_global <- as.data.frame(t(sapply(highBW_highGA[, which(names(highBW_highGA) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4])
})))

highBWhighGA_bw_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(highBWhighGA_bw_reg_table_global)), name_mapping$abbreviation)]

highBWhighGA_bw_reg_table_global_sig <- highBWhighGA_bw_reg_table_global %>% filter(bw_p < 0.05)

highBWhighGA_bw_reg_table_global_sig

#Regional phenotypes
highBWhighGA_bw_reg_table_full <- as.data.frame(t(sapply(highBW_highGA[, which(names(highBW_highGA) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4])
})))

highBWhighGA_bw_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(highBWhighGA_bw_reg_table_full)), name_mapping$abbreviation)]

highBWhighGA_bw_reg_table_full_sig <- highBWhighGA_bw_reg_table_full %>% filter(bw_p < 0.05)
highBWhighGA_bw_reg_table_full$bw_p_adj <- p.adjust(highBWhighGA_bw_reg_table_full$bw_p, method = "BH")
highBWhighGA_bw_reg_table_full_sig_MC <- highBWhighGA_bw_reg_table_full %>% filter(bw_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- highBWhighGA_bw_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "bw_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweight_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweight_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```

```{r}
#merge with atlas data
plot_data_dkt <- merge(highBWhighGA_bw_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(highBWhighGA_bw_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
highBWhighGA_bw_reg_table_full_sig_MC[!(highBWhighGA_bw_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(highBWhighGA_bw_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with BW, highBW 40 weeks")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW, highBW 40 weeks")
```

###birth weight - low BW low GA
```{r}
sum(!is.na(lowBW_lowGA$birth_weight_sum_oz))
bw_zscore <- z_score(lowBW_lowGA$birth_weight_sum_oz)

#Global phenotypes
lowBWlowGA_bw_reg_table_global <- as.data.frame(t(sapply(lowBW_lowGA[, which(names(lowBW_lowGA) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4])
})))

lowBWlowGA_bw_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWlowGA_bw_reg_table_global)), name_mapping$abbreviation)]

lowBWlowGA_bw_reg_table_global_sig <- lowBWlowGA_bw_reg_table_global %>% filter(bw_p < 0.05)

lowBWlowGA_bw_reg_table_global_sig

#Regional phenotypes
lowBWlowGA_bw_reg_table_full <- as.data.frame(t(sapply(lowBW_lowGA[, which(names(lowBW_lowGA) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4])
})))

lowBWlowGA_bw_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWlowGA_bw_reg_table_full)), name_mapping$abbreviation)]

lowBWlowGA_bw_reg_table_full_sig <- lowBWlowGA_bw_reg_table_full %>% filter(bw_p < 0.05)
lowBWlowGA_bw_reg_table_full$bw_p_adj <- p.adjust(lowBWlowGA_bw_reg_table_full$bw_p, method = "BH")
lowBWlowGA_bw_reg_table_full_sig_MC <- lowBWlowGA_bw_reg_table_full %>% filter(bw_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- lowBWlowGA_bw_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "bw_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweight_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweight_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```

```{r}
#merge with atlas data
plot_data_dkt <- merge(lowBWlowGA_bw_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(lowBWlowGA_bw_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
lowBWlowGA_bw_reg_table_full_sig_MC[!(lowBWlowGA_bw_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(lowBWlowGA_bw_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.25)) +
  theme_void() +
  labs(title = "Cortical Regions with BW, lowBW <=36 weeks")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.25)) +
  theme_void() +
  labs(title = "Subcortical with BW, lowBW <= 36 weeks")
```


###birth weight - high BW low GA
```{r}
sum(!is.na(highBW_lowGA$birth_weight_sum_oz))
bw_zscore <- z_score(highBW_lowGA$birth_weight_sum_oz)

#Global phenotypes
highBWlowGA_bw_reg_table_global <- as.data.frame(t(sapply(highBW_lowGA[, which(names(highBW_lowGA) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4])
})))

highBWlowGA_bw_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(highBWlowGA_bw_reg_table_global)), name_mapping$abbreviation)]

highBWlowGA_bw_reg_table_global_sig <- highBWlowGA_bw_reg_table_global %>% filter(bw_p < 0.05)

highBWlowGA_bw_reg_table_global_sig

#Regional phenotypes
highBWlowGA_bw_reg_table_full <- as.data.frame(t(sapply(highBW_lowGA[, which(names(highBW_lowGA) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_zscore)
  summary <- summary(lm)
  
  c(bw_beta = summary$coefficients[2,1], bw_p = summary$coefficients[2,4])
})))

highBWlowGA_bw_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(highBWlowGA_bw_reg_table_full)), name_mapping$abbreviation)]

highBWlowGA_bw_reg_table_full_sig <- highBWlowGA_bw_reg_table_full %>% filter(bw_p < 0.05)
highBWlowGA_bw_reg_table_full$bw_p_adj <- p.adjust(highBWlowGA_bw_reg_table_full$bw_p, method = "BH")
highBWlowGA_bw_reg_table_full_sig_MC <- highBWlowGA_bw_reg_table_full %>% filter(bw_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- highBWlowGA_bw_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "bw_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweight_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweight_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```


#BW-GA 2x2 -- GA focus (high GA includes >= 37 weeks)
?? Maybe make centile plots and color these groups differently
these groups include subjects born at >= 37 weeks in the "highGA" group
```{r}
highBW_lowGA <- test_prs %>% filter(birth_weight_sum_oz > median(birth_weight_sum_oz, na.rm = TRUE) & gestAge <=36)#63

lowBW_highGA <- test_prs %>% filter(birth_weight_sum_oz < median(test_prs$birth_weight_sum_oz, na.rm = TRUE) & gestAge > 36)#3095

lowBW_lowGA <- test_prs %>% filter(birth_weight_sum_oz < median(birth_weight_sum_oz, na.rm = TRUE) & gestAge <=36)#1345

highBW_highGA <- test_prs %>% filter(birth_weight_sum_oz > median(test_prs$birth_weight_sum_oz, na.rm = TRUE) & gestAge > 36)#4590
```
###gestational age - lowBW high GA
```{r}
sum(!is.na(lowBW_highGA$gestAge))
ga_zscore <- z_score(lowBW_highGA$gestAge)

#Global phenotypes
lowBWhighGA_ga_reg_table_global <- as.data.frame(t(sapply(lowBW_highGA[, which(names(lowBW_highGA) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4])
})))

lowBWhighGA_ga_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWhighGA_ga_reg_table_global)), name_mapping$abbreviation)]

lowBWhighGA_ga_reg_table_global_sig <- lowBWhighGA_ga_reg_table_global %>% filter(ga_p < 0.05)

lowBWhighGA_ga_reg_table_global_sig

#Regional phenotypes
lowBWhighGA_ga_reg_table_full <- as.data.frame(t(sapply(lowBW_highGA[, which(names(lowBW_highGA) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4])
})))

lowBWhighGA_ga_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWhighGA_ga_reg_table_full)), name_mapping$abbreviation)]

lowBWhighGA_ga_reg_table_full_sig <- lowBWhighGA_ga_reg_table_full %>% filter(ga_p < 0.05)
lowBWhighGA_ga_reg_table_full$ga_p_adj <- p.adjust(lowBWhighGA_ga_reg_table_full$ga_p, method = "BH")
lowBWhighGA_ga_reg_table_full_sig_MC <- lowBWhighGA_ga_reg_table_full %>% filter(ga_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- lowBWhighGA_ga_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "ga_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweight_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweight_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```

```{r}
#merge with atlas data
plot_data_dkt <- merge(lowBWhighGA_ga_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(lowBWhighGA_ga_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
lowBWhighGA_ga_reg_table_full_sig_MC[!(lowBWhighGA_ga_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(lowBWhighGA_ga_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with GA, lowBW >=37wks")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW, lowBW >=37wks")
```
plotting pre-FDR just to get an idea
```{r}
#merge with atlas data
plot_data_dkt <- merge(lowBWhighGA_ga_reg_table_full_sig, ggseg::dk, by = "label")
plot_data_aseg <- merge(lowBWhighGA_ga_reg_table_full_sig, ggseg::aseg, by = "label")

#Regions not matched in atlases
lowBWhighGA_ga_reg_table_full_sig[!(lowBWhighGA_ga_reg_table_full_sig$label %in% plot_data_dkt$label) & !(lowBWhighGA_ga_reg_table_full_sig$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with GA, lowBW >=37wks")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW, lowBW >=37wks")
```
###gestational age - highBW high GA --- all GA is 40weeks, cannot run correlation
###gestational age - low BW low GA
```{r}
sum(!is.na(lowBW_lowGA$gestAge))
ga_zscore <- z_score(lowBW_lowGA$gestAge)

#Global phenotypes
lowBWlowGA_ga_reg_table_global <- as.data.frame(t(sapply(lowBW_lowGA[, which(names(lowBW_lowGA) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4])
})))

lowBWlowGA_ga_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWlowGA_ga_reg_table_global)), name_mapping$abbreviation)]

lowBWlowGA_ga_reg_table_global_sig <- lowBWlowGA_ga_reg_table_global %>% filter(ga_p < 0.05)

lowBWlowGA_ga_reg_table_global_sig

#Regional phenotypes
lowBWlowGA_ga_reg_table_full <- as.data.frame(t(sapply(lowBW_lowGA[, which(names(lowBW_lowGA) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4])
})))

lowBWlowGA_ga_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWlowGA_ga_reg_table_full)), name_mapping$abbreviation)]

lowBWlowGA_ga_reg_table_full_sig <- lowBWlowGA_ga_reg_table_full %>% filter(ga_p < 0.05)
lowBWlowGA_ga_reg_table_full$ga_p_adj <- p.adjust(lowBWlowGA_ga_reg_table_full$ga_p, method = "BH")
lowBWlowGA_ga_reg_table_full_sig_MC <- lowBWlowGA_ga_reg_table_full %>% filter(ga_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- lowBWlowGA_ga_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "ga_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweight_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweight_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```

```{r}
#merge with atlas data
plot_data_dkt <- merge(lowBWlowGA_ga_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(lowBWlowGA_ga_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
lowBWlowGA_ga_reg_table_full_sig_MC[!(lowBWlowGA_ga_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(lowBWlowGA_ga_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with GA, lowBW <=36 weeks")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with GA, lowBW <= 36 weeks")
```



#BW-GA 2x2 -- BW-PGS focus (high GA includes 40weeks only)
?? Maybe make centile plots and color these groups differently

```{r}
highBW_lowGA <- test_prs %>% filter(birth_weight_sum_oz > median(birth_weight_sum_oz, na.rm = TRUE) & gestAge <=36)#63

lowBW_highGA <- test_prs %>% filter(birth_weight_sum_oz < median(test_prs$birth_weight_sum_oz, na.rm = TRUE) & gestAge > 36)#3095

lowBW_lowGA <- test_prs %>% filter(birth_weight_sum_oz < median(birth_weight_sum_oz, na.rm = TRUE) & gestAge <=36)#1345

highBW_highGA <- test_prs %>% filter(birth_weight_sum_oz > median(test_prs$birth_weight_sum_oz, na.rm = TRUE) & gestAge > 36)#4467
```
###birth weight PGS - lowBW high GA
```{r}
sum(!is.na(lowBW_highGA$bw_pgs))
bw_pgs_zscore <- as.data.frame(sapply(lowBW_highGA[,c("bw_pgs", "PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10")], function(x) {z_score(x)}))

#Global Phenotypes
lowBWhighGA_bw_pgs_reg_table_global <- as.data.frame(t(sapply(lowBW_highGA[, which(names(lowBW_highGA) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_pgs_zscore$bw_pgs + bw_pgs_zscore$PC1 + bw_pgs_zscore$PC2 + bw_pgs_zscore$PC3 + bw_pgs_zscore$PC4 + bw_pgs_zscore$PC5 + bw_pgs_zscore$PC6 + bw_pgs_zscore$PC7 + bw_pgs_zscore$PC8 + bw_pgs_zscore$PC9 + bw_pgs_zscore$PC10)
  summary <- summary(lm)
  
  c(bw_pgs_beta = summary$coefficients[2,1], bw_pgs_p = summary$coefficients[2,4])
})))

lowBWhighGA_bw_pgs_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWhighGA_bw_pgs_reg_table_global)), name_mapping$abbreviation)]

lowBWhighGA_bw_pgs_reg_table_global_sig <- lowBWhighGA_bw_pgs_reg_table_global %>% filter(bw_pgs_p < 0.05)

lowBWhighGA_bw_pgs_reg_table_global_sig

#Regional Phenotypes
lowBWhighGA_bw_pgs_reg_table_full <- as.data.frame(t(sapply(lowBW_highGA[,which(names(lowBW_highGA) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_pgs_zscore$bw_pgs + bw_pgs_zscore$PC1 + bw_pgs_zscore$PC2 + bw_pgs_zscore$PC3 + bw_pgs_zscore$PC4 + bw_pgs_zscore$PC5 + bw_pgs_zscore$PC6 + bw_pgs_zscore$PC7 + bw_pgs_zscore$PC8 + bw_pgs_zscore$PC9 + bw_pgs_zscore$PC10)
  summary <- summary(lm)
  
  c(bw_pgs_beta = summary$coefficients[2,1], bw_pgs_p = summary$coefficients[2,4])
})))

lowBWhighGA_bw_pgs_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWhighGA_bw_pgs_reg_table_full)), name_mapping$abbreviation)]

lowBWhighGA_bw_pgs_reg_table_full_sig <- lowBWhighGA_bw_pgs_reg_table_full %>% filter(bw_pgs_p < 0.05)
lowBWhighGA_bw_pgs_reg_table_full$bw_pgs_p_adj <- p.adjust(lowBWhighGA_bw_pgs_reg_table_full$bw_pgs_p, method = "BH")
lowBWhighGA_bw_pgs_reg_table_full_sig_MC <- lowBWhighGA_bw_pgs_reg_table_full %>% filter(bw_pgs_p_adj < 0.05)

#save tables of betas
save_tables = TRUE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- lowBWhighGA_bw_pgs_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "lowBWhighGA_bw_pgs_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweightPGS_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweightPGS_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```

```{r}
#merge with atlas data
plot_data_dkt <- merge(lowBWhighGA_bw_pgs_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(lowBWhighGA_bw_pgs_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
lowBWhighGA_bw_pgs_reg_table_full_sig_MC[!(lowBWhighGA_bw_pgs_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(lowBWhighGA_bw_pgs_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_pgs_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with BW pgs, low BW >=37wks")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_pgs_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW pgs, low BW >=37wks")
```

###birth weight PGS - lowBW low GA
```{r}
sum(!is.na(lowBW_lowGA$bw_pgs))
bw_pgs_zscore <- as.data.frame(sapply(lowBW_lowGA[,c("bw_pgs", "PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10")], function(x) {z_score(x)}))

#Global Phenotypes
lowBWlowGA_bw_pgs_reg_table_global <- as.data.frame(t(sapply(lowBW_lowGA[, which(names(lowBW_lowGA) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_pgs_zscore$bw_pgs + bw_pgs_zscore$PC1 + bw_pgs_zscore$PC2 + bw_pgs_zscore$PC3 + bw_pgs_zscore$PC4 + bw_pgs_zscore$PC5 + bw_pgs_zscore$PC6 + bw_pgs_zscore$PC7 + bw_pgs_zscore$PC8 + bw_pgs_zscore$PC9 + bw_pgs_zscore$PC10)
  summary <- summary(lm)
  
  c(bw_pgs_beta = summary$coefficients[2,1], bw_pgs_p = summary$coefficients[2,4])
})))

lowBWlowGA_bw_pgs_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWlowGA_bw_pgs_reg_table_global)), name_mapping$abbreviation)]

lowBWlowGA_bw_pgs_reg_table_global_sig <- lowBWlowGA_bw_pgs_reg_table_global %>% filter(bw_pgs_p < 0.05)

lowBWlowGA_bw_pgs_reg_table_global_sig

#Regional Phenotypes
lowBWlowGA_bw_pgs_reg_table_full <- as.data.frame(t(sapply(lowBW_lowGA[,which(names(lowBW_lowGA) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ bw_pgs_zscore$bw_pgs + bw_pgs_zscore$PC1 + bw_pgs_zscore$PC2 + bw_pgs_zscore$PC3 + bw_pgs_zscore$PC4 + bw_pgs_zscore$PC5 + bw_pgs_zscore$PC6 + bw_pgs_zscore$PC7 + bw_pgs_zscore$PC8 + bw_pgs_zscore$PC9 + bw_pgs_zscore$PC10)
  summary <- summary(lm)
  
  c(bw_pgs_beta = summary$coefficients[2,1], bw_pgs_p = summary$coefficients[2,4])
})))

lowBWlowGA_bw_pgs_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWlowGA_bw_pgs_reg_table_full)), name_mapping$abbreviation)]

lowBWlowGA_bw_pgs_reg_table_full_sig <- lowBWlowGA_bw_pgs_reg_table_full %>% filter(bw_pgs_p < 0.05)
lowBWlowGA_bw_pgs_reg_table_full$bw_pgs_p_adj <- p.adjust(lowBWlowGA_bw_pgs_reg_table_full$bw_pgs_p, method = "BH")
lowBWlowGA_bw_pgs_reg_table_full_sig_MC <- lowBWlowGA_bw_pgs_reg_table_full %>% filter(bw_pgs_p_adj < 0.05)

#save tables of betas
save_tables = TRUE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- lowBWlowGA_bw_pgs_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "lowBWlowGA_bw_pgs_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweightPGS_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweightPGS_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```
showing pre-FDR
```{r}
#merge with atlas data
plot_data_dkt <- merge(lowBWlowGA_bw_pgs_reg_table_full_sig, ggseg::dk, by = "label")
plot_data_aseg <- merge(lowBWlowGA_bw_pgs_reg_table_full_sig, ggseg::aseg, by = "label")

#Regions not matched in atlases
lowBWlowGA_bw_pgs_reg_table_full_sig[!(lowBWlowGA_bw_pgs_reg_table_full_sig$label %in% plot_data_dkt$label) & !(lowBWlowGA_bw_pgs_reg_table_full_sig$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = bw_pgs_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with BW pgs, low BW <37wks, pre-FDR")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = bw_pgs_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW pgs, low BW <37wks, pre-FDR")
```


#BW-GA 2x2 -- GA focus (high GA includes >= 37 weeks), bw division by z-scores
?? Maybe make centile plots and color these groups differently
these groups include subjects born at >= 37 weeks in the "highGA" group
```{r}
test_prs$bw_zscore <- z_score(test_prs$birth_weight_sum_oz)
highBW_lowGA <- test_prs %>% filter(bw_zscore > 1.5 & gestAge <=36)#6

lowBW_highGA <- test_prs %>% filter(bw_zscore < -1.5  & gestAge > 36)#148

lowBW_lowGA <- test_prs %>% filter(bw_zscore < -1.5  & gestAge <=36)#617

highBW_highGA <- test_prs %>% filter(bw_zscore > 1.5  & gestAge > 36)#516
```
###gestational age - lowBW high GA
```{r}
sum(!is.na(lowBW_highGA$gestAge))
ga_zscore <- z_score(lowBW_highGA$gestAge)

#Global phenotypes
lowBWhighGA_ga_reg_table_global <- as.data.frame(t(sapply(lowBW_highGA[, which(names(lowBW_highGA) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4])
})))

lowBWhighGA_ga_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWhighGA_ga_reg_table_global)), name_mapping$abbreviation)]

lowBWhighGA_ga_reg_table_global_sig <- lowBWhighGA_ga_reg_table_global %>% filter(ga_p < 0.05)

lowBWhighGA_ga_reg_table_global_sig

#Regional phenotypes
lowBWhighGA_ga_reg_table_full <- as.data.frame(t(sapply(lowBW_highGA[, which(names(lowBW_highGA) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4])
})))

lowBWhighGA_ga_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWhighGA_ga_reg_table_full)), name_mapping$abbreviation)]

lowBWhighGA_ga_reg_table_full_sig <- lowBWhighGA_ga_reg_table_full %>% filter(ga_p < 0.05)
lowBWhighGA_ga_reg_table_full$ga_p_adj <- p.adjust(lowBWhighGA_ga_reg_table_full$ga_p, method = "BH")
lowBWhighGA_ga_reg_table_full_sig_MC <- lowBWhighGA_ga_reg_table_full %>% filter(ga_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- lowBWhighGA_ga_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "ga_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweight_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweight_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```

```{r}
#merge with atlas data
plot_data_dkt <- merge(lowBWhighGA_ga_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(lowBWhighGA_ga_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
lowBWhighGA_ga_reg_table_full_sig_MC[!(lowBWhighGA_ga_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(lowBWhighGA_ga_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with GA, lowBW >=37wks")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW, lowBW >=37wks")
```
plotting pre-FDR just to get an idea
```{r}
#merge with atlas data
plot_data_dkt <- merge(lowBWhighGA_ga_reg_table_full_sig, ggseg::dk, by = "label")
plot_data_aseg <- merge(lowBWhighGA_ga_reg_table_full_sig, ggseg::aseg, by = "label")

#Regions not matched in atlases
lowBWhighGA_ga_reg_table_full_sig[!(lowBWhighGA_ga_reg_table_full_sig$label %in% plot_data_dkt$label) & !(lowBWhighGA_ga_reg_table_full_sig$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with GA, lowBW >=37wks")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with BW, lowBW >=37wks")
```
###gestational age - highBW high GA --- all GA is 40weeks, cannot run correlation
###gestational age - low BW low GA
```{r}
sum(!is.na(lowBW_lowGA$gestAge))
ga_zscore <- z_score(lowBW_lowGA$gestAge)

#Global phenotypes
lowBWlowGA_ga_reg_table_global <- as.data.frame(t(sapply(lowBW_lowGA[, which(names(lowBW_lowGA) %in% paste0(global_phenotypes, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4])
})))

lowBWlowGA_ga_reg_table_global$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWlowGA_ga_reg_table_global)), name_mapping$abbreviation)]

lowBWlowGA_ga_reg_table_global_sig <- lowBWlowGA_ga_reg_table_global %>% filter(ga_p < 0.05)

lowBWlowGA_ga_reg_table_global_sig

#Regional phenotypes
lowBWlowGA_ga_reg_table_full <- as.data.frame(t(sapply(lowBW_lowGA[, which(names(lowBW_lowGA) %in% paste0(phenotypes_for_MC, "_centiles"))], function(x) {
  x_zscore <- qnorm(x)
  lm <- lm(x_zscore ~ ga_zscore)
  summary <- summary(lm)
  
  c(ga_beta = summary$coefficients[2,1], ga_p = summary$coefficients[2,4])
})))

lowBWlowGA_ga_reg_table_full$label <- name_mapping$region_name[match(sub("_centiles", "", rownames(lowBWlowGA_ga_reg_table_full)), name_mapping$abbreviation)]

lowBWlowGA_ga_reg_table_full_sig <- lowBWlowGA_ga_reg_table_full %>% filter(ga_p < 0.05)
lowBWlowGA_ga_reg_table_full$ga_p_adj <- p.adjust(lowBWlowGA_ga_reg_table_full$ga_p, method = "BH")
lowBWlowGA_ga_reg_table_full_sig_MC <- lowBWlowGA_ga_reg_table_full %>% filter(ga_p_adj < 0.05)

#save tables of betas
save_tables = FALSE
if(save_tables == TRUE){
  output_folder <-"/mnt/isilon/bgdlab_processing/Eren/ABCD-braincharts/CSV/Surface_Maps/"
  save_table_full <- lowBWlowGA_ga_reg_table_full
  save_table_full$hemisphere <- ifelse(grepl("lh", save_table_full$label), "L", 
                         ifelse(grepl("rh", save_table_full$label), "R", NA))
  save_table_full$label <- sub("^rh_|lh_", "", save_table_full$label)
  save_table_sig <- save_table_full
  save_table_sig[which(save_table_sig$save_p_adj>0.05), "ga_beta"] <- 0
  filename_all <- paste0(output_folder, "dsk_birthweight_all.csv")
  filename_sig <- paste0(output_folder, "dsk_birthweight_sig.csv")
  write.csv(save_table_full, filename_all)
  write.csv(save_table_sig, filename_sig)
}
```

```{r}
#merge with atlas data
plot_data_dkt <- merge(lowBWlowGA_ga_reg_table_full_sig_MC, ggseg::dk, by = "label")
plot_data_aseg <- merge(lowBWlowGA_ga_reg_table_full_sig_MC, ggseg::aseg, by = "label")

#Regions not matched in atlases
lowBWlowGA_ga_reg_table_full_sig_MC[!(lowBWlowGA_ga_reg_table_full_sig_MC$label %in% plot_data_dkt$label) & !(lowBWlowGA_ga_reg_table_full_sig_MC$label %in% plot_data_aseg$label),]

# Plot using ggseg
ggplot(plot_data_dkt) +
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Cortical Regions with GA, lowBW <=36 weeks")

ggplot(plot_data_aseg) +
  geom_brain(atlas = aseg,
             aes(fill = ga_beta)) +
  scale_fill_gradient2(limits = c(-0.2, 0.2)) +
  theme_void() +
  labs(title = "Subcortical with GA, lowBW <= 36 weeks")
```

